\documentclass[10pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[margin=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}

\title{Divine Liturgy\\Reading from The Gospels}
\date{Week 19 after the Pentecost\vspace{-5ex}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\large\singlespacing
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 83 зач., XVI, 19-31.}\\
Некоторый человек был богат, одевался в порфиру и виссон и каждый день пиршествовал блистательно.\\
Был также некоторый нищий, именем Лазарь, который лежал у ворот его в струпьях\\
и желал напитаться крошками, падающими со стола богача, и псы, приходя, лизали струпья его.\\
Умер нищий и отнесен был Ангелами на лоно Авраамово. Умер и богач, и похоронили его.\\
И в аде, будучи в муках, он поднял глаза свои, увидел вдали Авраама и Лазаря на лоне его\\
и, возопив, сказал: отче Аврааме! умилосердись надо мною и пошли Лазаря, чтобы омочил конец перста своего в воде и прохладил язык мой, ибо я мучаюсь в пламени сем.\\
Но Авраам сказал: чадо! вспомни, что ты получил уже доброе твое в жизни твоей, а Лазарь - злое; ныне же он здесь утешается, а ты страдаешь;\\
и сверх всего того между нами и вами утверждена великая пропасть, так что хотящие перейти отсюда к вам не могут, также и оттуда к нам не переходят.\\
Тогда сказал он: так прошу тебя, отче, пошли его в дом отца моего,\\
ибо у меня пять братьев; пусть он засвидетельствует им, чтобы и они не пришли в это место мучения.\\
Авраам сказал ему: у них есть Моисей и пророки; пусть слушают их.\\
Он же сказал: нет, отче Аврааме, но если кто из мертвых придет к ним, покаются.\\
Тогда Авраам сказал ему: если Моисея и пророков не слушают, то если бы кто и из мертвых воскрес, не поверят.\\
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}
\textbf{Luke 16:19 -- 16:31.}\\
There was a certain rich man, which was clothed in purple and fine linen, and fared sumptuously every day:\\
And there was a certain beggar named Lazarus, which was laid at his gate, full of sores,\\
And desiring to be fed with the crumbs which fell from the rich man's table: moreover the dogs came and licked his sores.\\
And it came to pass, that the beggar died, and was carried by the angels into Abraham's bosom: the rich man also died, and was buried;\\
And in hell he lift up his eyes, being in torments, and seeth Abraham afar off, and Lazarus in his bosom.\\
And he cried and said, Father Abraham, have mercy on me, and send Lazarus, that he may dip the tip of his finger in water, and cool my tongue; for I am tormented in this flame.\\
But Abraham said, Son, remember that thou in thy lifetime receivedst thy good things, and likewise Lazarus evil things: but now he is comforted, and thou art tormented.\\
And beside all this, between us and you there is a great gulf fixed: so that they which would pass from hence to you cannot; neither can they pass to us, that would come from thence.\\
Then he said, I pray thee therefore, father, that thou wouldest send him to my father's house:\\
For I have five brethren; that he may testify unto them, lest they also come into this place of torment.\\
Abraham saith unto him, They have Moses and the prophets; let them hear them.\\
And he said, Nay, father Abraham: but if one went unto them from the dead, they will repent.\\
And he said unto him, If they hear not Moses and the prophets, neither will they be persuaded, though one rose from the dead.\\
\end{minipage}}
\newpage\huge
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 16:19 -- 16:31.}\\
「有一個財主穿着紫色袍和細麻布衣服，天天奢華宴樂。\\
又有一個討飯的，名叫 拉撒路，渾身長瘡，被人放在財主門口，\\
想得財主桌子上掉下來的碎食充飢，甚至還有狗來舔他的瘡。\\
後來那討飯的死了，被天使帶去放在 亞伯拉罕的懷裏。財主也死了，並且埋葬了。\\
他在陰間受苦，舉目遠遠地望見 亞伯拉罕，又望見 拉撒路在他懷裏，\\
他就喊着說：『我祖 亞伯拉罕哪，可憐我吧！請打發 拉撒路來，用指頭尖蘸點水，涼涼我的舌頭，因為我在這火焰裏，極其痛苦。』\\
亞伯拉罕說：『孩子啊，你該回想你生前享過福， 拉撒路也同樣受過苦，如今他在這裏得安慰，你卻受痛苦。\\
除此之外，在你們和我們之間，有深淵隔開，以致人要從這邊過到你們那邊是不可能的；要從那邊過到這邊也是不可能的。』\\
財主說：『我祖啊，既然這樣，求你打發 拉撒路到我父家去，\\
因為我還有五個兄弟，他可以警告他們，免得他們也來到這痛苦的地方。』\\
亞伯拉罕說：『他們有 摩西和先知的話可以聽從。』\\
他說：『不！我祖 亞伯拉罕哪，假如有一個人從死人中到他們那裏去，他們一定會悔改。』\\
亞伯拉罕對他說：『如果他們不聽從 摩西和先知的話，就是有人從死人中復活，他們也不會信服的。』」 \\
\end{CJK}
\end{minipage}}
\end{document}
