\documentclass[10pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[margin=0.75in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}

\title{Divine Liturgy\\Reading from The Gospels}
\date{Week 17 after the Pentecost}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\large\doublespacing
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 30 зач., VII, 11-16.}\\
После сего Иисус пошел в город, называемый Наин; и с Ним шли многие из учеников Его и множество народа.\\
Когда же Он приблизился к городским воротам, тут выносили умершего, единственного сына у матери, а она была вдова; и много народа шло с нею из города.\\
Увидев ее, Господь сжалился над нею и сказал ей: не плачь.\\
И, подойдя, прикоснулся к одру; несшие остановились, и Он сказал: юноша! тебе говорю, встань!\\
Мертвый, поднявшись, сел и стал говорить; и отдал его Иисус матери его.\\
И всех объял страх, и славили Бога, говоря: великий пророк восстал между нами, и Бог посетил народ Свой. 
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}
\textbf{Luke 7:11 -- 7:16.}\\
And it came to pass the day after, that he went into a city called Nain; and many of his disciples went with him, and much people.\\
Now when he came nigh to the gate of the city, behold, there was a dead man carried out, the only son of his mother, and she was a widow: and much people of the city was with her.\\
And when the Lord saw her, he had compassion on her, and said unto her, Weep not.\\
And he came and touched the bier: and they that bare him stood still. And he said, Young man, I say unto thee, Arise.\\
And he that was dead sat up, and began to speak. And he delivered him to his mother.\\
And there came a fear on all: and they glorified God, saying, That a great prophet is risen up among us; and, That God hath visited his people.\\
\end{minipage}}
\newpage\huge
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 7:11 -- 7:16.}\\
過了不久(註)，耶穌往一座城去，這城名叫 拿因，他的門徒和一大羣人與他同行。\\
當他走近城門時，有一個死人被抬出來。這人是他母親獨生的兒子，而他母親又是寡婦。城裏的許多人與她一同送殯。\\
主看見那寡婦就憐憫她，對她說：「不要哭。」\\
於是耶穌進前來，按着槓，抬的人就站住了。耶穌說：「年輕人，我吩咐你，起來！」\\
那死人就坐了起來，開始說話，耶穌就把他交給他的母親。\\
眾人都驚奇，歸榮耀給上帝，說：「有大先知在我們當中興起了！」又說：「上帝眷顧了他的百姓！」 
\end{CJK}
\end{minipage}}
\end{document}
