\documentclass[8pt]{article} % use larger type; default would be 10pt

%\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage[10pt]{type1ec}          % use only 10pt fonts
\usepackage[T1]{fontenc}
%\usepackage{CJK}
\usepackage{graphicx}
\usepackage{float}
\usepackage{CJKutf8}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{enumitem}

\newtheorem{prob}{Problem}

\newenvironment{solution}%
{\par\textbf{Solution}\space }%
{\par}

\title{Study Plan\\Submitted as a part of an\\Application Package for\\the Master of Philosophy Degree (Full-time)\\Inst. of Multimedia Engineering
 \\College of Computer Science\\National Chiao Tung University}
\author{Oleksii Leontiev}
\begin{document}
\begin{CJK}{UTF8}{bsmi}
\maketitle
\end{CJK}
%tell that I'm a student and how good NCTU is
Immediately after my graduation from the high school in Ukraine I've started my studies in National Chiao Tung University on Applied Math Department. These 4 years were the 
great time for me: I've learned Chinese and became accustomed to great Taiwanese culture, I took double degree in Computer Science and Mathematics and learned a lot of new
things in friendly academic atmosphere of NCTU. NCTU gave me a lot of opportunities in cultural sense (contact with foreign culture, especially as fascinating as Taiwanese,
left big imprint on me), in academic sense (NCTU was generous to me, providing me with rich opportunities, perfect education and scholarship on top of all this) and in
psychological aspect (naturally, I missed home in my first year and the friendly environment I've encountered in Taiwan helped me to bypass the pain).

%tell about my research with Prof Chuang and topic of research
As I mentioned above, academic environment in NCTU was very rich and giving. Besides getting full tuition waiver and scholarship, I had a chance to apply learned in classroom to
practical problems, by participating in various projects both on Math and Computer Science Departments. One of the most fascinating ones was a project with professor
\textbf{Jung Hong Chuang} of Computer Science Department, that I am happy to currently participate in. Professor Chuang, whose class I took while being
a junior, was tremendously supportive to me. His research in Computer Graphics and Computational Geometry is deep, his achievement and lab are well-known on the Department
and outside Taiwan as well. This research, being on edge between Mathematics and Computer Science, was a gift for me, due to its uniqueness.

%tell why this research is interesting for me
Since I am a double degree student, I am faced with a difficult choice between Math and Computer Science, as I am becoming graduate student and the amount of respected
inter-discipline programs is vanishingly small. Thus, I am even more happy to have chance to find such a precious research topic in the University that I am used to, with the 
Professor who I know very well, in country that I love after 4 years. Indeed, Professor Chuang's project on Computer Vision was a gift, and I feel myself much more
lucky than average bachelor student. It is an ability to apply my programming and math knowledge in practice, while doing something really useful. Moreover, this project
requires work in a lot of directions: point cloud registration (both rigid and non-rigid), surface reconstruction, filtering etc. All these are mathematical problems,
as well as real-life applications, and I'm happy that I've worked on this, and I would be happy to continue.

%tell about what I did and want to do
I believe that studying under Professor Chuang's guidance in rich academic international atmosphere of CS Department, I will grow fast enough to make something useful.
I am participating in this project for a year already and thus already have some small achievements,
such as implementation of Stochastic Rigid Registration algorithm of Chavdar Papazov
in C++ with PCL library. And I am eager to do more, if I will have an opportunity to join Jung Hong Chuang's lab. I realize, that my application package is not
perfect: Medical Certificate is not in place
and I did not provide original Bank Statement, just a copy. I would like an honorable committee to take into account, that I am currently abroad on exchange studies and
therefore have problems submitting some documents, that I did not prepare in advance. I hope my pledge will be heard and I will be allowed to postpone submission of
original documents, mentioned above.
\end{document}
