\documentclass[8pt]{article} % use larger type; default would be 10pt

\usepackage{mathtext}                 % підключення кирилиці у математичних формулах
                                          % (mathtext.sty входить в пакет t2).
\usepackage[T1,T2A]{fontenc}         % внутрішнє кодування шрифтів (може бути декілька);
                                          % вказане останнім діє по замовчуванню;
                                          % кириличне має співпадати з заданим в ukrhyph.tex.
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
                                          % може бути cp1251, koi8-u, macukr, iso88595, utf8.
\usepackage[english,ukrainian]{babel} % національна локалізація; може бути декілька
                                          % мов; остання з переліку діє по замовчуванню. 

%\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage[10pt]{type1ec}          % use only 10pt fonts
\usepackage[T1]{fontenc}
%\usepackage{CJK}
\usepackage{graphicx}
\usepackage{float}
\usepackage{CJKutf8}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{enumitem}

\newtheorem{prob}{Problem}

\newenvironment{solution}%
{\par\textbf{Solution}\space }%
{\par}

\title{Application Materials for\\Taiwan Scholarship 2013-2014
}
\author{Oleksii Leontiev}
\date{\selectlanguage{english}\today}

\begin{document}
\begin{CJK}{UTF8}{bsmi}
\maketitle
\end{CJK}

Dear Sir/Madam. Please, find attached:
\begin{enumerate}
	\item{Taiwan Scholarship Application Form (filled electronically on English, printed and signed).}
	\item{Copy of my passport (загранпаспорт), nationality: Ukraine.}
	\item{Recent transcript from National Chiao Tung University (in Hsinchu, Taiwan), where I'm currently a senior student.
		Note, that as a senior student, I do not have a graduation certificate yet,
		but I \textbf{expect to get it in June} and would like to ask for a postponement.}
	\item{Proof of application to university in Taiwan:
		\begin{enumerate}
			\item{Application to National Taiwan University - official Application Receipt, certifying that my application was received, passed the eligibility
				check and is now being processed.}
			\item{Application to National Chiao Tung University - screenshot of an Online Application System.}
		\end{enumerate}}%TODO
	\item{Copy of my TOEFL iBT score (112/120). Please, let me know if the original certificate is required.}
	\item{Copy of my Certificate of Chinese Language Proficiency (TOCFL, Level 3/5, grade 96/100).}
	\item{Two recommendation letters in sealed envelopes.}
	\item{This Supplementary Notice.}
\end{enumerate}
\end{document}
