\documentclass[8pt]{article} % use larger type; default would be 10pt

%\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage[10pt]{type1ec}          % use only 10pt fonts
\usepackage[T1]{fontenc}
%\usepackage{CJK}
\usepackage{graphicx}
\usepackage{float}
\usepackage{CJKutf8}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{enumitem}

\newtheorem{prob}{Problem}

\newenvironment{solution}%
{\par\textbf{Solution}\space }%
{\par}

\title{Application Package for\\the Master of Philosophy Degree (Full-time)\\ Graduate School of Mathematical Sciences
 \\The University of Tokyo}
\author{Oleksii Leontiev}

\begin{document}
\begin{CJK}{UTF8}{bsmi}
\maketitle
\end{CJK}

Dear Sir/Madam. Please, find attached:
\begin{enumerate}
	\item{Completed Application.}%TODO: fill
	\item{Curriculum Vitae.}%TODO: print
	\item{Copy of my passport (nationality: Ukrainian).}
	\item{My recent official transcript. Currently I am only fourth-year student, therefore I cannot provide the bachelor diploma yet.
		I expect to get it on June 2013.}
	\item{As I do not have bachelor diploma yet, I was said to provide a proof, that I will get the diploma in June. My University {will
		send this proof to Todai} separately later (in May).
		I realize that my application might not get processed before the aforementioned proof will arrive at Todai.}
	\item{Three Recommendation Letters in sealed envelopes will be sent to Tokyo University by my referees before the end of May.}
%		any other document which supports the applicant
	\item{Copy of my TOEFL iBT score (112/120). Original certificate was sent by me to Todai around September 2012.}
	\item{Copy of my Certificate of Chinese Language Proficiency (TOCFL, Level 3/5, grade 96/100).}
	\item{Note that although I do not have any Japanese Proficiency tests results now, I have been learning it for a year and I \textbf{will take
		a JLPT Level 4 test in July}.}
	%TODO: more merit documents
	\item{4 certificates of merit given to me by my Department (in traditional Chinese).}
	\item{One of my letter of awards with special scholarship (I received similar award each semester, based on result of competitive review during my studies).}
	\item{Commendation, certifying that I was award with the "Wiki Partnership Scholarship", funding my Computer Science diploma project, as a result of competitive
		selection.}
	\item{The proof of studies in Chiao Tung University with class ranking (1sh in class of 68 students).}
	%		details of the desired field of research with the proposed research program
	%		the names of the possible supervisors
%		a list of the articles written by the applicant with a photocopy of the articles (optional)
	\item{This Supplementary Note.}
\end{enumerate}

\end{document}
