\documentclass{elsarticle}

\usepackage{lineno,hyperref}
\usepackage{mathtext}
\usepackage{empheq}
\usepackage{mystyle}
\modulolinenumbers[5]

%custom theorem environments
\newtheorem{definition}{Definition}[section]
\renewcommand{\thedefinition}{\arabic{definition}}
\newtheorem{example}{\indent Example}[section]
\renewcommand{\theexample}{\arabic{example}}
\newtheorem{exercise}{Exercise}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{observation}{Observation}
\newtheorem*{fact}{Fact}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}[proposition]{Corollary}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

\journal{Journal of Mathematical Analysis and Applications}
\bibliographystyle{elsarticle-num}

\begin{document}

\begin{frontmatter}

\title{The new criterion for the roughness of exponential dichotomy on $\mathbb{R}$}

\author[todai]{Oleksii Leontiev\corref{cor}}
\ead{leontiev@ms.u-tokyo.ac.jp}
\author[erfurt]{Petro Feketa}
\ead{petro.feketa@gmail.com}

\cortext[cor]{Corresponding author}

\address[erfurt]{Erfurt University of Applied Sciences}
\address[todai]{The University of Tokyo}

\begin{abstract}
	It is well known (see \cite{coppel1978dichotomies})
	that system $x'=A(t)x$ possesses exponential dichotomy on $\mathbb{R}^+$ iff so does perturbed system
	$x'=(A(t)+B(t))x$, where perturbation $B(t)$ is ``small'', that is $\lim_{t\to+\infty}\mynorm{B(t)}=0$. However, it is also
	known that corresponding statement for exponential dichotomy on $\mathbb{R}$ fails.\\
	In this work we show that under additional hypothesis of commutativity of $A(s)$ and $B(t)$ for all $s,t\in\mathbb{R}$
	it can indeed be shown that dichotomy on $\mathbb{R}$ is unaffected by ``small'' perturbations (while ``small'' now
	has meaning of ``being in $L^1$ class'').\\
	We also provide some examples and particular corollaries of theory to show that hypotheses are natural and apply to wide
	range of problems.
\end{abstract}

\begin{keyword}
exponential dichotomy \sep perturbation theory \sep linear differential equations
\MSC[2010] 34D09\sep 34D10
\end{keyword}

\end{frontmatter}

\linenumbers

\section{Introduction}
Consider the system 
\[x'(t)=A(t)x(t)\]
where $x(t)$ and $A(t)$ are respectively vector-valued and square-matrix-valued functions defined for $t\in S\subseteq\mathbb{R}$.
In subsequent, we will impose conditions on $A(t)$, so that any initial value problem $x(t_0)=x_0,\;t_0\in S$ has a unique
continuous solution
that extends to the whole $S$. This will allow us to speak of the \textit{fundamental matrix} $\Omega_a^b(A)$, which is a linear map
that maps $x_0$ to $x(b)$, where $x(t)$ satisfies the aforementioned system and initial conditions
$x(a)=x_0$ (linearity follows from the homogeneity of
a system).
Now, the system is
 said to possess \textbf{"exponential dichotomy"} on $S$ (or simply "dichotomy" in subsequent), if the phase space $\R^n$
can be decomposed into the direct sum of subspaces
$E^+\oplus E^-$ and for arbitrary $x^+\in E^+,\; x^-\in E^-$ and $a,b\in S$ the following estimates hold:
\begin{equation}\begin{aligned}\label{DichotomyDef}
	\mynorm{\Omega^b_0(A)x^+}\leq K\mynorm{\Omega_0^a(A)x^+}\exp\left\{-\gamma\myabs{a-b}\right\},\;a\leq b\\
	\mynorm{\Omega^b_0(A)x^-}\leq K\mynorm{\Omega_0^a(A)x^-}\exp\left\{-\gamma\myabs{a-b}\right\},\;b\leq a\\
\end{aligned}\end{equation}
for some constants $K,\;\gamma>0$, that do not depend on $x^+,\;x^-,\;a,\;b$.

\begin{remark}The alternative definition, as given in \cite{coppel1978dichotomies} can be formulated as follows: there exist projection-operator $P$ and numbers
$K,\;\gamma>0$, such that
 for $\forall a,b\in S$
\[\mynorm{\Omega_0^a(A)P\mybra{\Omega_0^b(A)}^{-1}}\leq K e^{-\gamma(a-b)},\;a\geq b\]
\[\mynorm{\Omega_0^a(A)(I-P)\mybra{\Omega_0^b(A)}^{-1}}\leq K e^{-\gamma(b-a)},\;b\geq a\]
\end{remark}

The concept of exponential dichotomy plays an important role both in theory and applications. For instance
 in \cite{mitropolsky2002dichotomies},
 exponential dichotomy properties have been utilized
 for the investigation of multi-frequency oscillations and qualitative behavior of solutions of linear extensions of dynamical
 systems on torus. Roughness of exponential dichotomy (that is, its persistence under ``small'' perturbations) are the main
 properties that allow to apply this concept to the investigations of
 a variety of real-world phenomena and processes. This causes a particular relevance of research in this field. 

Coppell was one of the first to realise the importance of a concept. His monography
 \cite{coppel1978dichotomies} contains the exposition of how the dichotomy relates to basic concepts in systems of ODE, such as
roughness, Lypapunov functions and functional analysis aspects. It also encompasses the criteria for dichotomy and roughness
conditions, in particular that exponential dichotomy on any interval $J$ is \textit{not} affected when the perturbation $B(t)$
satisfies $\mynorm{B}_\infty:=\sup_{t\in J}\mynorm{B(t)}<\delta$, where $\delta$ is some fixed constant, depending on function $A$.
From there, this roughness result was worked upon by numerous researchers. For example, Palmer in
\cite{palmer1984exponential} has shown (among other results) that dichotomy on $[t_0,+\infty)$ is preserved under perturbation
$B(t)$ if $\lim_{t\to\infty}\mynorm{B(t)}=0$. The constant $\delta$ mentioned above was sharpened in
\cite{Naulin1998559}, where authors also have extended Coppel's roughness statement to the case when dichotomy constants
$K$ and $\gamma$ (see above) can be different for $E^+$ and $E^-$. Besides, in \cite{Ju200139}, authors tackled the case when
$A$ is assumed only locally integrable, not necessarily continuous or even bounded on $J$.

Although in this work we confine ourselves to the finite-dimensional setting, one can easily introduce the corresponding
exponential dichotomy theory to the case of operators on Banach spaces with many results and proofs carrying through. Then it
is fruitful to study the preservation of dichotomy under ``small'' (in some sense) perturbations in this new generalised setting.
Anyhow, we refer the interested reader to \cite{Popescu2006436} and references therein.

In this work we show that under additional hypothesis of commutativity of $A(s)$ and $B(t)$ for all $s,t\in\mathbb{R}$
it can indeed be shown that dichotomy on $\mathbb{R}$ is unaffected by ``small'' perturbations (while ``small'' now
has meaning of ``being in $L^1$ class).\\
We also provide some examples and particular corollaries of theory to show that hypotheses are natural and apply to wide
range of problems. Some comparison with previously known results will follow.

The rest of the paper is organized as follows: In section 2 we state our main result, section 3 is devoted to its proof.
In section 4 we have collected some corollaries and examples to highlight how our result relates to the previously known ones.
Finally, the last section concludes with a short discussion of a further work.
\section{Results}
%TODO: setting
In subsequent, all matrix functions will be assumed to be continuous. 
%%In principle, results probably can be extended to partially
%%give up this assumption, but for simplicity we shall keep it.
In particular, continuity assumption will let us immediately assume
that Cauchy problem for every ODE system $x'=A(t)x$ has a unique solution on $\mathbb{R}$ for any initial conditions.
\begin{proposition}
	\label{strong}
	Assume that for the two systems 
	\begin{equation}\label{Unperturbed}
	x'=A(t)x(t)
	\end{equation}
	and
	\begin{equation}\label{Perturbed}
	x'=(A(t)+B(t))x(t)
	\end{equation}
	the following two conditions hold:
	\begin{enumerate}[(H1)]
	\item For any $t,s\in\mathbb{R}$ matrices $A(s)$ and $B(t)$ commute;
	\item $B\in L^1(\mathbb{R})\cap C(\mathbb{R})$, that is $\int_{-\infty}^{\infty}\mynorm{B(s)}\;ds<\infty$.
	\end{enumerate}
	Then, \eqref{Perturbed} has exponential dichotomy on $\mathbb{R}$ if \eqref{Unperturbed} does.
\end{proposition}
%%\begin{remark}The boundedness hypothesis of the statement \ref{strong} (the second condition) holds in particular if
%%$\int_{-\infty}^\infty\mynorm{B(s)}\;ds<+\infty$ or $\lim_{\myabs{t}\to\infty}\mynorm{B(t)}=0$.
%%\end{remark}
\begin{remark}The hypothesis of the proposition \ref{strong} about the commutativity (the first condition) holds in particular if
	$\forall t,\;B(t)\in\bigcap\limits_{s\in\mathbb{R}} Z_{\mathfrak{gl}_n}(A(s))$, where
	$Z_{\mathfrak{gl}_n}(A)$ denotes the (Lie algebra) centralizer of $A$.
	If furthermore $A(t)\equiv A$, this condition can be simply rewritten as $\forall t,\;B(t)\in Z_{\mathfrak{gl}_n}(A)$.\end{remark}
\section{Proofs}
\begin{proof}{(of proposition \ref{strong}).\;}
The desired result will follow from two observations, which we shall state now and prove later. It should be noted that the observations have
weaker hypothesis than that of the proposition, and are useful results on their own.
\begin{observation}\label{Hard}Let $A$ and $B$ be continuous (not necessary bounded matrices-valued functions on $\mathbb{R}$). Assume further
that for every $s,t\in\mathbb{R}$ $A(s)$ and $B(t)$ commute. We shall also assume that for system $x'=Bx$, every Cauchy problem has a unique
solution on $\mathbb{R}$, in other words, that the fundamental matrix (we shall denote it by $X_B$) is well-defined on $\mathbb{R}$. Then,
for arbitrary $t,s\in\mathbb{R}$, $A(t)$ and $X_B(s)$ commute.
\end{observation}
\begin{observation}\label{Easy}Let $B$ be continuous matrix-valued function, such that $B\in L^1\cap C$. Then,
the fundamental matrix $X_B$ of $x'=Bx$ is well-defined on $\mathbb{R}$, and $\exists C\forall t,\;\mynorm{X_B(t)},\mynorm{X^{-1}_B
(t)}\leq C$.
\end{observation}
Assuming these two for the moment, let us see how the proof of the proposition can be obtained from them. Consider the $x'=Bx$ system, whose
fundamental matrix (existing by observation \ref{Easy}) we shall denote by $X_B$. Let us make the variable change $x=X_Bz$. Then, we have
\[BX_Bz+X_Bz'=(X_Bz)'=x'=(A+B)X_Bz\]
Now, as by observation \ref{Hard} $A$ and $X_B$ commute, we have
\[X_Bz'=X_BAz\]
thus $z$ is the solution to $z'=Az$, hence the fundamental matrix of $x'=(A+B)x$ has the structure
\[X_{A+B}=X_BX_A\]
Now, from \cite{coppel1978dichotomies} we know, that the exponential dichotomy on $\mathbb{R}$ can be defined as the existence of projection operator $P$
and numbers $\gamma,K>0$, such that $\forall s,t\in\mathbb{R}$ we have
\[\mynorm{X(t)PX^{-1}(s)}\leq Ke^{-\gamma(t-s)},\;s\leq t\]
\[\mynorm{X(t)(I-P)X^{-1}(s)}\leq K^{-\gamma(s-t)},\;t\leq s\]
We shall show, that this estimation remains the same for perturbed system \refeq{Perturbed} with the same $P$ and $\gamma$, but perhaps different $K$
. Indeed, we shall have
\[\mynorm{X_{A+B}(t)PX^{-1}_{A+B}(s)}=\mynorm{X_B(t)X_A(s)PX^{-1}_A(t)X^{-1}_B(t)}\leq\]
\[\leq\mynorm{X_B(t)}\cdot\mynorm{X_A(s)PX^{-1}_A(t)}\cdot\mynorm{X^{-1}_B(t)}\leq \underbrace{KC^2}_{=:\tilde{K}}e^{-\gamma(t-s)}.\]
The second inequality is worked out in the same way, so it just remains to prove the observations stated above.
\end{proof}
\begin{proof}{(of the observation \ref{Easy}).\;}The existence of fundamental matrix follows immediately from the continuity assumption. The uniform
boundedness of $\mynorm{X_B}$
 follows from the \cite[Corollary 3.24]{teschlordinary} (which states that if the system $x'=Cx$ with $C$ constant is uniformly stable and
 $B\in L^1\cap C$, then $x'=(C+B)x$ is stable as well; in our case we take obviously stable system $x'=0\cdot x$ as $x'=Cx$)
 . We shall denote the upper bound obtained for $X_B$ by $M$. It is
sufficient to show that $\mynorm{X^{-1}_B(t)}\leq M$. Let us fix $\tau\in\mathbb{R}$. $X^{-1}_B(\tau)$ can be characterized as $X^{-1}_B(\tau)x(\tau)
=x(0)$, where $x$ is the solution to $x'=Bx$ or as $X^{-1}(\tau)y(0)=y(-\tau)$, where $y'=\tilde{B}y$ and $\tilde{B}(t):=B(t+\tau)$. Thus,
it's enough to show that the norm of $X_{\tilde{B}}$ is uniformly bounded by $M$ as well. The latter, however, follows from the proof
of \cite[Corollary 3.24]{teschlordinary}, as the upper bound obtained there really depends only on the
$\int_{-\infty}^\infty\mynorm{\tilde{B}(s)}\;ds=\int_{-\infty}^\infty\mynorm{B(s)}\;ds$.\end{proof}
\begin{proof}{(of the observation \ref{Hard}).\;}
We shall employ the theory of Magnus expansion, described in \cite{Moan:2008:CMS:1391929.1391932}. For convenience, we collect
the properties we need in the following proposition
\begin{fact}{(\textbf{Magnus Expansion, see \cite{Moan:2008:CMS:1391929.1391932})}}
	Assume that we have a system $x'=Bx$ with continuous $B$ and fundamental matrix $X$. Assume
	further that for $T$ we have
	\[\myabs{\int_0^T\mynorm{B(s)}\;ds}<\pi\]
	then, on $t\in[0,T)$ $X(t)=\exp(\Omega(t))$, where $\Omega(t)=\sum\limits_{k=1}^\infty\Omega_k(t)$ and $\Omega_k(t)$ is an integral
	of commutators of increasing length, such as
	\begin{align*}
	\Omega_1(t) &= \int_0^t B(t_1)\,dt_1, \\
	\Omega_2(t) &= \frac{1}{2}\int_0^t dt_1 \int_0^{t_1} dt_2\ \left[  B(t_1),B(t_2)\right], \\
	\Omega_3(t) &= \frac{1}{6} \int_0^t dt_1 \int_0^{t_1}d t_2 \int_0^{t_2} dt_3
	\Bigl(\left[B(t_1),\left[B(t_2),B(t_3)\right]\right]+\left[B(t_3),\left[  B(t_2),B(t_{1})\right]\right]\Bigr), \\
	\Omega_4(t) &= \frac{1}{12} \int_0^t dt_1 \int_0^{t_1}d t_2 \int_0^{t_2} dt_3 \int_0^{t_3} dt_4
	\Bigl(\left[\left[\left[B_1,B_2\right],B_3\right],B_4\right] \\
	&\quad+\left[B_1,\left[\left[B_2,B_3\right],B_4\right]\right]
	+\left[B_1,\left[B_2,\left[B_3,B_4\right]\right]\right]
	+\left[B_2,\left[B_3,\left[B_4,B_1\right]\right]\right]\Bigr)
	\end{align*}
\end{fact}
Having this, we shall fix $\tau\in\mathbb{R}$ and show that for any $t\in\mathbb{R}$,
\[\mysbra{A(\tau),X_B(t)}=0\]
where $\mysbra{\cdot,\cdot}$ denotes the Lie bracket. As for $t=0$ the equality holds (as $X(0)=I$ commutes with all matrices), it is enough
to show that the set where equality holds is both open and closed. As both $A$, $X$ and Lie bracket are continuous, closedness follows and it
remains thus to show, that if $\mysbra{A(\tau),X(t_0)}=0$, then equality also holds on a small neighborhood of $t_0$.

It is sufficient to show that $A(\tau)$ commutes with $\tilde{X}(s):=X(t_0+s)X^{-1}(t_0)$ for small $s$. Now, $\tilde{X}$ can be realized
as a fundamental matrix of $x'=\tilde{B}x$, where $\tilde{B}(t)=B(t+t_0)$. Thus, without loss of generality we may assume that
$t_0=0$. Now, on the small
neighborhood of $0$ the hypothesis of ~\hyperref[MagnusConvergenceFact]{fact} is satisfied, hence we may apply Magnus expansion.

Now, if $A$ and $B$ commute with $C$, then so do $A\pm B$, $AB$ and $[A,B]$. Also, if $B(t)$ commutes with $A$ for all $t$, then so does
$\int_a^bB(s)\;ds$. Thus, we see that every $\Omega_k(t)$ commutes with $A(\tau)$, as former is the integral of commutators of $B$. Finally,
as Lie bracket is continuous, we also have that $\Omega(t)$ commutes with $A(\tau)$ whenever well-defined, and so does $X(t)=\exp(\Omega(t))=
\sum_{n=0}^\infty\frac{\Omega^n(t)}{n!}$.
\end{proof}
\section{Corollaries and Examples}
We recall the often used in analysis space of test functions, called \textit{Schawrtz space}. These are characterized
as $\mysetn{f\in C^{\infty}(\mathbb{R}^n)}{\forall \alpha,\beta,\quad\sup_x\myabs{x^\alpha D^\beta f(x)}<\infty}$,
where $\alpha$ and $\beta$ runs over all multi-indices. The definition is obviously adapted to matrix-valued functions.
Schwartz space is easily shown to be strictly bigger than the more often used space of $C^\infty$ functions with compact support.
As it is a well-known fact that Schwartz functions are $L^1$, we have the following.
\begin{corollary}
	If $x'=A(t)x(t)$ is system with exponential dichotomy on $\R$ $B(t)$ is matrix valued function, such that $\forall s,t\in\R$
	$A(t)$ and $B(s)$ commute, then perturbed system $x'=(A(t)+B(t))x(t)$ has also exponential dichotomy, once $B(t)$ is a member
	of a Schwartz space.
\end{corollary}
As Schwartz functions are so commonly encountered nowadays in analysis, we hope this corollary to be of some interest and use.

Another way to produce interesting corollaries may be on contrary, to \textit{strengthen} commutativity hypothesis of Proposition
\ref{strong}. In this direction the following may be of interest
\begin{corollary}
	If $x'=cx$ is system with exponential dichotomy, where $c$ is constant (that is the same as require $\Re c\neq0$)
	, then for \textit{any} matrix-valued $L^1$ function $B(t)$ perturbed system has also dichotomy.
\end{corollary}
It should be noted that this corollary is \textit{not} a direct corollary of well-known result 
\cite[Corollary 3.21]{teschlordinary}. Indeed, that result states that asymptotical stability is unaffected by 
$o(1)$-perturbations (that is, such that $\lim_{t\to\pm\infty}\mynorm{B(t)}=0$), while previous corollary states that
it is unaffected by $L^1$ perturbations (indeed, for $x'=cx$ exponential dichotomy is the same as forward/backward asymptotic
stability). As neither of classes $o(1)$ and $L^1$ is not a subset of other, last corollary is no direct implication of
\cite[Corollary 3.21]{teschlordinary}.

To conclude, we shall demonstrate one example, showing how our derived results are stronger than the original theorem of Palmer in
\cite{palmer1984exponential} 
\begin{example}
	Consider the two-dimensional system
	\[\begin{bmatrix}\dot{x}\\\dot{y}\end{bmatrix}=
		\begin{bmatrix}1&0\\0&-1\end{bmatrix}
	\begin{bmatrix}{x}\\{y}\end{bmatrix}\]
	It obviously has a dichotomy on $\R$. Now, perturb it to get
	\[\begin{bmatrix}\dot{x}\\\dot{y}\end{bmatrix}=
		\begin{bmatrix}1+P(x,y)e^{-x^2-y^2}&0\\0&-1+Q(x,y)e^{-x^2-y^2}\end{bmatrix}
	\begin{bmatrix}{x}\\{y}\end{bmatrix},\]
	where $P(x,y)$ and $Q(x,y)$ are arbitrary polynomials in $x$ and $y$.

	Then, our theorem shows that perturbed system still possess the dichotomy on $\R$ (as we've perturbed by Schwartz function, see above),
	while Palmer's theorem only allows one to conclude that the dichotomy on $\pm\R$ is preserved.
\end{example}
\section{Further work}%FIXME: 
The proposition we have shown together with its corollaries listed can be possibly extended to other classes of differential equations
, whenever the concept of exponential dichotomy is of relevance to them. In particular new results and corresponding proof techniques
could be applied to the investigations of the existence of invariant toroidal manifolds of multi-frequency systems, for
 which the exponential dichotomy plays an essential role (see \cite{samoilenko2012elements,mitropolsky2002dichotomies} for details).
\section*{References}
\bibliography{thesis_paper}

\end{document}
%cor: intro -->keywords --> further work
%cor: cors_and_examps: Schwartz, diagonal matrices --> ask feketa --> no o(1) counter-example

%%\bibitem{krein}
%%Ю. Л. Далецкий, М. Г. Крейн
%%\emph{Устойчивость решений дифференциальных уравнений в банаховом пространстве}.
%%Видавництво "Наука"{}, Головна редакція фізико-математичної літератури. Москва, 1970.
%%\bibitem{mitrop}
%%Митропольський Ю. А., Самойленко А. М., Кулик В. Л.
%%\emph{Исследование дихотомии линейных систем дифференциальных уравнений с помощью функций Ляпунова}.
%%АН УССР. Ін-т математики. Київ, "Наукова думка", 1990.
%%\bibitem{palmer84}
%%	Kenneth J. Palmer, {\em Exponential Dichotomies and Transversal Homoclinic Points} (1983).
%%\bibitem{palmer88}
%%	Kenneth J. Palmer, {\em Exponential Dichotomies and Fredholm Operators} (1988).
%%\bibitem{ju}
%%	Ning Ju and Stephen Wiggins, {\em On Roughness of Exponential Dichotomy} (2000).
%%\bibitem{naulin}
%%	Ra\'ul Naulin and Manuel Pinto, {\em Admissible perturbations of Exponential Dichotomy Roughness} (1997).
%%\bibitem{chow}
%%	Shui-Nee Chow and Hugo Leiva, {\em Existence and Roughness of the Exponential Dichotomy for Skew-Product Semiflow in Banach Spaces} (1994).
%%\bibitem{demidovich}
%%Demidovich B. P. \emph{Lectures on the mathematical theory of stability} --
%%Moscow (1967) (in Russian).

% http://people.cs.nctu.edu.tw/~inp9822058/thesis_paper.pdf
