\documentclass[8pt]{beamer}
\mode<presentation>{\usetheme{Warsaw}}
\usepackage{mystyle}
\usepackage{amsmath}

\newcommand{\red}[1]{{\color[rgb]{0.6,0,0}#1}}
\newcommand{\Sol}{\mbox{Sol}}

\makeatletter
\def\th@mystyle{%
    \normalfont % body font
    \setbeamercolor{block title example}{bg=orange,fg=white}
    \setbeamercolor{block body example}{bg=orange!20,fg=black}
    \def\inserttheoremblockenv{exampleblock}
  }
\makeatother
\theoremstyle{mystyle}
\newtheorem*{remark}{Remark}

\title{Presentation on the Master Thesis Preparation}
\subtitle{Alex Leontiev}

\begin{document}
\begin{frame}\titlepage\end{frame}
\begin{frame}{$P'/G\backslash P$}
	\begin{theorem}[Kobayashi-Speh]\[G/P=P'[q_+]\sqcup P'[p_+]\sqcup P'[p_+]=
		(S^n-S^{n-1})\sqcup (S^{n-1}-{p_+})\sqcup p_+\]
		and these are pulled back to $\R^n-\R^{n-1}$, $\R^{n-1}-0$ and $0$ respectively via Bruhat parametrization and
		only the first one is open dense in $\R^n$.
\end{theorem}
\begin{theorem}[$O(p,q),\;n:=(p-1)+(q-1)$]
	\[G/P=P'[0_{p-1},1,0_{q-1},1]\sqcup P'[q+]\sqcup P'[0_{p-2},1,0,1,0_{q-1}]\sqcup P'[p_+]\sqcup P'[p_-]\]
	and these are pulled back to $\R^n-A-B,\;B-A,\;A\cap B-{0},\;{0}$ and $A-B$ respectively via Bruhat parametrization and
		only the first one is open dense in $\R^n$.
Here $A:=\mycbra{x_{p-1}=0}$ and $B:=\mysetn{(x,y)\in\R^{p-1,q-1}}{\myabs{x}_{p-1}=\myabs{y}_{q-1}}$ closed subsets of $\R^n$.
\end{theorem}
\end{frame}
\begin{frame}{Equations for kernels}
\begin{theorem}[Kobayashi-Speh]Kernel of symmetry breaker is distribution $F$ on $\R^n$ satisfies
	\[E-(\lambda-\nu-n))F=0\quad\mbox{($A'$-action)}\]
\[(2\nu x_j+(\myabs{x}^2+x_n^2)\frac{\partial}{\partial x_j})F=0,\;1\leq j\leq n-1\quad\mbox{($N_+'$-action)}\]
\[F(mx,x_n)=F(x,x_n),\;\forall m\in O(n-1)\quad\mbox{($M'$-action)}\]
\[F(-\tilde{x})=F(\tilde{x})\quad\mbox{($M'$-action)}\]
\end{theorem}
\begin{theorem}[O(p,q), $Q(\cdot)$ denotes indefinite $(p-1,q-1)$-norm on $\R^{ p,q }$]Kernel of symmetry breaker is distribution $F$ on $\R^{(p-1)+(q-1)}=:\R^n$ satisfies
\[E-(\lambda-\nu-n))F=0\quad\mbox{($A$-action)}\]
\[(2\epsilon_j\nu x_j+Q(x)\frac{\partial}{\partial x_j})F=0,\;1\leq j\leq n,\;j\neq p-1\quad\mbox{
($N'_+$-action)}\]
\[F(x,x_{p-1},y)=F(x',x_{p-1},y'),\;(x',y'):=m(x,y)\;\forall m\in O(p-2,q-1)\quad\mbox{($M'$-action)}\]
\[F(-\tilde{x})=F(\tilde{x})\quad\mbox{($M'$-action)}\]
\end{theorem}
\end{frame}
\begin{frame}{Differential symmetry breaking operators}
\begin{theorem}[Kobayashi-Speh]
	Differential symmetry breakers exist only when $\lambda-\nu=0,-2,-4,\hdots$ and in that case space of
	differential symmetry breaking operators is one-dimensional (given by Gegenbauer polynomial)
\end{theorem}
\begin{theorem}[$O(p,q),\;n:=(p-1)+(q-1)$]
	literally the same
\end{theorem}
\end{frame}
\begin{frame}{Lemma 6.7}
	The lemma deals with the exact sequence
	\[0\rightarrow \Sol_{\mycbra{0}}(\R^n)\rightarrow \Sol(\R^n)\rightarrow\Sol(\R^n-\mycbra{0})\]
	more precisely, it explicitly constructs basis for the rightmost term.
In my opinion, it is important to the whole argument. It's purpose is twofold:
\begin{enumerate}
	\item it gives good upper estimates on dimension of symmetry breakers for all parameters (unlike, given by say [Sun-Zhu]),
		which can later be refined by showing that the rightmost morphism is zero map.
	\item it provides clue about how kernels of symmetry breaking operators should look like, by showing how solutions should
		look like when problem is restricted to open dense subset.
\end{enumerate}
\end{frame}
\begin{frame}{Lemma 6.7}
\begin{theorem}[Kobayashi-Speh]
	\[\Sol(\R^n-\mycbra{0})=\C g(x_n)(\myabs{x}^2+x_n^2)^{-\nu}\], where
	\[\mathcal{D}'(\R)\ni g(x):=\left\{\begin{array}{ll}
				x_+^{\lambda+\nu-n}+x_-^{\lambda+\nu-n}&\mbox{if }\lambda+\nu-n\neq-1,-3,-5,\hdots\\
				\delta^{-\lambda-\nu+n-1}(x)&\mbox{if }\lambda+\nu-n\in\mycbra{-1,-3,-5,\hdots}\\
		\end{array}\right.\]
\end{theorem}
Let $Q(\cdot)$ be indefinite $(p-1,q-1)$ norm on $\R^{p-1,q-1}$.  
Trying to mimic the logic of [Kobayashi-Speh] we are led to consider the exact sequence
\[0\rightarrow \Sol_{\mycbra{Q=0}}(\R^n)\rightarrow \Sol(\R^n)\rightarrow\Sol(
	\mycbra{Q\neq0})\]
\begin{theorem}[$O(p,q),\;n:=(p-1)+(q-1)$]
	\[\Sol(\mycbra{Q\neq0})=\Sol(\mycbra{Q<0})\oplus \Sol(\mycbra{Q>0})\]
	\[\Sol(\mycbra{Q>0})=\C g(x_p)\myabs{Q(x)}^{-\nu}\big|_{Q>0},\mbox{ if }p-1>1\]
	\begin{multline*}\Sol(\mycbra{Q>0})=\C \myabs{x_p}^{\lambda+\nu-n}\myabs{Q(x)}^{-\nu}\big|_{Q>0},\mbox{ if }p-1=1\\
	\mbox{(here $\myabs{x_p}^{\lambda+\nu-n}$ is the regular functional on $\R-\mycbra{0}$)}\end{multline*}
	\[\Sol(\mycbra{Q<0})=\C\myabs{Q(x)}^{-\nu}g(x_p)\big|_{Q<0}\]
\end{theorem}
\end{frame}
\begin{frame}{Lemma 6.7}
	Trying to understand $Sol_{\mycbra{Q=0}}(\R^n)$ we are led to another exact sequence
	\[0\rightarrow\Sol_{\mycbra{0}}(\R^n)\rightarrow\Sol_{\mycbra{Q=0}}(\R^n)\rightarrow
	\Sol_{\mycbra{Q=0}-\mycbra{0}}(\R^n-\mycbra{0})\]

\begin{theorem}
	If $\nu\notin\Z_{ >0 }$ we have $\Sol_{\mycbra{Q=0}-\mycbra{0}}(\R^n-\mycbra{0})=0$. Otherwise,
	in $(\mu,s,\omega_{ p-2 },\omega_{ q-2 })$ coordinates\footnotemark
	$\Sol_{\mycbra{Q=0}-\mycbra{0}}(\R^n-\mycbra{0})=\C\delta^{ (\nu-1) }(\mu-1)
	\otimes s^{-\nu }u$, where $u\in\mathcal{ D }'(\R_{ >0 }\times\mathbb{ S }^{ p-2 })$
	is a pullback of $g(x_{ p-1 })$ via the polar coordinate change\footnotemark
\end{theorem}
\begin{remark}
	For fixed $\nu\in\Z_{ >0 }$
	the non-trivial element of $\Sol_{\mycbra{Q=0}-\mycbra{0}}(\R^n-\mycbra{0})$ for $\lambda\in\C$ such that 
	$\Re(\lambda+\nu)>n-1$ and $\Re(\lambda-\nu)>0$ can be extended to the generalized function on the whole $\R^n$,
	which satisfies the equations.
\end{remark}
\footnotetext{ $\R^{ p-1}\times\R^{ q-1 }\ni(x,y)=(\sqrt{ s }\omega_{ p-2 },\sqrt{ \mu s }\omega_{ q-1 })$}
\footnotetext{ $\R^{ p-1}\setminus\mycbra{ 0 }\ni x=\sqrt{ s }\omega_{ p-1 }$}
\end{frame}
\begin{frame}{$K$-finite vectors in non-compact picture}
\begin{theorem}[Kobayashi-Speh; Proposition 4.3]
	The $K$-finite vectors in non-compact picture are equal to
	\[\C\myabra{ F_\lambda[\psi,h]:N\in\Z_{ \geq0 },\;\psi\in\mathcal{ H }^N(\mathbb{ S }^{ n-1 }),\;h\in\C[s] }.\]
	where
	\[F_\lambda[\psi,h](r\omega):=(1+r^2)^{ -\lambda }\mybra{ \frac{ 2r }{ 1+r^2 } }^N\psi(\omega)h\mybra{\frac{ 1-r^2 }{1+r^2}}\]
\end{theorem}
\begin{theorem}[$O(p,q),\;n:=(p-1)+(q-1)$]
	The $K$-finite vectors in non-compact picture are contained in
	\[\C\myabra{ F_\lambda[\psi,\psi',N,M,n',m']:N,M,n',m'\in\Z_{ \geq0 },
	\;\psi\in\mathcal{ H }^N(\mathbb{ S }^{ p-2 }),\;\psi'\in\mathcal{ H }^M(\mathbb{ S }^{ q-2 }) }.\]
	where
	\[F_\lambda[\psi,\psi',N,M,n',m'](r\omega_{ p-1 },r\sqrt{ \mu }\omega_{ q-1 }):=\]
	\[:=R(r,\mu)^\Theta\psi(\omega_{ p-1 })\psi'(\omega_{ q-1 })(2r)^{ M+N }\mu^{ M/2 }(1-r^2(1-\mu))^{ n' }(1+r^2(1-\mu))^
	{m'}\]
	where
	\[\Theta:={ -\lambda/2-N/2-n'/2-M/2-m'/2 }\]
	\[R(r,\mu)=1+2(1+\mu)r^2+(\mu-1)^2r^4\]
\end{theorem}
\end{frame}
\begin{frame}{normalization $\tilde{K}_{ \lambda,\nu }$}
\begin{theorem}[Kobayashi-Speh; Proposition 7.3]
	Set $\tilde{K}^{\mathbb{ A }}_{ \lambda,\nu }:={{K}^{\mathbb{ A }}_{ \lambda,\nu }}/\Gamma(\frac{ \lambda+\nu-n+1 }{2})/
	\Gamma(\frac{ \lambda-\nu }{ 2 })$. Then $\forall f\in C^{ \infty }(S^n)_K$ we have $
	\myabra{\tilde{K}^{\mathbb{ A }}_{ \lambda,\nu },f}$ being holo on $\mathbb{ C }^2$. Moreover, $\mysbra{\forall f\in C^{ \infty }(S^n)
	_K,\;\myabra{\tilde{K}^{\mathbb{ A }}_{ \lambda,\nu },f}=0}\iff (\lambda,\nu)\in L_{ \mbox{even} }$
\end{theorem}
\begin{theorem}[$O(p+1,q+1),\;n:=p+q$]
	Let $K_{ \lambda,\nu }$ be the nontrivial element of $Sol_{\mycbra{Q=0}-\mycbra{0}}(\R^n)$
	and normalize it as $\tilde{ K }_{ \lambda,\nu }
	:=K_{ \lambda,\nu }/\Gamma(\frac{ \lambda+\nu-1-q }{ 2 })/\Gamma(\frac{ \lambda+ \nu-p+1}{ 2 })$
	if $q$:even and $2\nu\geq q$ and 
	$:=K_{ \lambda,\nu }/\Gamma(\frac{ \lambda-\nu-1 }{ 2 })/\Gamma(\frac{ \lambda+ \nu-p+1}{ 2 })$ otherwise.
	Then $\forall F_\lambda[\psi,\psi',N,M,n',m']$ we have $\myabra{ \tilde{ K }_{ \lambda,\nu }, F_\lambda[\psi,\psi',N,M,n',m']}
	$ being holo in $\lambda$. Moreover, $\forall (\lambda,\nu)\in\C\times\mathbb{ Z }_{ >0 },\;\tilde{ K }_{ \lambda,\nu }\neq0$.
\end{theorem}
\begin{remark}
	Proof is done modulo the hypothesis %TODO: formulate the hypo
	that seems to agree with the experimental data.
\end{remark}
\end{frame}
\begin{frame}{meromorphic extension of ${K}_{ \lambda,\nu }$}
\begin{theorem}[Kobayashi-Speh; Lemma 8.2]
	\[\frac{ \partial }{ \partial x_n }K^+_{ \lambda+1,\nu }=(\lambda+\nu-n+1)K^+_{ \lambda,\nu }-2\nu K^+_{ \lambda,\nu +1}\]
	\[\Delta_{ n-1 }K^+_{ \lambda+1,\nu-1 }=2(\nu-1)(2\nu-n+1)K^+_{ \lambda,\nu }-4(\nu-1)K^+_{\lambda+1,\nu+1  }\]
\end{theorem}
\begin{theorem}[$O(p+1,q+1),\;n:=(p)+(q)$]
	\[\frac{ \partial }{ \partial x_p }K^+_{ \lambda,\nu }=-2K_{ \lambda,\nu+1 }+(\lambda+\nu-n)K_{ \lambda,\nu }\]
	\[\Delta_{ p-1,q }K^+_{ \lambda+1,\nu-1 }=4\nu K^+_{ \lambda,\nu+1 }-4K^+_{ \lambda,\nu+2 }\]
\end{theorem}
\end{frame}
\begin{frame}{Further work}%TODO
	Possible approaches:
	\begin{itemize}
		\item Continue to mimic the argument in [Kobayashi-Speh]
			\begin{enumerate}
				\item verify that the regularization of non-trivial element of $\Sol_S(\R^n\setminus\mycbra{ 0 })$
					is indeed a kernel of an intertwiner
				\item see how it acts on $K$-finite vectors and where the poles are
				\item Renormalize it and analytically continuate it to the kernel of 
					regular symmetry breaking operator with support in $S$
				\item use logic similar to Prop 11.12 and Prop 11.13 in [Kobayashi-Speh] to 
					the question of when the last morphism
	$0\rightarrow\Sol_{\mycbra{0}}(\R^n)\rightarrow\Sol_{\mycbra{Q=0}}(\R^n)\rightarrow
	\Sol_{\mycbra{Q=0}-\mycbra{0}}(\R^n-\mycbra{0})$
	is onto
				\item go on to consider 
				$0\rightarrow\Sol_{\mycbra{ Q=0 }}(\R^n)\rightarrow\Sol(\R^n)\rightarrow
				\Sol(\mycbra{Q\neq0})$
			\end{enumerate}
		\item F-method
			\begin{enumerate}
				\item {[done]} perform algebraic Fourier transform on the defining equations for kernel of symmetry
					breaker. The only equation which will change substantially is the $N_+'$-action. It will
					become second order PDE.
				\item Read books [Slavyanov] and [Smirnov] suggested by Prof. Pevzner to find (maybe) and solve
					equations for $N_+'$ action.
				\item filter out among solutions to $N_+'$ action equations those that also satisfy $M'$ and $A'$
					invariance.
				\item make inverse algebraic Fourier transform to get explicit form of kernels
			\end{enumerate}
		\item Apply [Sun-Zhu]
			\begin{enumerate}
				\item Use data in [Howe-Tan] to find for fixed $(p,q)$ for which values of $(\lambda,\nu)$ both
					$I(\lambda)$ is irreducible for $O(p,q)$ and $J(\nu)$ for $O(p-1,q)$.
				\item Use the result [Sun-Zhu] to conclude that for those cases dimension of symmetry breakers
					is no more than one.
				\item Improve the upper bound to precise and construct explicit symmetry breakers in those cases.
				\item see what we are left with
			\end{enumerate}
	\end{itemize}
\end{frame}
\begin{frame}{Questions (which I'll answer myself)}
	\begin{enumerate}
		\item Understand the proof of Prop 11.12 of [Kobayashi-Speh]
		\item Understand the proof of Prop 11.7 of [Kobayashi-Speh]
	\end{enumerate}
\end{frame}
\begin{frame}{References}
	\begin{itemize}
		\item {[Sun-Zhu]} Sun, Binyong, and Chen-Bo Zhu. "Multiplicity one theorems: the Archimedean case." 
			{\it arXiv preprint arXiv:0903.1413 (2009)}.
		\item {[Kobayashi-Speh]} Kobayashi, Toshiyuki, and Birgit Speh. "Symmetry breaking for representations of rank one orthogonal groups." (2015).
		\item {[Slavyanov]} Slavianov, S.I.U. \&
			Lay, W. (2000). {\it Special Functions: A Unified Theory Based on Singularities}. Oxford University Press
		\item {[Smirnov]} Smirnov, V.I. (1964). {\it A Course of Higher Mathematics}.
			Pergamon Press; [U.S.A. ed. distributed by Addison-Wesley Publishing Company, Reading, Mass.
			\item {[Howe-Tan]} Howe, Roger E., and Eng-Chye Tan. "Homogeneous functions on light cones: the infinitesimal structure of some degenerate principal series representations." Bulletin of the American Mathematical Society 28.1 (1993): 1-74.
		\item {[Gelfand-Shilov I]} Gelfand, I.M. \& Shilov, G.E. (1969).
				{\it Generalized Functions. Vol. 1: Properties and Operations}. New York
	\end{itemize}
\end{frame}
\end{document}
