\documentclass[12pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 35 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Кол., 258 зач., III, 12-16.}\\
\Large%for eng/rus
Итак облекитесь, как избранные Божии, святые и возлюбленные, в милосердие, благость, смиренномудрие, кротость, долготерпение,
\\
снисходя друг другу и прощая взаимно, если кто на кого имеет жалобу: как Христос простил вас, так и вы.
\\
Более же всего облекитесь в любовь, которая есть совокупность совершенства.
\\
И да владычествует в сердцах ваших мир Божий, к которому вы и призваны в одном теле, и будьте дружелюбны.
\\
Слово Христово да вселяется в вас обильно, со всякою премудростью; научайте и вразумляйте друг друга псалмами, славословием и духовными песнями, во благодати воспевая в сердцах ваших Господу.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Colossians 3:12--3:16.}\\
Put on therefore, as the elect of God, holy and beloved, bowels of mercies, kindness, humbleness of mind, meekness, longsuffering;\\
Forbearing one another, and forgiving one another, if any man have a quarrel against any: even as Christ forgave you, so also do ye.\\
And above all these things put on charity, which is the bond of perfectness.\\
And let the peace of God rule in your hearts, to the which also ye are called in one body; and be ye thankful.\\
Let the word of Christ dwell in you richly in all wisdom; teaching and admonishing one another in psalms and hymns and spiritual songs, singing with grace in your hearts to the Lord.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{歌羅西書 3:12--3:16.}\\
所以你們既是　神的選民、聖潔蒙愛的人、就要存〔原文作穿下同〕憐憫、恩慈、謙虛、溫柔、忍耐的心。\\
倘若這人與那人有嫌隙、總要彼此包容、彼此饒恕．主怎樣饒恕了你們、你們也要怎樣饒恕人。\\
在這一切之外、要存著愛心．愛心就是聯絡全德的。\\
又要叫基督的平安在你們心裡作主．你們也為此蒙召、歸為一體．且要存感謝的心。\\
當用各樣的智慧、把基督的道理、豐豐富富的存在心裡、〔或作當把基督的道理豐豐富富的存在心裡以各樣的智慧〕用詩章、頌詞、靈歌、彼此教導、互相勸戒心被恩感歌頌　神。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
