\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 5 of the Great Lent\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\onehalfspacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Евр., 321 зач. (от полу́), IX, 11-14.}\\
\Large%for eng/rus
Но Христос, Первосвященник будущих благ, придя с большею и совершеннейшею скиниею, нерукотворенною, то есть не такового устроения,
\\
и не с кровью козлов и тельцов, но со Своею Кровию, однажды вошел во святилище и приобрел вечное искупление.
\\
Ибо если кровь тельцов и козлов и пепел телицы, через окропление, освящает оскверненных, дабы чисто было тело,
\\
то кольми паче Кровь Христа, Который Духом Святым принес Себя непорочного Богу, очистит совесть нашу от мертвых дел, для служения Богу живому и истинному!
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Hebrews 9:11--9:14.}\\
But Christ being come an high priest of good things to come, by a greater and more perfect tabernacle, not made with hands, that is to say, not of this building;\\
Neither by the blood of goats and calves, but by his own blood he entered in once into the holy place, having obtained eternal redemption for us.\\
For if the blood of bulls and of goats, and the ashes of an heifer sprinkling the unclean, sanctifieth to the purifying of the flesh:\\
How much more shall the blood of Christ, who through the eternal Spirit offered himself without spot to God, purge your conscience from dead works to serve the living God?\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.5}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{希伯來書 9:11--9:14.}\\
但現在基督已經來到、作了將來美事的大祭司、經過那更大更全備的帳幕、不是人手所造也不是屬乎這世界的．\\
並且不用山羊和牛犢的血、乃用自己的血、只一次進入聖所、成了永遠贖罪的事。\\
若山羊和公牛的血、並母牛犢的灰、灑在不潔的人身上、尚且叫人成聖、身體潔淨．\\
何況基督藉著永遠的靈、將自己無瑕無疵獻給　神、他的血豈不更能洗淨你們的心〔原文作良心〕除去你們的死行、使你們事奉那永生　神麼。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
