%simple
\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.3in,bottom=0.3in,left=0.2in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\usepackage{setspace}
\title{\vspace{-2ex}Divine Liturgy\\Reading from The Epistles}
\author{Week Easter\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Деян., 1 зач., I, 1-8.   }\\
\Large%for eng/rus
Первую книгу написал я к тебе, Феофил, о всем, что Иисус делал и чему учил от начала
\\
до того дня, в который Он вознесся, дав Святым Духом повеления Апостолам, которых Он избрал,
\\
которым и явил Себя живым, по страдании Своем, со многими верными доказательствами, в продолжение сорока дней являясь им и говоря о Царствии Божием.
\\
И, собрав их, Он повелел им: не отлучайтесь из Иерусалима, но ждите обещанного от Отца, о чем вы слышали от Меня,
\\
ибо Иоанн крестил водою, а вы, через несколько дней после сего, будете крещены Духом Святым.
\\
Посему они, сойдясь, спрашивали Его, говоря: не в сие ли время, Господи, восстановляешь Ты царство Израилю?
\\
Он же сказал им: не ваше дело знать времена или сроки, которые Отец положил в Своей власти,
\\
но вы примете силу, когда сойдет на вас Дух Святый; и будете Мне свидетелями в Иерусалиме и во всей Иудее и Самарии и даже до края земли.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Acts 1:1--1:8.}\\
The former treatise have I made, O Theophilus, of all that Jesus began both to do and teach,\\
Until the day in which he was taken up, after that he through the Holy Ghost had given commandments unto the apostles whom he had chosen:\\
To whom also he shewed himself alive after his passion by many infallible proofs, being seen of them forty days, and speaking of the things pertaining to the kingdom of God:\\
And, being assembled together with them, commanded them that they should not depart from Jerusalem, but wait for the promise of the Father, which, saith he, ye have heard of me.\\
For John truly baptized with water; but ye shall be baptized with the Holy Ghost not many days hence.\\
When they therefore were come together, they asked of him, saying, Lord, wilt thou at this time restore again the kingdom to Israel?\\
And he said unto them, It is not for you to know the times or the seasons, which the Father hath put in his own power.\\
But ye shall receive power, after that the Holy Ghost is come upon you: and ye shall be witnesses unto me both in Jerusalem, and in all Judaea, and in Samaria, and unto the uttermost part of the earth.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.1}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{使徒行傳 1:1--1:8.}\\
提阿非羅阿、我已經作了前書、論到耶穌開頭一切所行所教訓的、\\
直到他藉著聖靈、吩咐所揀選的使徒、以後被接上升的日子為止。\\
他受害之後、用許多的憑據、將自己活活的顯給使徒看、四十天之久向他們顯現、講說　神國的事。\\
耶穌和他們聚集的時候、囑咐他們說、不要離開耶路撒冷、要等候父所應許的、就是你們聽見我說過的。\\
約翰是用水施洗．但不多幾日、你們要受聖靈的洗。\\
他們聚集的時候、問耶穌說、主阿、你復興以色列國、就在這時候嗎。\\
耶穌對他們說、父憑著自己的權柄、所定的時候日期、不是你們可以知道的。\\
但聖靈降臨在你們身上、你們就必得著能力．並要在耶路撒冷、猶太全地、和撒瑪利亞、直到地極、作我的見證。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
