\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.2in,bottom=0.2in,left=0.3in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 10 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{1 Кор., 131 зач., IV, 9-16.}\\
\Large%for eng/rus
Ибо я думаю, что нам, последним посланникам, Бог судил быть как бы приговоренными к смерти, потому что мы сделались позорищем для мира, для Ангелов и человеков.
\\
Мы безумны Христа ради, а вы мудры во Христе; мы немощны, а вы крепки; вы в славе, а мы в бесчестии.
\\
Даже доныне терпим голод и жажду, и наготу и побои, и скитаемся,
\\
и трудимся, работая своими руками. Злословят нас, мы благословляем; гонят нас, мы терпим;
\\
хулят нас, мы молим; мы как сор для мира, как прах, всеми попираемый доныне.
\\
Не к постыжению вашему пишу сие, но вразумляю вас, как возлюбленных детей моих.
\\
Ибо, хотя у вас тысячи наставников во Христе, но не много отцов; я родил вас во Христе Иисусе благовествованием.
\\
Посему умоляю вас: подражайте мне, как я Христу.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{1 Corinthians 4:9--4:16.}\\
For I think that God hath set forth us the apostles last, as it were appointed to death: for we are made a spectacle unto the world, and to angels, and to men.\\
We are fools for Christ's sake, but ye are wise in Christ; we are weak, but ye are strong; ye are honourable, but we are despised.\\
Even unto this present hour we both hunger, and thirst, and are naked, and are buffeted, and have no certain dwellingplace;\\
And labour, working with our own hands: being reviled, we bless; being persecuted, we suffer it:\\
Being defamed, we intreat: we are made as the filth of the world, and are the offscouring of all things unto this day.\\
I write not these things to shame you, but as my beloved sons I warn you.\\
For though ye have ten thousand instructors in Christ, yet have ye not many fathers: for in Christ Jesus I have begotten you through the gospel.\\
Wherefore I beseech you, be ye followers of me.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{哥林多前書 4:9--4:16.}\\
我想　神把我們使徒明明列在末後、好像定死罪的囚犯．因為我們成了一臺戲、給世人和天使觀看。\\
我們為基督的緣故算是愚拙的、你們在基督裡倒是聰明的、我們軟弱、你們倒強壯．你們有榮耀、我們倒被藐視。\\
直到如今、我們還是又飢、又渴、又赤身露體、又挨打、又沒有一定的住處．\\
並且勞苦、親手作工．被人咒罵、我們就祝福．被人逼迫、我們就忍受．\\
被人毀謗、我們就善勸．直到如今、人還把我們看作世界上的污穢、萬物中的渣滓。\\
我寫這話、不是叫你們羞愧、乃是警戒你們、好像我所親愛的兒女一樣。\\
你們學基督的、師傅雖有一萬、為父的卻是不多、因我在基督耶穌裡用福音生了你們。\\
所以我求你們效法我。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
