\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.2in,bottom=0.2in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 26 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Еф., 229 зач., V, 8-19.}\\
\Large%for eng/rus
Вы были некогда тьма, а теперь - свет в Господе: поступайте, как чада света,
\\
потому что плод Духа состоит во всякой благости, праведности и истине.
\\
Испытывайте, что благоугодно Богу,
\\
и не участвуйте в бесплодных делах тьмы, но и обличайте.
\\
Ибо о том, что они делают тайно, стыдно и говорить.
\\
Все же обнаруживаемое делается явным от света, ибо все, делающееся явным, свет есть.
\\
Посему сказано: "встань, спящий, и воскресни из мертвых, и осветит тебя Христос".
\\
Итак, смотрите, поступайте осторожно, не как неразумные, но как мудрые,
\\
дорожа временем, потому что дни лукавы.
\\
Итак, не будьте нерассудительны, но познавайте, что есть воля Божия.
\\
И не упивайтесь вином, от которого бывает распутство; но исполняйтесь Духом,
\\
назидая самих себя псалмами и славословиями и песнопениями духовными, поя и воспевая в сердцах ваших Господу,
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Ephesians 5:8--5:19.}\\
For ye were sometimes darkness, but now are ye light in the Lord: walk as children of light:\\
(For the fruit of the Spirit is in all goodness and righteousness and truth;)\\
Proving what is acceptable unto the Lord.\\
And have no fellowship with the unfruitful works of darkness, but rather reprove them.\\
For it is a shame even to speak of those things which are done of them in secret.\\
But all things that are reproved are made manifest by the light: for whatsoever doth make manifest is light.\\
Wherefore he saith, Awake thou that sleepest, and arise from the dead, and Christ shall give thee light.\\
See then that ye walk circumspectly, not as fools, but as wise,\\
Redeeming the time, because the days are evil.\\
Wherefore be ye not unwise, but understanding what the will of the Lord is.\\
And be not drunk with wine, wherein is excess; but be filled with the Spirit;\\
Speaking to yourselves in psalms and hymns and spiritual songs, singing and making melody in your heart to the Lord;\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{以弗所書 5:8--5:19.}\\
從前你們是暗昧的、但如今在主裡面是光明的、行事為人就當像光明的子女．\\
光明所結的果子、就是一切良善、公義、誠實．\\
總要察驗何為主所喜悅的事。\\
那暗昧無益的事、不要與人同行、倒要責備行這事的人．\\
因為他們暗中所行的、就是提起來、也是可恥的。\\
凡事受了責備、就被光顯明出來．因為一切能顯明的、就是光。\\
所以主說、你這睡著的人、當醒過來、從死裡復活、基督就要光照你了。\\
你們要謹慎行事、不要像愚昧人、當像智慧人．\\
要愛惜光陰、因為現今的世代邪惡。\\
不要作糊塗人、要明白主的旨意如何。\\
不要醉酒、酒能使人放蕩、乃要被聖靈充滿。\\
當用詩章、頌詞、靈歌、彼此對說、口唱心和的讚美主．
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
