\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Palm Sunday\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\onehalfspacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Флп., 247 зач., IV, 4-9.}\\
\Large%for eng/rus
Радуйтесь всегда в Господе; и еще говорю: радуйтесь.
\\
Кротость ваша да будет известна всем человекам. Господь близко.
\\
Не заботьтесь ни о чем, но всегда в молитве и прошении с благодарением открывайте свои желания пред Богом,
\\
и мир Божий, который превыше всякого ума, соблюдет сердца ваши и помышления ваши во Христе Иисусе.
\\
Наконец, братия мои, что только истинно, что честно, что справедливо, что чисто, что любезно, что достославно, что только добродетель и похвала, о том помышляйте.
\\
Чему вы научились, что приняли и слышали и видели во мне, то исполняйте,- и Бог мира будет с вами.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Philippians 4:4--4:9.}\\
Rejoice in the Lord alway: and again I say, Rejoice.\\
Let your moderation be known unto all men. The Lord is at hand.\\
Be careful for nothing; but in every thing by prayer and supplication with thanksgiving let your requests be made known unto God.\\
And the peace of God, which passeth all understanding, shall keep your hearts and minds through Christ Jesus.\\
Finally, brethren, whatsoever things are true, whatsoever things are honest, whatsoever things are just, whatsoever things are pure, whatsoever things are lovely, whatsoever things are of good report; if there be any virtue, and if there be any praise, think on these things.\\
Those things, which ye have both learned, and received, and heard, and seen in me, do: and the God of peace shall be with you.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.5}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{腓立比書 4:4--4:9.}\\
你們要靠主常常喜樂．我再說、你們要喜樂。\\
當叫眾人知道你們謙讓的心。主已經近了。\\
應當一無挂慮、只要凡事藉著禱告、祈求、和感謝、將你們所要的告訴　神。\\
　神所賜出人意外的平安、必在基督耶穌裡、保守你們的心懷意念。\\
弟兄們、我還有未盡的話．凡是真實的、可敬的、公義的、清潔的、可愛的、有美名的．若有甚麼德行、若有甚麼稱讚、這些事你們都要思念。\\
你們在我身上所學習的、所領受的、所聽見的、所看見的、這些事你們都要去行．賜平安的　神、就必與你們同在。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
