\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.0in,bottom=0.0in,left=-0.15in,right=0.25in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{\vspace{-4ex}Divine Liturgy\vspace{-0.7ex}\\Reading from The Epistles\vspace{-1.8ex}}
\author{Week 6 after Easter\vspace{
-11ex%for author
}}
\date{\vspace{
-11ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.48\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Деян., 38 зач., XVI, 16-34.}\\
Случилось, что, когда мы шли в молитвенный дом, встретилась нам одна служанка, одержимая духом прорицательным, которая через прорицание доставляла большой доход господам своим.
\\
Идя за Павлом и за нами, она кричала, говоря: сии человеки - рабы Бога Всевышнего, которые возвещают нам путь спасения.
\\
Это она делала много дней. Павел, вознегодовав, обратился и сказал духу: именем Иисуса Христа повелеваю тебе выйти из нее. И дух вышел в тот же час.
\\
Тогда господа ее, видя, что исчезла надежда дохода их, схватили Павла и Силу и повлекли на площадь к начальникам.
\\
И, приведя их к воеводам, сказали: сии люди, будучи Иудеями, возмущают наш город
\\
и проповедуют обычаи, которых нам, Римлянам, не следует ни принимать, ни исполнять.
\\
Народ также восстал на них, а воеводы, сорвав с них одежды, велели бить их палками
\\
и, дав им много ударов, ввергли в темницу, приказав темничному стражу крепко стеречь их.
\\
Получив такое приказание, он ввергнул их во внутреннюю темницу и ноги их забил в колоду.
\\
Около полуночи Павел и Сила, молясь, воспевали Бога; узники же слушали их.
\\
Вдруг сделалось великое землетрясение, так что поколебалось основание темницы; тотчас отворились все двери, и у всех узы ослабели.
\\
Темничный же страж, пробудившись и увидев, что двери темницы отворены, извлек меч и хотел умертвить себя, думая, что узники убежали.
\\
Но Павел возгласил громким голосом, говоря: не делай себе никакого зла, ибо все мы здесь.
\\
Он потребовал огня, вбежал в темницу и в трепете припал к Павлу и Силе,
\\
и, выведя их вон, сказал: государи мои! что мне делать, чтобы спастись?
\\
Они же сказали: веруй в Господа Иисуса Христа, и спасешься ты и весь дом твой.
\\
И проповедали слово Господне ему и всем, бывшим в доме его.
\\
И, взяв их в тот час ночи, он омыл раны их и немедленно крестился сам и все домашние его.
\\
И, приведя их в дом свой, предложил трапезу и возрадовался со всем домом своим, что уверовал в Бога.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.49\textwidth}

\textbf{Acts 16:16--16:34.}\\
And it came to pass, as we went to prayer, a certain damsel possessed with a spirit of divination met us, which brought her masters much gain by soothsaying:\\
The same followed Paul and us, and cried, saying, These men are the servants of the most high God, which shew unto us the way of salvation.\\
And this did she many days. But Paul, being grieved, turned and said to the spirit, I command thee in the name of Jesus Christ to come out of her. And he came out the same hour.\\
And when her masters saw that the hope of their gains was gone, they caught Paul and Silas, and drew them into the marketplace unto the rulers,\\
And brought them to the magistrates, saying, These men, being Jews, do exceedingly trouble our city,\\
And teach customs, which are not lawful for us to receive, neither to observe, being Romans.\\
And the multitude rose up together against them: and the magistrates rent off their clothes, and commanded to beat them.\\
And when they had laid many stripes upon them, they cast them into prison, charging the jailor to keep them safely:\\
Who, having received such a charge, thrust them into the inner prison, and made their feet fast in the stocks.\\
And at midnight Paul and Silas prayed, and sang praises unto God: and the prisoners heard them.\\
And suddenly there was a great earthquake, so that the foundations of the prison were shaken: and immediately all the doors were opened, and every one's bands were loosed.\\
And the keeper of the prison awaking out of his sleep, and seeing the prison doors open, he drew out his sword, and would have killed himself, supposing that the prisoners had been fled.\\
But Paul cried with a loud voice, saying, Do thyself no harm: for we are all here.\\
Then he called for a light, and sprang in, and came trembling, and fell down before Paul and Silas,\\
And brought them out, and said, Sirs, what must I do to be saved?\\
And they said, Believe on the Lord Jesus Christ, and thou shalt be saved, and thy house.\\
And they spake unto him the word of the Lord, and to all that were in his house.\\
And he took them the same hour of the night, and washed their stripes; and was baptized, he and all his, straightway.\\
And when he had brought them into his house, he set meat before them, and rejoiced, believing in God with all his house.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{使徒行傳 16:16--16:34.}\\
後來、我們往那禱告的地方去．有一個使女迎著面來、他被巫鬼所附、用法術、叫他主人們大得財利。\\
他跟隨保羅和我們、喊著說、這些人是至高　神的僕人、對你們傳說救人的道。\\
他一連多日這樣喊叫、保羅就心中厭煩、轉身對那鬼說、我奉耶穌基督的名、吩咐你從他身上出來．那鬼當時就出來了。\\
使女的主人們、見得利的指望沒有了、便揪住保羅和西拉、拉他們到市上去見首領．\\
又帶到官長面前說、這些人原是猶太人、竟騷擾我們的城、\\
傳我們羅馬人所不可受、不可行的規矩。\\
眾人就一同起來攻擊他們．官長吩咐剝了他們的衣裳、用棍打。\\
打了許多棍、便將他們下在監裡、囑咐禁卒嚴緊看守。\\
禁卒領了這樣的命、就把他們下在內監裡、兩腳上了木狗。\\
約在半夜、保羅和西拉、禱告唱詩讚美　神．眾囚犯也側耳而聽。\\
忽然地大震動、甚至監牢的地基都搖動了．監門立刻全開、眾囚犯的鎖鍊也都鬆開了。\\
禁卒一醒、看見監門全開、以為囚犯已經逃走、就拔刀要自殺。\\
保羅大聲呼叫說、不要傷害自己、我們都在這裡。\\
禁卒叫人拿燈來、就跳進去、戰戰兢兢的、俯伏在保羅西拉面前．\\
又領他們出來、說、二位先生、我當怎樣行纔可以得救。\\
他們說、當信主耶穌、你和你一家都必得救。\\
他們就把主的道、講給他和他全家的人聽。\\
當夜、就在那時候、禁卒把他們帶去、洗他們的傷．他和屬乎他的人、立時都受了洗。\\
於是禁卒領他們上自己家裡去、給他們擺上飯、他和全家、因為信了　神、都很喜樂。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
