\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=-0.05in,bottom=0.0in,left=0.2in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 7 after Easter\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Деян., 44 зач., XX, 16-18, 28-36.}\\
\large%for eng/rus
ибо Павлу рассудилось миновать Ефес, чтобы не замедлить ему в Асии; потому что он поспешал, если можно, в день Пятидесятницы быть в Иерусалиме.
\\
Из Милита же послав в Ефес, он призвал пресвитеров церкви,
\\
и, когда они пришли к нему, он сказал им: вы знаете, как я с первого дня, в который пришел в Асию, все время был с вами,
\\
Итак внимайте себе и всему стаду, в котором Дух Святый поставил вас блюстителями, пасти Церковь Господа и Бога, которую Он приобрел Себе Кровию Своею.
\\
Ибо я знаю, что, по отшествии моем, войдут к вам лютые волки, не щадящие стада;
\\
и из вас самих восстанут люди, которые будут говорить превратно, дабы увлечь учеников за собою.
\\
Посему бодрствуйте, памятуя, что я три года день и ночь непрестанно со слезами учил каждого из вас.
\\
И ныне предаю вас, братия, Богу и слову благодати Его, могущему назидать вас более и дать вам наследие со всеми освященными.
\\
Ни серебра, ни золота, ни одежды я ни от кого не пожелал:
\\
сами знаете, что нуждам моим и нуждам бывших при мне послужили руки мои сии.
\\
Во всем показал я вам, что, так трудясь, надобно поддерживать слабых и памятовать слова Господа Иисуса, ибо Он Сам сказал: "блаженнее давать, нежели принимать".
\\
Сказав это, он преклонил колени свои и со всеми ими помолился.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Acts 20:16--20:18, 20:28--20:36.}\\
For Paul had determined to sail by Ephesus, because he would not spend the time in Asia: for he hasted, if it were possible for him, to be at Jerusalem the day of Pentecost.\\
And from Miletus he sent to Ephesus, and called the elders of the church.\\
And when they were come to him, he said unto them, Ye know, from the first day that I came into Asia, after what manner I have been with you at all seasons,\\
Take heed therefore unto yourselves, and to all the flock, over the which the Holy Ghost hath made you overseers, to feed the church of God, which he hath purchased with his own blood.\\
For I know this, that after my departing shall grievous wolves enter in among you, not sparing the flock.\\
Also of your own selves shall men arise, speaking perverse things, to draw away disciples after them.\\
Therefore watch, and remember, that by the space of three years I ceased not to warn every one night and day with tears.\\
And now, brethren, I commend you to God, and to the word of his grace, which is able to build you up, and to give you an inheritance among all them which are sanctified.\\
I have coveted no man's silver, or gold, or apparel.\\
Yea, ye yourselves know, that these hands have ministered unto my necessities, and to them that were with me.\\
I have shewed you all things, how that so labouring ye ought to support the weak, and to remember the words of the Lord Jesus, how he said, It is more blessed to give than to receive.\\
And when he had thus spoken, he kneeled down, and prayed with them all.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{使徒行傳 20:16--20:18, 20:28--20:36.}\\
乃因保羅早已定意越過以弗所、免得在亞西亞耽延．他急忙前走、巴不得趕五旬節能到耶路撒冷。\\
保羅從米利都打發人往以弗所去、請教會的長老來。\\
他們來了、保羅就說、你們知道、自從我到亞西亞的日子以來、在你們中間始終為人如何、\\
聖靈立你們作全群的監督、你們就當為自己謹慎、也為全群謹慎、牧養　神的教會、就是他用自己血所買來的。〔或作救贖的〕\\
我知道我去之後、必有兇暴的豺狼、進入你們中間、不愛惜羊群。\\
就是你們中間、也必有人起來、說悖謬的話、要引誘門徒跟從他們。\\
所以你們應當儆醒、記念我三年之久、晝夜不住的流淚、勸戒你們各人。\\
如今我把你們交託　神、和他恩惠的道．這道能建立你們、叫你們和一切成聖的人同得基業。\\
我未曾貪圖一個人的金、銀、衣服。\\
我這兩隻手、常供給我和同人的需用、這是你們自己知道的。\\
我凡事給你們作榜樣、叫你們知道、應當這樣勞苦、扶助軟弱的人、又當記念主耶穌的話、說、施比受更為有福。\\
保羅說完了這話、就跪下同眾人禱告。\\
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
