\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.2in,bottom=0.2in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 3 after Easter\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Деян., 16 зач., VI, 1-7.}\\
\Large%for eng/rus
Тогда двенадцать Апостолов, созвав множество учеников, сказали: нехорошо нам, оставив слово Божие, пещись о столах.
\\
Итак, братия, выберите из среды себя семь человек изведанных, исполненных Святаго Духа и мудрости; их поставим на эту службу,
\\
а мы постоянно пребудем в молитве и служении слова.
\\
И угодно было это предложение всему собранию; и избрали Стефана, мужа, исполненного веры и Духа Святаго, и Филиппа, и Прохора, и Никанора, и Тимона, и Пармена, и Николая Антиохийца, обращенного из язычников;
\\
их поставили перед Апостолами, и сии, помолившись, возложили на них руки.
\\
И слово Божие росло, и число учеников весьма умножалось в Иерусалиме; и из священников очень многие покорились вере.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Acts 6:1--6:7.}\\
And in those days, when the number of the disciples was multiplied, there arose a murmuring of the Grecians against the Hebrews, because their widows were neglected in the daily ministration.\\
Then the twelve called the multitude of the disciples unto them, and said, It is not reason that we should leave the word of God, and serve tables.\\
Wherefore, brethren, look ye out among you seven men of honest report, full of the Holy Ghost and wisdom, whom we may appoint over this business.\\
But we will give ourselves continually to prayer, and to the ministry of the word.\\
And the saying pleased the whole multitude: and they chose Stephen, a man full of faith and of the Holy Ghost, and Philip, and Prochorus, and Nicanor, and Timon, and Parmenas, and Nicolas a proselyte of Antioch:\\
Whom they set before the apostles: and when they had prayed, they laid their hands on them.\\
And the word of God increased; and the number of the disciples multiplied in Jerusalem greatly; and a great company of the priests were obedient to the faith.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{使徒行傳 6:1--6:7.}\\
那時、門徒增多、有說希利尼話的猶太人、向希伯來人發怨言．因為在天天的供給上忽略了他們的寡婦。\\
十二使徒叫眾門徒來、對他們說、我們撇下　神的道、去管理飯食、原是不合宜的。\\
所以弟兄們、當從你們中間選出七個有好名聲、被聖靈充滿、智慧充足的人、我們就派他們管理這事。\\
但我們要專心以祈禱傳道為事。\\
大眾都喜悅這話、就揀選了司提反、乃是大有信心、聖靈充滿的人、又揀選腓利、伯羅哥羅、尼迦挪、提門、巴米拿、並進猶太教的安提阿人尼哥拉．\\
叫他們站在使徒面前．使徒禱告了、就按手在他們頭上。\\
　神的道興旺起來．在耶路撒冷門徒數目加增的甚多．也有許多祭司信從了這道。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
