\documentclass[12pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.3in,bottom=0.3in,left=0.3in,right=0.4in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 34 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Еф., 224 зач. (от полу́), IV, 7-13.}\\
\Large%for eng/rus
Каждому же из нас дана благодать по мере дара Христова.
\\
Посему и сказано: восшед на высоту, пленил плен и дал дары человекам.
\\
А "восшел" что означает, как не то, что Он и нисходил прежде в преисподние места земли?
\\
Нисшедший, Он же есть и восшедший превыше всех небес, дабы наполнить все.
\\
И Он поставил одних Апостолами, других пророками, иных Евангелистами, иных пастырями и учителями,
\\
к совершению святых, на дело служения, для созидания Тела Христова,
\\
доколе все придем в единство веры и познания Сына Божия, в мужа совершенного, в меру полного возраста Христова;
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Ephesians 4:7--4:13.}\\
But unto every one of us is given grace according to the measure of the gift of Christ.\\
Wherefore he saith, When he ascended up on high, he led captivity captive, and gave gifts unto men.\\
(Now that he ascended, what is it but that he also descended first into the lower parts of the earth?\\
He that descended is the same also that ascended up far above all heavens, that he might fill all things.)\\
And he gave some, apostles; and some, prophets; and some, evangelists; and some, pastors and teachers;\\
For the perfecting of the saints, for the work of the ministry, for the edifying of the body of Christ:\\
Till we all come in the unity of the faith, and of the knowledge of the Son of God, unto a perfect man, unto the measure of the stature of the fulness of Christ:\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.5}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{以弗所書 4:7--4:13.}\\
我們各人蒙恩、都是照基督所量給各人的恩賜。\\
所以經上說、『他升上高天的時候、擄掠了仇敵、將各樣的恩賜賞給人。』\\
（既說升上、豈不是先降在地下麼．\\
那降下的、就是遠升諸天之上要充滿萬有的。）\\
他所賜的有使徒、有先知．有傳福音的．有牧師和教師．\\
為要成全聖徒、各盡其職、建立基督的身體．\\
直等到我們眾人在真道上同歸於一、認識　神的兒子、得以長大成人、滿有基督長成的身量．
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
