\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.2in,bottom=0.2in,left=0.1in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 13 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{1 Кор., 166 зач., XVI, 13-24.}\\
\Large%for eng/rus
Бодрствуйте, стойте в вере, будьте мужественны, тверды.
\\
Все у вас да будет с любовью.
\\
Прошу вас, братия (вы знаете семейство Стефаново, что оно есть начаток Ахаии и что они посвятили себя на служение святым),
\\
будьте и вы почтительны к таковым и ко всякому содействующему и трудящемуся.
\\
Я рад прибытию Стефана, Фортуната и Ахаика: они восполнили для меня отсутствие ваше,
\\
ибо они мой и ваш дух успокоили. Почитайте таковых.
\\
Приветствуют вас церкви Асийские; приветствуют вас усердно в Господе Акила и Прискилла с домашнею их церковью.
\\
Приветствуют вас все братия. Приветствуйте друг друга святым целованием.
\\
Мое, Павлово, приветствие собственноручно.
\\
Благодать Господа нашего Иисуса Христа с вами,
\\
и любовь моя со всеми вами во Христе Иисусе. Аминь.
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{1 Corinthians 16:13--16:24.}\\
Watch ye, stand fast in the faith, quit you like men, be strong.\\
Let all your things be done with charity.\\
I beseech you, brethren, (ye know the house of Stephanas, that it is the firstfruits of Achaia, and that they have addicted themselves to the ministry of the saints,)\\
That ye submit yourselves unto such, and to every one that helpeth with us, and laboureth.\\
I am glad of the coming of Stephanas and Fortunatus and Achaicus: for that which was lacking on your part they have supplied.\\
For they have refreshed my spirit and yours: therefore acknowledge ye them that are such.\\
The churches of Asia salute you. Aquila and Priscilla salute you much in the Lord, with the church that is in their house.\\
All the brethren greet you. Greet ye one another with an holy kiss.\\
The salutation of me Paul with mine own hand.\\
If any man love not the Lord Jesus Christ, let him be Anathema Maranatha.\\
The grace of our Lord Jesus Christ be with you.\\
My love be with you all in Christ Jesus. Amen. 
\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.2}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{哥林多前書 16:13--16:24.}\\
你們務要儆醒、在真道上站立得穩、要作大丈夫、要剛強。\\
凡你們所作的、都要憑愛心而作。\\
弟兄們、你們曉得司提反一家、是亞該亞初結的果子．並且他們專以服事聖徒為念．\\
我勸你們順服這樣的人、並一切同工同勞的人。\\
司提反、和福徒拿都、並亞該古、到這裡來、我很喜歡．因為你們待我有不及之處、他們補上了。\\
他們叫我和你們心裡都快活．這樣的人、你們務要敬重。\\
亞西亞的眾教會問你們安。亞居拉和百基拉、並在他們家裡的教會、因主多多的問你們安。\\
眾弟兄都問你們安。你們要親嘴問安、彼此務要聖潔。\\
我保羅親筆問安。\\
若有人不愛主、這人可詛可咒。主必要來。\\
願主耶穌基督的恩、常與你們眾人同在。\\
我在基督耶穌裡的愛、與你們眾人同在。阿們。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
