\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.2in,bottom=0.2in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 2 after Easter\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Деян., 14 зач., V, 12-20.}\\
\Large%for eng/rus
Руками же Апостолов совершались в народе многие знамения и чудеса; и все единодушно пребывали в притворе Соломоновом.
\\
Из посторонних же никто не смел пристать к ним, а народ прославлял их.
\\
Верующих же более и более присоединялось к Господу, множество мужчин и женщин,
\\
так что выносили больных на улицы и полагали на постелях и кроватях, дабы хотя тень проходящего Петра осенила кого из них.
\\
Сходились также в Иерусалим многие из окрестных городов, неся больных и нечистыми духами одержимых, которые и исцелялись все.
\\
Первосвященник же и с ним все, принадлежавшие к ереси саддукейской, исполнились зависти,
\\
и наложили руки свои на Апостолов, и заключили их в народную темницу.
\\
Но Ангел Господень ночью отворил двери темницы и, выведя их, сказал:
\\
идите и, став в храме, говорите народу все сии слова жизни.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Acts 5:12--5:20.}\\
And by the hands of the apostles were many signs and wonders wrought among the people; (and they were all with one accord in Solomon's porch.\\
And of the rest durst no man join himself to them: but the people magnified them.\\
And believers were the more added to the Lord, multitudes both of men and women.)\\
Insomuch that they brought forth the sick into the streets, and laid them on beds and couches, that at the least the shadow of Peter passing by might overshadow some of them.\\
There came also a multitude out of the cities round about unto Jerusalem, bringing sick folks, and them which were vexed with unclean spirits: and they were healed every one.\\
Then the high priest rose up, and all they that were with him, (which is the sect of the Sadducees,) and were filled with indignation,\\
And laid their hands on the apostles, and put them in the common prison.\\
But the angel of the Lord by night opened the prison doors, and brought them forth, and said,\\
Go, stand and speak in the temple to the people all the words of this life.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{使徒行傳 5:12--5:20.}\\
主藉使徒的手、在民間行了許多神蹟奇事、（他們〔或作信的人〕都同心合意的在所羅門的廊下。\\
其餘的人、沒有一個敢貼近他們．百姓卻尊重他們。\\
信而歸主的人、越發增添、連男帶女很多）\\
甚至有人將病人抬到街上、放在床上、或褥子上、指望彼得過來的時候、或者得他的影兒照在甚麼人身上。\\
還有許多人、帶著病人、和被污鬼纏磨的、從耶路撒冷四圍的城邑來、全都得了醫治。\\
大祭司和他的一切同人、就是撒都該教門的人、都起來、滿心忌恨。\\
就下手拿住使徒、收在外監。\\
但主的使者、夜間開了監門、領他們出來、\\
說、你們去站在殿裡、把這生命的道、都講給百姓聽。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
