\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 14 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\LARGE%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{1 Тим., 282 зач., II, 1-7.}\\
\LARGE%for eng/rus
Итак прежде всего прошу совершать молитвы, прошения, моления, благодарения за всех человеков,
\\
за царей и за всех начальствующих, дабы проводить нам жизнь тихую и безмятежную во всяком благочестии и чистоте,
\\
ибо это хорошо и угодно Спасителю нашему Богу,
\\
Который хочет, чтобы все люди спаслись и достигли познания истины.
\\
Ибо един Бог, един и посредник между Богом и человеками, человек Христос Иисус,
\\
предавший Себя для искупления всех. Таково было в свое время свидетельство,
\\
для которого я поставлен проповедником и Апостолом,- истину говорю во Христе, не лгу,- учителем язычников в вере и истине.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{1 Timothy 2:1--2:7.}\\
I exhort therefore, that, first of all, supplications, prayers, intercessions, and giving of thanks, be made for all men;\\
For kings, and for all that are in authority; that we may lead a quiet and peaceable life in all godliness and honesty.\\
For this is good and acceptable in the sight of God our Saviour;\\
Who will have all men to be saved, and to come unto the knowledge of the truth.\\
For there is one God, and one mediator between God and men, the man Christ Jesus;\\
Who gave himself a ransom for all, to be testified in due time.\\
Whereunto I am ordained a preacher, and an apostle, (I speak the truth in Christ, and lie not;) a teacher of the Gentiles in faith and verity.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\vspace*{\fill}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\begin{spacing}{1.2}
\fontsize{30}{35}\selectfont
\textbf{提摩太前書 2:1--2:7.}\\
我勸你第一要為萬人懇求、禱告、代求、祝謝．\\
為君王和一切在位的也該如此．使我們可以敬虔端正、平安無事的度日。\\
這是好的、在　神我們救主面前可蒙悅納。\\
他願意萬人得救、明白真道．\\
因為只有一位　神、在　神和人中間、只有一位中保、乃是降世為人的基督耶穌。\\
他捨自己作萬人的贖價．到了時候、這事必證明出來。\\
我為此奉派、作傳道的、作使徒、作外邦人的師傅、教導他們相信、學習真道。我說的是真話、並不是謊言。
\end{spacing}
\end{CJK}
\end{minipage}}
\vspace*{\fill}
\end{document}
