\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 23 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\LARGE%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Еф., 220 зач., II, 4-10.}\\
\LARGE%for eng/rus
Бог, богатый милостью, по Своей великой любви, которою возлюбил нас,
\\
и нас, мертвых по преступлениям, оживотворил со Христом,- благодатью вы спасены,-
\\
и воскресил с Ним, и посадил на небесах во Христе Иисусе,
\\
дабы явить в грядущих веках преизобильное богатство благодати Своей в благости к нам во Христе Иисусе.
\\
Ибо благодатью вы спасены через веру, и сие не от вас, Божий дар:
\\
не от дел, чтобы никто не хвалился.
\\
Ибо мы - Его творение, созданы во Христе Иисусе на добрые дела, которые Бог предназначил нам исполнять.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Ephesians 2:4--2:10.}\\
But God, who is rich in mercy, for his great love wherewith he loved us,\\
Even when we were dead in sins, hath quickened us together with Christ, (by grace ye are saved;)\\
And hath raised us up together, and made us sit together in heavenly places in Christ Jesus:\\
That in the ages to come he might shew the exceeding riches of his grace in his kindness toward us through Christ Jesus.\\
For by grace are ye saved through faith; and that not of yourselves: it is the gift of God:\\
Not of works, lest any man should boast.\\
For we are his workmanship, created in Christ Jesus unto good works, which God hath before ordained that we should walk in them.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{以弗所書 2:4--2:10.}\\
然而　神既有豐富的憐憫．因他愛我們的大愛、\\
當我們死在過犯中的時候、便叫我們與基督一同活過來．（你們得救是本乎恩）\\
他又叫我們與基督耶穌一同復活、一同坐在天上、\\
要將他極豐富的恩典、就是他在基督耶穌裡向我們所施的恩慈、顯明給後來的世代看．\\
你們得救是本乎恩、也因著信、這並不是出於自己、乃是　神所賜的．\\
也不是出於行為、免得有人自誇。\\
我們原是他的工作、在基督耶穌裡造成的、為要叫我們行善、就是　神所預備叫我們行的。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
