\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 21 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Гал., 203 зач., II, 16-20.}\\
\Large%for eng/rus
однако же, узнав, что человек оправдывается не делами закона, а только верою в Иисуса Христа, и мы уверовали во Христа Иисуса, чтобы оправдаться верою во Христа, а не делами закона; ибо делами закона не оправдается никакая плоть.
\\
Если же, ища оправдания во Христе, мы и сами оказались грешниками, то неужели Христос есть служитель греха? Никак.
\\
Ибо если я снова созидаю, что разрушил, то сам себя делаю преступником.
\\
Законом я умер для закона, чтобы жить для Бога. Я сораспялся Христу,
\\
и уже не я живу, но живет во мне Христос. А что ныне живу во плоти, то живу верою в Сына Божия, возлюбившего меня и предавшего Себя за меня.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Galatians 2:16--2:20.}\\
Knowing that a man is not justified by the works of the law, but by the faith of Jesus Christ, even we have believed in Jesus Christ, that we might be justified by the faith of Christ, and not by the works of the law: for by the works of the law shall no flesh be justified.\\
But if, while we seek to be justified by Christ, we ourselves also are found sinners, is therefore Christ the minister of sin? God forbid.\\
For if I build again the things which I destroyed, I make myself a transgressor.\\
For I through the law am dead to the law, that I might live unto God.\\
I am crucified with Christ: nevertheless I live; yet not I, but Christ liveth in me: and the life which I now live in the flesh I live by the faith of the Son of God, who loved me, and gave himself for me.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{加拉太書 2:16--2:20.}\\
既知道人稱義、不是因行律法、乃是因信耶穌基督、連我們也信了基督耶穌、使我們因信基督稱義、不因行律法稱義．因為凡有血氣的、沒有一人因行律法稱義。\\
我們若求在基督裡稱義、卻仍舊是罪人、難道基督是叫人犯罪的麼．斷乎不是。\\
我素來所拆毀的、若重新建造、這就證明自己是犯罪的人。\\
我因律法、就向律法死了、叫我可以向　神活著。\\
我已經與基督同釘十字架．現在活著的、不再是我、乃是基督在我裡面活著．並且我如今在肉身活著、是因信　神的兒子而活、他是愛我、為我捨己。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
