\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.0in,bottom=0.2in,left=0.0in,right=0.3in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 4 after Easter\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\onehalfspacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Деян., 23 зач., IX, 32-42.}\\
\large%for eng/rus
Случилось, что Петр, обходя всех, пришел и к святым, живущим в Лидде.
\\
Там нашел он одного человека, именем Энея, который восемь уже лет лежал в постели в расслаблении.
\\
Петр сказал ему: Эней! исцеляет тебя Иисус Христос; встань с постели твоей. И он тотчас встал.
\\
И видели его все, живущие в Лидде и в Сароне, которые и обратились к Господу.
\\
В Иоппии находилась одна ученица, именем Тавифа, что значит: "серна"; она была исполнена добрых дел и творила много милостынь.
\\
Случилось в те дни, что она занемогла и умерла. Ее омыли и положили в горнице.
\\
А как Лидда была близ Иоппии, то ученики, услышав, что Петр находится там, послали к нему двух человек просить, чтобы он не замедлил прийти к ним.
\\
Петр, встав, пошел с ними; и когда он прибыл, ввели его в горницу, и все вдовицы со слезами предстали перед ним, показывая рубашки и платья, какие делала Серна, живя с ними.
\\
Петр выслал всех вон и, преклонив колени, помолился, и, обратившись к телу, сказал: Тавифа! встань. И она открыла глаза свои и, увидев Петра, села.
\\
Он, подав ей руку, поднял ее, и, призвав святых и вдовиц, поставил ее перед ними живою.
\\
Это сделалось известным по всей Иоппии, и многие уверовали в Господа.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Acts 9:32--9:42.}\\
And it came to pass, as Peter passed throughout all quarters, he came down also to the saints which dwelt at Lydda.\\
And there he found a certain man named Aeneas, which had kept his bed eight years, and was sick of the palsy.\\
And Peter said unto him, Aeneas, Jesus Christ maketh thee whole: arise, and make thy bed. And he arose immediately.\\
And all that dwelt at Lydda and Saron saw him, and turned to the Lord.\\
Now there was at Joppa a certain disciple named Tabitha, which by interpretation is called Dorcas: this woman was full of good works and almsdeeds which she did.\\
And it came to pass in those days, that she was sick, and died: whom when they had washed, they laid her in an upper chamber.\\
And forasmuch as Lydda was nigh to Joppa, and the disciples had heard that Peter was there, they sent unto him two men, desiring him that he would not delay to come to them.\\
Then Peter arose and went with them. When he was come, they brought him into the upper chamber: and all the widows stood by him weeping, and shewing the coats and garments which Dorcas made, while she was with them.\\
But Peter put them all forth, and kneeled down, and prayed; and turning him to the body said, Tabitha, arise. And she opened her eyes: and when she saw Peter, she sat up.\\
And he gave her his hand, and lifted her up, and when he had called the saints and widows, presented her alive.\\
And it was known throughout all Joppa; and many believed in the Lord.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.05}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{使徒行傳 9:32--9:42.}\\
彼得周流四方的時候、也到了居住呂大的聖徒那裡。\\
遇見一個人、名叫以尼雅、得了癱瘓、在褥子上躺臥八年。\\
彼得對他說、以尼雅、耶穌基督醫好你了．起來、收拾你的褥子．他就立刻起來了。\\
凡住呂大和沙崙的人、都看見了他、就歸服主。\\
在約帕有一個女徒、名叫大比大、翻希利尼話、就是多加．〔多加就是羚羊的意思〕他廣行善事、多施賙濟。\\
當時、他患病而死．有人把他洗了、停在樓上。\\
呂大原與約帕相近．門徒聽見彼得在那裡、就打發兩個人去見他、央求他說、快到我們那裡去、不要耽延。\\
彼得就起身和他們同去．到了、便有人領他上樓．眾寡婦都站在彼得旁邊哭、拿多加與他們同在時、所做的裡衣外衣給他看。\\
彼得叫他們都出去、就跪下禱告、轉身對著死人說、大比大、起來、他就睜開眼睛、見了彼得、便坐起來。\\
彼得伸手扶他起來、叫眾聖徒和寡婦進去、把多加活活的交給他們。\\
這事傳遍了約帕、就有許多人信了主。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
