%simple
\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week Week 4 after Easter (Martyr)\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Евр., 335 зач., XIII, 17-21.}\\
\Large%for eng/rus
Повинуйтесь наставникам вашим и будьте покорны, ибо они неусыпно пекутся о душах ваших, как обязанные дать отчет; чтобы они делали это с радостью, а не воздыхая, ибо это для вас неполезно.
\\
Молитесь о нас; ибо мы уверены, что имеем добрую совесть, потому что во всем желаем вести себя честно.
\\
Особенно же прошу делать это, дабы я скорее возвращен был вам.
\\
Бог же мира, воздвигший из мертвых Пастыря овец великого Кровию завета вечного, Господа нашего Иисуса Христа,
\\
да усовершит вас во всяком добром деле, к исполнению воли Его, производя в вас благоугодное Ему через Иисуса Христа. Ему слава во веки веков! Аминь.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Hebrews 13:17--13:21.}\\
Obey them that have the rule over you, and submit yourselves: for they watch for your souls, as they that must give account, that they may do it with joy, and not with grief: for that is unprofitable for you.\\
Pray for us: for we trust we have a good conscience, in all things willing to live honestly.\\
But I beseech you the rather to do this, that I may be restored to you the sooner.\\
Now the God of peace, that brought again from the dead our Lord Jesus, that great shepherd of the sheep, through the blood of the everlasting covenant,\\
Make you perfect in every good work to do his will, working in you that which is wellpleasing in his sight, through Jesus Christ; to whom be glory for ever and ever. Amen.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{希伯來書 13:17--13:21.}\\
你們要依從那些引導你們的、且要順服．因他們為你們的靈魂時刻儆醒、好像那將來交賬的人．你們要使他們交的時候有快樂、不至憂愁．若憂愁就與你們無益了。\\
請你們為我們禱告．因我們自覺良心無虧、願意凡事按正道而行。\\
我更求你們為我禱告、使我快些回到你們那裡去。\\
但願賜平安的　神、就是那憑永約之血使群羊的大牧人我主耶穌、從死裡復活的　神、\\
在各樣善事上、成全你們、叫你們遵行他的旨意、又藉著耶穌基督在你們心裡行他所喜悅的事．願榮耀歸給他、直到永永遠遠。阿們。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
