\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.2in,bottom=0.2in,left=0.4in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 17 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\huge%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{2 Кор., 182 зач. (от полу́), VI, 16 - VII, 1.}\\
\huge%for eng/rus
Какая совместность храма Божия с идолами? Ибо вы храм Бога живаго, как сказал Бог: вселюсь в них и буду ходить в них; и буду их Богом, и они будут Моим народом.
\\
И потому выйдите из среды их и отделитесь, говорит Господь, и не прикасайтесь к нечистому; и Я прииму вас.
\\
И буду вам Отцем, и вы будете Моими сынами и дщерями, говорит Господь Вседержитель.
\\
Итак, возлюбленные, имея такие обетования, очистим себя от всякой скверны плоти и духа, совершая святыню в страхе Божием.
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{2 Corinthians 6:16--7:1.}\\
And what agreement hath the temple of God with idols? for ye are the temple of the living God; as God hath said, I will dwell in them, and walk in them; and I will be their God, and they shall be my people.\\
Wherefore come out from among them, and be ye separate, saith the Lord, and touch not the unclean thing; and I will receive you,\\
And will be a Father unto you, and ye shall be my sons and daughters, saith the Lord Almighty.\\
Having therefore these promises, dearly beloved, let us cleanse ourselves from all filthiness of the flesh and spirit, perfecting holiness in the fear of God.
\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\fontsize{35}{42}\selectfont
\textbf{
\fontsize{35}{42}\selectfont
哥林多後書 6:16--7:1.}\\
神的殿和偶像有甚麼相同呢．因為我們是永生　神的殿．就如　神曾說、『我要在他們中間居住、在他們中間來往．我要作他們的　神、他們要作我的子民。』\\
又說、『你們務要從他們中間出來、與他們分別、不要沾不潔淨的物、我就收納你們。\\
我要作你們的父、你們要作我的兒女。』這是全能的主說的。\\
親愛的弟兄阿、我們既有這等應許、就當潔淨自己、除去身體靈魂一切的污穢、敬畏　神、得以成聖。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
