\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[margin=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 21 after the Pentecost\vspace{-3ex}}
\date{\vspace{-5ex}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\large
\doublespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Гал., 203 зач., II, 16-20.}\\
однако же, узнав, что человек оправдывается не делами закона, а только верою в Иисуса Христа, и мы уверовали во Христа Иисуса, чтобы оправдаться верою во Христа, а не делами закона; ибо делами закона не оправдается никакая плоть.\\
Если же, ища оправдания во Христе, мы и сами оказались грешниками, то неужели Христос есть служитель греха? Никак.\\
Ибо если я снова созидаю, что разрушил, то сам себя делаю преступником.\\
Законом я умер для закона, чтобы жить для Бога. Я сораспялся Христу,\\
и уже не я живу, но живет во мне Христос. А что ныне живу во плоти, то живу верою в Сына Божия, возлюбившего меня и предавшего Себя за меня.\\
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Galatians 2:16 -- 2:20.}\\
Knowing that a man is not justified by the works of the law, but by the faith of Jesus Christ, even we have believed in Jesus Christ, that we might be justified by the faith of Christ, and not by the works of the law: for by the works of the law shall no flesh be justified.\\
But if, while we seek to be justified by Christ, we ourselves also are found sinners, is therefore Christ the minister of sin? God forbid.\\
For if I build again the things which I destroyed, I make myself a transgressor.\\
For I through the law am dead to the law, that I might live unto God.\\
I am crucified with Christ: nevertheless I live; yet not I, but Christ liveth in me: and the life which I now live in the flesh I live by the faith of the Son of God, who loved me, and gave himself for me.\\
\end{minipage}}
\newpage\huge
\doublespacing %for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{加拉太書 2:16 -- 2:20.}\\
可是我們知道，人稱義不是因律法的行為，而是因信耶穌基督(註)，我們也信了基督耶穌，為要使我們因信基督稱義，不因律法的行為稱義，因為，凡血肉之軀沒有一個能因律法的行為稱義。\\
我們若求在基督裏稱義，自己卻還被視為罪人，那麼，基督是罪的用人嗎？絕對不是！\\
如果我重新建造我所拆毀的，這就證明自己是違犯律法的人。\\
我因律法而向律法死了，使我可以向上帝活着。我已經與基督同釘十字架，\\
現在活着的不再是我，乃是基督在我裏面活着；並且我如今在肉身活着，是因信上帝的兒子而活；他是愛我，為我捨己。\\
\end{CJK}
\end{minipage}}
\end{document}
