\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[margin=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 27 after the Pentecost\vspace{-3ex}}
\date{\vspace{-5ex}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large
\onehalfspacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Кол., 257 зач., III, 4-11.}\\
\Large
Когда же явится Христос, жизнь ваша, тогда и вы явитесь с Ним во славе.\\
Итак, умертвите земные члены ваши: блуд, нечистоту, страсть, злую похоть и любостяжание, которое есть идолослужение,\\
за которые гнев Божий грядет на сынов противления,\\
в которых и вы некогда обращались, когда жили между ними.\\
А теперь вы отложите все: гнев, ярость, злобу, злоречие, сквернословие уст ваших;\\
не говорите лжи друг другу, совлекшись ветхого человека с делами его\\
и облекшись в нового, который обновляется в познании по образу Создавшего его,\\
где нет ни Еллина, ни Иудея, ни обрезания, ни необрезания, варвара, Скифа, раба, свободного, но все и во всем Христос. \\
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Colossians 3:4 -- 3:11.}\\
When Christ, who is our life, shall appear, then shall ye also appear with him in glory.\\
Mortify therefore your members which are upon the earth; fornication, uncleanness, inordinate affection, evil concupiscence, and covetousness, which is idolatry:\\
For which things' sake the wrath of God cometh on the children of disobedience:\\
In the which ye also walked some time, when ye lived in them.\\
But now ye also put off all these; anger, wrath, malice, blasphemy, filthy communication out of your mouth.\\
Lie not one to another, seeing that ye have put off the old man with his deeds;\\
And have put on the new man, which is renewed in knowledge after the image of him that created him:\\
Where there is neither Greek nor Jew, circumcision nor uncircumcision, Barbarian, Scythian, bond nor free: but Christ is all, and in all.\\
\end{minipage}}
\vspace*{\fill}
\newpage\Huge
\vspace*{\fill}
\onehalfspacing %for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{歌羅西書 3:4 -- 3:11.}\\
基督是你們的生命，他顯現的時候，你們也要與他一同在榮耀裏顯現。\\
所以，要治死你們在地上的肢體；就如淫亂、污穢、邪情、惡慾和貪婪—貪婪就是拜偶像。\\
因這些事，上帝的憤怒必臨到那些悖逆的人(註)。\\
當你們在這些事中活着的時候，你們的行為也曾是這樣的。\\
但現在你們要棄絕這一切的事，就是惱恨、憤怒、惡毒、毀謗和口中污穢的言語。\\
不要彼此說謊，因為你們已經脫去舊人和舊人的行為，\\
穿上了新人，這新人照着造他的主的形像在知識上不斷地更新。\\
在這事上並不分 希臘人和 猶太人，受割禮的和未受割禮的，未開化的人、 西古提人、為奴的、自主的；惟獨基督是一切，又在一切之內。 \\
\end{CJK}
\end{minipage}}
\vspace*{\fill}
\end{document}
