\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week about the Pharisee and the Publician\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{2 Тим., 296 зач., III, 10-15.}\\
\Large%for eng/rus
А ты последовал мне в учении, житии, расположении, вере, великодушии, любви, терпении,
\\
в гонениях, страданиях, постигших меня в Антиохии, Иконии, Листрах; каковые гонения я перенес, и от всех избавил меня Господь.
\\
Да и все, желающие жить благочестиво во Христе Иисусе, будут гонимы.
\\
Злые же люди и обманщики будут преуспевать во зле, вводя в заблуждение и заблуждаясь.
\\
А ты пребывай в том, чему научен и что тебе вверено, зная, кем ты научен.
\\
Притом же ты из детства знаешь священные писания, которые могут умудрить тебя во спасение верою во Христа Иисуса.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{2 Timothy 3:10--3:15.}\\
But thou hast fully known my doctrine, manner of life, purpose, faith, longsuffering, charity, patience,\\
Persecutions, afflictions, which came unto me at Antioch, at Iconium, at Lystra; what persecutions I endured: but out of them all the Lord delivered me.\\
Yea, and all that will live godly in Christ Jesus shall suffer persecution.\\
But evil men and seducers shall wax worse and worse, deceiving, and being deceived.\\
But continue thou in the things which thou hast learned and hast been assured of, knowing of whom thou hast learned them;\\
And that from a child thou hast known the holy scriptures, which are able to make thee wise unto salvation through faith which is in Christ Jesus.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{提摩太後書 3:10--3:15.}\\
但你已經服從了我的教訓、品行、志向、信心、寬容、愛心、忍耐、\\
以及我在安提阿、以哥念、路司得、所遭遇的逼迫、苦難．我所忍受是何等的逼迫．但從這一切苦難中、主都把我救出來了。\\
不但如此、凡立志在基督耶穌裡敬虔度日的、也都要受逼迫。\\
只是作惡的、和迷惑人的、必越久越惡、他欺哄人也被人欺哄。\\
但你所學習的、所確信的、要存在心裡．因為你知道是跟誰學的．\\
並且知道你是從小明白聖經．這聖經能使你因信基督耶穌有得救的智慧。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
