\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[margin=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 22 after the Pentecost\vspace{-3ex}}
\date{\vspace{-5ex}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\large
\doublespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Гал., 215 зач., VI, 11-18.}\\
Видите, как много написал я вам своею рукою.\\
Желающие хвалиться по плоти принуждают вас обрезываться только для того, чтобы не быть гонимыми за крест Христов,\\
ибо и сами обрезывающиеся не соблюдают закона, но хотят, чтобы вы обрезывались, дабы похвалиться в вашей плоти.\\
А я не желаю хвалиться, разве только крестом Господа нашего Иисуса Христа, которым для меня мир распят, и я для мира.\\
Ибо во Христе Иисусе ничего не значит ни обрезание, ни необрезание, а новая тварь.\\
Тем, которые поступают по сему правилу, мир им и милость, и Израилю Божию.\\
Впрочем никто не отягощай меня, ибо я ношу язвы Господа Иисуса на теле моем.\\
Благодать Господа нашего Иисуса Христа со духом вашим, братия. Аминь.\\
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Galatians 6:11 -- 6:18.}\\
Ye see how large a letter I have written unto you with mine own hand.\\
As many as desire to make a fair shew in the flesh, they constrain you to be circumcised; only lest they should suffer persecution for the cross of Christ.\\
For neither they themselves who are circumcised keep the law; but desire to have you circumcised, that they may glory in your flesh.\\
But God forbid that I should glory, save in the cross of our Lord Jesus Christ, by whom the world is crucified unto me, and I unto the world.\\
For in Christ Jesus neither circumcision availeth any thing, nor uncircumcision, but a new creature.\\
And as many as walk according to this rule, peace be on them, and mercy, and upon the Israel of God.\\
From henceforth let no man trouble me: for I bear in my body the marks of the Lord Jesus.\\
Brethren, the grace of our Lord Jesus Christ be with your spirit. Amen.\\
\end{minipage}}
\newpage\huge
\doublespacing %for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{加拉太書 6:11 -- 6:18.}\\
你們看我親手寫給你們的字是何等的大！\\
那些想要炫耀外表的人才勉強你們受割禮，無非是怕自己為基督的十字架受迫害。\\
他們那些受割禮的，連自己也不守律法；他們要你們受割禮，不過是要拿你們的肉體誇口。\\
但我絕不以別的誇口，只誇我們主耶穌基督的十字架；因這十字架(註)，就我而論，世界已經釘在十字架上；就世界而論，我已經釘在十字架上。\\
受割禮或不受割禮都無關緊要，要緊的就是作新造的人。\\
凡照這準則行的人，願平安(註)憐憫加給他們，和上帝的 以色列民。\\
從今以後，不要有人再攪擾我，因為我身上帶着耶穌的印記。\\
弟兄們，願我們主耶穌基督的恩與你們的靈同在。阿們！\\
\end{CJK}
\end{minipage}}
\end{document}
