%simple
\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 37 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{1 Тим., 285 зач. (от полу́), IV, 9-15.}\\
\Large%for eng/rus
Слово сие верно и всякого принятия достойно.
\\
Ибо мы для того и трудимся и поношения терпим, что уповаем на Бога живаго, Который есть Спаситель всех человеков, а наипаче верных.
\\
Проповедуй сие и учи.
\\
Никто да не пренебрегает юностью твоею; но будь образцом для верных в слове, в житии, в любви, в духе, в вере, в чистоте.
\\
Доколе не приду, занимайся чтением, наставлением, учением.
\\
Не неради о пребывающем в тебе даровании, которое дано тебе по пророчеству с возложением рук священства.
\\
О сем заботься, в сем пребывай, дабы успех твой для всех был очевиден.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{1 Timothy 4:9--4:15.}\\
This is a faithful saying and worthy of all acceptation.\\
For therefore we both labour and suffer reproach, because we trust in the living God, who is the Saviour of all men, specially of those that believe.\\
These things command and teach.\\
Let no man despise thy youth; but be thou an example of the believers, in word, in conversation, in charity, in spirit, in faith, in purity.\\
Till I come, give attendance to reading, to exhortation, to doctrine.\\
Neglect not the gift that is in thee, which was given thee by prophecy, with the laying on of the hands of the presbytery.\\
Meditate upon these things; give thyself wholly to them; that thy profiting may appear to all.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{提摩太前書 4:9--4:15.}\\
這話是可信的、是十分可佩服的。\\
我們勞苦努力、正是為此．因我們的指望在乎永生的　神．他是萬人的救主、更是信徒的救主。\\
這些事你要吩咐人、也要教導人。\\
不可叫人小看你年輕．總要在言語、行為、愛心、信心、清潔上．都作信徒的榜樣。\\
你要以宣讀、勸勉、教導為念、直等到我來。\\
你不要輕忽所得的恩賜、就是從前藉著預言、在眾長老按手的時候、賜給你的。\\
這些事你要殷勤去作、並要在此專心、使眾人看出你的長進來。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
