\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.1in,bottom=0.2in,left=0.2in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 8 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{1 Кор., 124 зач., I, 10-18.}\\
\Large%for eng/rus
Умоляю вас, братия, именем Господа нашего Иисуса Христа, чтобы все вы говорили одно, и не было между вами разделений, но чтобы вы соединены были в одном духе и в одних мыслях.
\\
Ибо от домашних Хлоиных сделалось мне известным о вас, братия мои, что между вами есть споры.
\\
Я разумею то, что у вас говорят: "я Павлов"; "я Аполлосов"; "я Кифин"; "а я Христов".
\\
Разве разделился Христос? разве Павел распялся за вас? или во имя Павла вы крестились?
\\
Благодарю Бога, что я никого из вас не крестил, кроме Криспа и Гаия,
\\
дабы не сказал кто, что я крестил в мое имя.
\\
Крестил я также Стефанов дом; а крестил ли еще кого, не знаю.
\\
Ибо Христос послал меня не крестить, а благовествовать, не в премудрости слова, чтобы не упразднить креста Христова.
\\
Ибо слово о кресте для погибающих юродство есть, а для нас, спасаемых,- сила Божия.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{1 Corinthians 1:10--1:18.}\\
Now I beseech you, brethren, by the name of our Lord Jesus Christ, that ye all speak the same thing, and that there be no divisions among you; but that ye be perfectly joined together in the same mind and in the same judgment.\\
For it hath been declared unto me of you, my brethren, by them which are of the house of Chloe, that there are contentions among you.\\
Now this I say, that every one of you saith, I am of Paul; and I of Apollos; and I of Cephas; and I of Christ.\\
Is Christ divided? was Paul crucified for you? or were ye baptized in the name of Paul?\\
I thank God that I baptized none of you, but Crispus and Gaius;\\
Lest any should say that I had baptized in mine own name.\\
And I baptized also the household of Stephanas: besides, I know not whether I baptized any other.\\
For Christ sent me not to baptize, but to preach the gospel: not with wisdom of words, lest the cross of Christ should be made of none effect.\\
For the preaching of the cross is to them that perish foolishness; but unto us which are saved it is the power of God.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{哥林多前書 1:10--1:18.}\\
弟兄們、我藉我們主耶穌基督的名、勸你們都說一樣的話．你們中間也不可分黨．只要一心一意彼此相合。\\
因為革來氏家裡的人、曾對我提起弟兄們來、說你們中間有分爭。\\
我的意思就是你們各人說、我是屬保羅的．我是屬亞波羅的．我是屬磯法的．我是屬基督的。\\
基督是分開的麼．保羅為你們釘了十字架麼．你們是奉保羅的名受了洗麼。\\
我感謝　神、除了基利司布並該猶以外、我沒有給你們一個人施洗．\\
免得有人說、你們是奉我的名受洗。\\
我也給司提反家施過洗．此外給別人施洗沒有、我卻記不清。\\
基督差遣我、原不是為施洗、乃是為傳福音．並不用智慧的言語、免得基督的十字架落了空。\\
因為十字架的道理、在那滅亡的人為愚拙．在我們得救的人卻為　神的大能。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
