\documentclass[14pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 36 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{1 Тим., 280 зач. (от полу́), I, 15-17.}\\
\Large%for eng/rus
Верно и всякого принятия достойно слово, что Христос Иисус пришел в мир спасти грешников, из которых я первый.
\\
Но для того я и помилован, чтобы Иисус Христос во мне первом показал все долготерпение, в пример тем, которые будут веровать в Него к жизни вечной.
\\
Царю же веков нетленному, невидимому, единому премудрому Богу честь и слава во веки веков. Аминь.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{1 Timothy 1:15--1:17.}\\
This is a faithful saying, and worthy of all acceptation, that Christ Jesus came into the world to save sinners; of whom I am chief.\\
Howbeit for this cause I obtained mercy, that in me first Jesus Christ might shew forth all longsuffering, for a pattern to them which should hereafter believe on him to life everlasting.\\
Now unto the King eternal, immortal, invisible, the only wise God, be honour and glory for ever and ever. Amen.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{提摩太前書 1:15--1:17.}\\
基督耶穌降世、為要拯救罪人．這話是可信的、是十分可佩服的．在罪人中我是個罪魁。\\
然而我蒙了憐憫、是因耶穌基督要在我這罪魁身上、顯明他一切的忍耐、給後來信他得永生的人作榜樣。\\
但願尊貴榮耀歸與那不能朽壞不能看見永世的君王、獨一的　神、直到永永遠遠。阿們。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
