%simple
\documentclass[12pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.3in,bottom=0.3in,left=0.3in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 2 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Рим., 81 зач. (от полу́), II, 10-16.}\\
\Large%for eng/rus
Напротив, слава и честь и мир всякому, делающему доброе, во-первых, Иудею, потом и Еллину!
\\
Ибо нет лицеприятия у Бога.
\\
Те, которые, не имея закона, согрешили, вне закона и погибнут; а те, которые под законом согрешили, по закону осудятся
\\
(потому что не слушатели закона праведны пред Богом, но исполнители закона оправданы будут,
\\
ибо когда язычники, не имеющие закона, по природе законное делают, то, не имея закона, они сами себе закон:
\\
они показывают, что дело закона у них написано в сердцах, о чем свидетельствует совесть их и мысли их, то обвиняющие, то оправдывающие одна другую)
\\
в день, когда, по благовествованию моему, Бог будет судить тайные дела человеков через Иисуса Христа.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Romans 2:10--2:16.}\\
But glory, honour, and peace, to every man that worketh good, to the Jew first, and also to the Gentile:\\
For there is no respect of persons with God.\\
For as many as have sinned without law shall also perish without law: and as many as have sinned in the law shall be judged by the law;\\
(For not the hearers of the law are just before God, but the doers of the law shall be justified.\\
For when the Gentiles, which have not the law, do by nature the things contained in the law, these, having not the law, are a law unto themselves:\\
Which shew the work of the law written in their hearts, their conscience also bearing witness, and their thoughts the mean while accusing or else excusing one another;)\\
In the day when God shall judge the secrets of men by Jesus Christ according to my gospel.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{羅馬書 2:10--2:16.}\\
卻將榮耀、尊貴、平安、加給一切行善的人、先是猶太人、後是希利尼人．\\
因為　神不偏待人。\\
凡沒有律法犯了罪的、也必不按律法滅亡．凡在律法以下犯了罪的、也必按律法受審判、\\
（原來在　神面前、不是聽律法的為義、乃是行律法的稱義．\\
沒有律法的外邦人、若順著本性行律法上的事、他們雖然沒有律法、自己就是自己的律法．\\
這是顯出律法的功用刻在他們心裡、他們是非之心同作見證、並且他們的思念互相較量、或以為是、或以為非）\\
就在　神藉耶穌基督審判人隱秘事的日子、照著我的福音所言。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
