\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 30 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Кол., 257 зач., III, 4-11.}\\
\Large%for eng/rus
Когда же явится Христос, жизнь ваша, тогда и вы явитесь с Ним во славе.
\\
Итак, умертвите земные члены ваши: блуд, нечистоту, страсть, злую похоть и любостяжание, которое есть идолослужение,
\\
за которые гнев Божий грядет на сынов противления,
\\
в которых и вы некогда обращались, когда жили между ними.
\\
А теперь вы отложите все: гнев, ярость, злобу, злоречие, сквернословие уст ваших;
\\
не говорите лжи друг другу, совлекшись ветхого человека с делами его
\\
и облекшись в нового, который обновляется в познании по образу Создавшего его,
\\
где нет ни Еллина, ни Иудея, ни обрезания, ни необрезания, варвара, Скифа, раба, свободного, но все и во всем Христос.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Colossians 3:4--3:11.}\\
When Christ, who is our life, shall appear, then shall ye also appear with him in glory.\\
Mortify therefore your members which are upon the earth; fornication, uncleanness, inordinate affection, evil concupiscence, and covetousness, which is idolatry:\\
For which things' sake the wrath of God cometh on the children of disobedience:\\
In the which ye also walked some time, when ye lived in them.\\
But now ye also put off all these; anger, wrath, malice, blasphemy, filthy communication out of your mouth.\\
Lie not one to another, seeing that ye have put off the old man with his deeds;\\
And have put on the new man, which is renewed in knowledge after the image of him that created him:\\
Where there is neither Greek nor Jew, circumcision nor uncircumcision, Barbarian, Scythian, bond nor free: but Christ is all, and in all.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.1}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{歌羅西書 3:4--3:11.}\\
基督是我們的生命、他顯現的時候、你們也要與他一同顯現在榮耀裡。\\
所以要治死你們在地上的肢體．就如淫亂、污穢、邪情、惡慾、和貪婪、貪婪就與拜偶像一樣。\\
因這些事、　神的忿怒必臨到那悖逆之子。\\
當你們在這些事中活著的時候、也曾這樣行過。\\
但現在你們要棄絕這一切的事、以及惱恨、忿怒、惡毒、〔或作陰毒〕毀謗、並口中污穢的言語。\\
不要彼此說謊．因你們已經脫去舊人、和舊人的行為、\\
穿上了新人．這新人在知識上漸漸更新、正如造他主的形像．\\
在此並不分希利尼人、猶太人、受割禮的、未受割禮的、化外人、西古提人、為奴的、自主的．惟有基督是包括一切、又住在各人之內。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
