\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.2in,bottom=0.1in,left=0.3in,right=0.3in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 2 of the Great Lent\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\onehalfspacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.48\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Евр., 304 зач., I, 10 - II, 3.}\\
\Large%for eng/rus
И: в начале Ты, Господи, основал землю, и небеса - дело рук Твоих;
\\
они погибнут, а Ты пребываешь; и все обветшают, как риза,
\\
и как одежду свернешь их, и изменятся; но Ты тот же, и лета Твои не кончатся.
\\
Кому когда из Ангелов сказал Бог: седи одесную Меня, доколе положу врагов Твоих в подножие ног Твоих?
\\
Не все ли они суть служебные духи, посылаемые на служение для тех, которые имеют наследовать спасение?
\\
Посему мы должны быть особенно внимательны к слышанному, чтобы не отпасть.
\\
Ибо, если через Ангелов возвещенное слово было твердо, и всякое преступление и непослушание получало праведное воздаяние,
\\
то как мы избежим, вознерадев о толиком спасении, которое, быв сначала проповедано Господом, в нас утвердилось слышавшими от Него,
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Hebrews 1:10--2:3.}\\
And, Thou, Lord, in the beginning hast laid the foundation of the earth; and the heavens are the works of thine hands:\\
They shall perish; but thou remainest; and they all shall wax old as doth a garment;\\
And as a vesture shalt thou fold them up, and they shall be changed: but thou art the same, and thy years shall not fail.\\
But to which of the angels said he at any time, Sit on my right hand, until I make thine enemies thy footstool?\\
Are they not all ministering spirits, sent forth to minister for them who shall be heirs of salvation?\\
Therefore we ought to give the more earnest heed to the things which we have heard, lest at any time we should let them slip.\\
For if the word spoken by angels was stedfast, and every transgression and disobedience received a just recompence of reward;\\
How shall we escape, if we neglect so great salvation; which at the first began to be spoken by the Lord, and was confirmed unto us by them that heard him;\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{希伯來書 1:10--2:3.}\\
又說、『主阿、你起初立了地的根基、天也是你手所造的．\\
天地都要滅沒、你卻要長存．天地都要像衣服漸漸舊了．\\
你要將天地捲起來、像一件外衣、天地就都改變了．惟有你永不改變、你的年數沒有窮盡。』\\
所有的天使、　神從來對那一個說、『你坐在我的右邊、等我使你仇敵作你的腳凳。』\\
天使豈不都是服役的靈、奉差遣為那將要承受救恩的人效力麼。\\
所以我們當越發鄭重所聽見的道理、恐怕我們隨流失去。\\
那藉著天使所傳的話、既是確定的、凡干犯悖逆的、都受了該受的報應．\\
我們若忽略這麼大的救恩、怎能逃罪呢．這救恩起先是主親自講的、後來是聽見的人給我們證實了．\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
