\documentclass[14pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.2in,bottom=0.2in,left=0.1in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 23 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 27 зач., VIII, 23-27.}\\
И когда вошел Он в лодку, за Ним последовали ученики Его.
\\
И вот, сделалось великое волнение на море, так что лодка покрывалась волнами; а Он спал.
\\
Тогда ученики Его, подойдя к Нему, разбудили Его и сказали: Господи! спаси нас, погибаем.
\\
И говорит им: что вы так боязливы, маловерные? Потом, встав, запретил ветрам и морю, и сделалась великая тишина.
\\
Люди же, удивляясь, говорили: кто это, что и ветры и море повинуются Ему?
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 8:23--8:27.}\\
And when he was entered into a ship, his disciples followed him.\\
And, behold, there arose a great tempest in the sea, insomuch that the ship was covered with the waves: but he was asleep.\\
And his disciples came to him, and awoke him, saying, Lord, save us: we perish.\\
And he saith unto them, Why are ye fearful, O ye of little faith? Then he arose, and rebuked the winds and the sea; and there was a great calm.\\
But the men marvelled, saying, What manner of man is this, that even the winds and the sea obey him!\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 8:23--8:27.}\\
耶穌上了船、門徒跟著他。\\
海裡忽然起了暴風、甚至船被波浪掩蓋．耶穌卻睡著了。\\
門徒來叫醒了他、說、主阿、救我們、我們喪命啦。\\
耶穌說、你們這小信的人哪、為甚麼膽怯呢．於是起來、斥責風和海、風和海就大大的平靜了。\\
眾人希奇說、這是怎樣的人、連風和海也聽從他了。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
