\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 6 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\onehalfspacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Рим., 110 зач., XII, 6-14.}\\
\Large%for eng/rus
И как, по данной нам благодати, имеем различные дарования, то, имеешь ли пророчество, пророчествуй по мере веры;
\\
имеешь ли служение, пребывай в служении; учитель ли,- в учении;
\\
увещатель ли, увещевай; раздаватель ли, раздавай в простоте; начальник ли, начальствуй с усердием; благотворитель ли, благотвори с радушием.
\\
Любовь да будет непритворна; отвращайтесь зла, прилепляйтесь к добру;
\\
будьте братолюбивы друг к другу с нежностью; в почтительности друг друга предупреждайте;
\\
в усердии не ослабевайте; духом пламенейте; Господу служите;
\\
утешайтесь надеждою; в скорби будьте терпеливы, в молитве постоянны;
\\
в нуждах святых принимайте участие; ревнуйте о странноприимстве.
\\
Благословляйте гонителей ваших; благословляйте, а не проклинайте.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Romans 12:6--12:14.}\\
Having then gifts differing according to the grace that is given to us, whether prophecy, let us prophesy according to the proportion of faith;\\
Or ministry, let us wait on our ministering: or he that teacheth, on teaching;\\
Or he that exhorteth, on exhortation: he that giveth, let him do it with simplicity; he that ruleth, with diligence; he that sheweth mercy, with cheerfulness.\\
Let love be without dissimulation. Abhor that which is evil; cleave to that which is good.\\
Be kindly affectioned one to another with brotherly love; in honour preferring one another;\\
Not slothful in business; fervent in spirit; serving the Lord;\\
Rejoicing in hope; patient in tribulation; continuing instant in prayer;\\
Distributing to the necessity of saints; given to hospitality.\\
Bless them which persecute you: bless, and curse not.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.45}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{羅馬書 12:6--12:14.}\\
按我們所得的恩賜、各有不同．或說預言、就當照著信心的程度說預言．\\
或作執事、就當專一執事．或作教導的、就當專一教導．\\
或作勸化的、就當專一勸化．施捨的、就當誠實．治理的、就當殷勤．憐憫人的、就當甘心。\\
愛人不可虛假、惡要厭惡、善要親近。\\
愛弟兄、要彼此親熱．恭敬人、要彼此推讓。\\
殷勤不可懶惰．要心裡火熱．常常服事主。\\
在指望中要喜樂．在患難中要忍耐。禱告要恆切．\\
聖徒缺乏要幫補．客要一味的款待。\\
逼迫你們的、要給他們祝福．只要祝福、不可咒詛。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
