\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 4 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\onehalfspacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Рим., 93 зач., VI, 18-23.}\\
\Large%for eng/rus
Освободившись же от греха, вы стали рабами праведности.
\\
Говорю по рассуждению человеческому, ради немощи плоти вашей. Как предавали вы члены ваши в рабы нечистоте и беззаконию на дела беззаконные, так ныне представьте члены ваши в рабы праведности на дела святые.
\\
Ибо, когда вы были рабами греха, тогда были свободны от праведности.
\\
Какой же плод вы имели тогда? Такие дела, каких ныне сами стыдитесь, потому что конец их - смерть.
\\
Но ныне, когда вы освободились от греха и стали рабами Богу, плод ваш есть святость, а конец - жизнь вечная.
\\
Ибо возмездие за грех - смерть, а дар Божий - жизнь вечная во Христе Иисусе, Господе нашем.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Romans 6:18--6:23.}\\
Being then made free from sin, ye became the servants of righteousness.\\
I speak after the manner of men because of the infirmity of your flesh: for as ye have yielded your members servants to uncleanness and to iniquity unto iniquity; even so now yield your members servants to righteousness unto holiness.\\
For when ye were the servants of sin, ye were free from righteousness.\\
What fruit had ye then in those things whereof ye are now ashamed? for the end of those things is death.\\
But now being made free from sin, and become servants to God, ye have your fruit unto holiness, and the end everlasting life.\\
For the wages of sin is death; but the gift of God is eternal life through Jesus Christ our Lord.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{羅馬書 6:18--6:23.}\\
你們既從罪裡得了釋放、就作了義的奴僕。\\
我因你們肉體的軟弱、就照人的常話對你們說、你們從前怎樣將肢體獻給不潔不法作奴僕、以至於不法．現今也要照樣將肢體獻給義作奴僕、以至於成聖．\\
因為你們作罪之奴僕的時候、就不被義約束了。\\
你們現今所看為羞恥的事、當日有甚麼果子呢．那些事的結局就是死。\\
但現今你們既從罪裡得了釋放、作了　神的奴僕、就有成聖的果子、那結局就是永生。\\
因為罪的工價乃是死．惟有　神的恩賜、在我們的主基督耶穌裡、乃是永生。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
