\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.3in,bottom=0.2in,left=0.3in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 28 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\LARGE%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Кол., 250 зач., I, 12-18.}\\
\LARGE%for eng/rus
благодаря Бога и Отца, призвавшего нас к участию в наследии святых во свете,
\\
избавившего нас от власти тьмы и введшего в Царство возлюбленного Сына Своего,
\\
в Котором мы имеем искупление Кровию Его и прощение грехов,
\\
Который есть образ Бога невидимого, рожденный прежде всякой твари;
\\
ибо Им создано всё, что на небесах и что на земле, видимое и невидимое: престолы ли, господства ли, начальства ли, власти ли,- все Им и для Него создано;
\\
и Он есть прежде всего, и все Им стоит.
\\
И Он есть глава тела Церкви; Он - начаток, первенец из мертвых, дабы иметь Ему во всем первенство,
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Colossians 1:12--1:18.}\\
Giving thanks unto the Father, which hath made us meet to be partakers of the inheritance of the saints in light:\\
Who hath delivered us from the power of darkness, and hath translated us into the kingdom of his dear Son:\\
In whom we have redemption through his blood, even the forgiveness of sins:\\
Who is the image of the invisible God, the firstborn of every creature:\\
For by him were all things created, that are in heaven, and that are in earth, visible and invisible, whether they be thrones, or dominions, or principalities, or powers: all things were created by him, and for him:\\
And he is before all things, and by him all things consist.\\
And he is the head of the body, the church: who is the beginning, the firstborn from the dead; that in all things he might have the preeminence.
\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{歌羅西書 1:12--1:18.}\\
又感謝父、叫我們能與眾聖徒在光明中同得基業．\\
他救了我們脫離黑暗的權勢、把我們遷到他愛子的國裡．\\
我們在愛子裡得蒙救贖、罪過得以赦免。\\
愛子是那不能看見之　神的像、是首生的、在一切被造的以先．\\
因為萬有都是靠他造的、無論是天上的、地上的、能看見的、不能看見的、或是有位的、主治的、執政的、掌權的、一概都是藉著他造的、又是為他造的．\\
他在萬有之先．萬有也靠他而立。\\
他也是教會全體之首．他是元始、是從死裡首先復生的、使他可以在凡事上居首位。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
