%simple
\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.3in,bottom=0.3in,left=0.3in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles1}
\author{Week about the Prodigal Son\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{1 Кор., 135 зач., VI, 12-20.}\\
\Large%for eng/rus
Все мне позволительно, но не все полезно; все мне позволительно, но ничто не должно обладать мною.
\\
Пища для чрева, и чрево для пищи; но Бог уничтожит и то и другое. Тело же не для блуда, но для Господа, и Господь для тела.
\\
Бог воскресил Господа, воскресит и нас силою Своею.
\\
Разве не знаете, что тела ваши суть члены Христовы? Итак отниму ли члены у Христа, чтобы сделать их членами блудницы? Да не будет!
\\
Или не знаете, что совокупляющийся с блудницею становится одно тело с нею? ибо сказано: два будут одна плоть.
\\
А соединяющийся с Господом есть один дух с Господом.
\\
Бегайте блуда; всякий грех, какой делает человек, есть вне тела, а блудник грешит против собственного тела.
\\
Не знаете ли, что тела ваши суть храм живущего в вас Святаго Духа, Которого имеете вы от Бога, и вы не свои?
\\
Ибо вы куплены дорогою ценою. || Посему прославляйте Бога и в телах ваших и в душах ваших, которые суть Божии.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{1 Corinthians 6:12--6:20.}\\
All things are lawful unto me, but all things are not expedient: all things are lawful for me, but I will not be brought under the power of any.\\
Meats for the belly, and the belly for meats: but God shall destroy both it and them. Now the body is not for fornication, but for the Lord; and the Lord for the body.\\
And God hath both raised up the Lord, and will also raise up us by his own power.\\
Know ye not that your bodies are the members of Christ? shall I then take the members of Christ, and make them the members of an harlot? God forbid.\\
What? know ye not that he which is joined to an harlot is one body? for two, saith he, shall be one flesh.\\
But he that is joined unto the Lord is one spirit.\\
Flee fornication. Every sin that a man doeth is without the body; but he that committeth fornication sinneth against his own body.\\
What? know ye not that your body is the temple of the Holy Ghost which is in you, which ye have of God, and ye are not your own?\\
For ye are bought with a price: therefore glorify God in your body, and in your spirit, which are God's.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.1}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{哥林多前書 6:12--6:20.}\\
凡事我都可行．但不都有益處。凡事我都可行、但無論那一件、我總不受他的轄制。\\
食物是為肚腹、肚腹是為食物．但　神要叫這兩樣都廢壞。身子不是為淫亂、乃是為主．主也是為身子．\\
並且　神已經叫主復活、也要用自己的能力叫我們復活。\\
豈不知你們的身子是基督的肢體麼．我可以將基督的肢體作為娼妓的肢體麼．斷乎不可。\\
豈不知與娼妓聯合的、便是與他成為一體麼．因為主說、『二人要成為一體。』\\
但與主聯合的、便是與主成為一靈。\\
你們要逃避淫行。人所犯的、無論甚麼罪、都在身子以外．惟有行淫的、是得罪自己的身子。\\
豈不知你們的身子就是聖靈的殿麼．這聖靈是從　神而來、住在你們裡頭的．並且你們不是自己的人．\\
因為你們是重價買來的．所以要在你們的身子上榮耀　神。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
