\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.2in,bottom=0.2in,left=0.1in,right=0.3in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{setspace}
\title{Divine Liturgy\\Reading from The Epistles}
\author{Week 9 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{1 Кор., 128 зач., III, 9-17.}\\
\Large%for eng/rus
Ибо мы соработники у Бога, а вы Божия нива, Божие строение.
\\
Я, по данной мне от Бога благодати, как мудрый строитель, положил основание, а другой строит на нем; но каждый смотри, как строит.
\\
Ибо никто не может положить другого основания, кроме положенного, которое есть Иисус Христос.
\\
Строит ли кто на этом основании из золота, серебра, драгоценных камней, дерева, сена, соломы,-
\\
каждого дело обнаружится; ибо день покажет, потому что в огне открывается, и огонь испытает дело каждого, каково оно есть.
\\
У кого дело, которое он строил, устоит, тот получит награду.
\\
А у кого дело сгорит, тот потерпит урон; впрочем сам спасется, но так, как бы из огня.
\\
Разве не знаете, что вы храм Божий, и Дух Божий живет в вас?
\\
Если кто разорит храм Божий, того покарает Бог: ибо храм Божий свят; а этот храм - вы.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{1 Corinthians 3:9--3:17.}\\
For we are labourers together with God: ye are God's husbandry, ye are God's building.\\
According to the grace of God which is given unto me, as a wise masterbuilder, I have laid the foundation, and another buildeth thereon. But let every man take heed how he buildeth thereupon.\\
For other foundation can no man lay than that is laid, which is Jesus Christ.\\
Now if any man build upon this foundation gold, silver, precious stones, wood, hay, stubble;\\
Every man's work shall be made manifest: for the day shall declare it, because it shall be revealed by fire; and the fire shall try every man's work of what sort it is.\\
If any man's work abide which he hath built thereupon, he shall receive a reward.\\
If any man's work shall be burned, he shall suffer loss: but he himself shall be saved; yet so as by fire.\\
Know ye not that ye are the temple of God, and that the Spirit of God dwelleth in you?\\
If any man defile the temple of God, him shall God destroy; for the temple of God is holy, which temple ye are.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}%for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{哥林多前書 3:9--3:17.}\\
因為我們是與　神同工的．你們是　神所耕種的田地、所建造的房屋。\\
我照　神所給我的恩、好像一個聰明的工頭、立好了根基、有別人在上面建造．只是各人要謹慎怎樣在上面建造。\\
因為那已經立好的根基、就是耶穌基督、此外沒有人能立別的根基。\\
若有人用金、銀、寶石、草木、禾楷、在這根基上建造．\\
各人的工程必然顯露．因為那日子要將他表明出來、有火發現．這火要試驗各人的工程怎樣。\\
人在那根基上所建造的工程、若存得住、他就要得賞賜。\\
人的工程若被燒了、他就要受虧損．自己卻要得救．雖然得救乃像從火裡經過的一樣。\\
豈不知你們是　神的殿、　神的靈住在你們裡頭麼。\\
若有人毀壞　神的殿、　神必要毀壞那人．因為　神的殿是聖的、這殿就是你們。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
