\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[bottom=0.5in,left=0.5in,right=0.5in,top=0.1in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 29 after the Pentecost\vspace{-8ex}}
\date{\vspace{-9ex}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large
\singlespacing %\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 4 зач., II, 13-23.}\\
Когда же они отошли,- се, Ангел Господень является во сне Иосифу и говорит: встань, возьми Младенца и Матерь Его и беги в Египет, и будь там, доколе не скажу тебе, ибо Ирод хочет искать Младенца, чтобы погубить Его.\\
Он встал, взял Младенца и Матерь Его ночью и пошел в Египет,\\
и там был до смерти Ирода, да сбудется реченное Господом через пророка, который говорит: из Египта воззвал Я Сына Моего.\\
Тогда Ирод, увидев себя осмеянным волхвами, весьма разгневался, и послал избить всех младенцев в Вифлееме и во всех пределах его, от двух лет и ниже, по времени, которое выведал от волхвов.\\
Тогда сбылось реченное через пророка Иеремию, который говорит:\\
глас в Раме слышен, плач и рыдание и вопль великий; Рахиль плачет о детях своих и не хочет утешиться, ибо их нет.\\
По смерти же Ирода,- се, Ангел Господень во сне является Иосифу в Египте\\
и говорит: встань, возьми Младенца и Матерь Его и иди в землю Израилеву, ибо умерли искавшие души Младенца.\\
Он встал, взял Младенца и Матерь Его и пришел в землю Израилеву.\\
Услышав же, что Архелай царствует в Иудее вместо Ирода, отца своего, убоялся туда идти; но, получив во сне откровение, пошел в пределы Галилейские\\
и, придя, поселился в городе, называемом Назарет, да сбудется реченное через пророков, что Он Назореем наречется. \\
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 2:13 -- 2:23.}\\
And when they were departed, behold, the angel of the Lord appeareth to Joseph in a dream, saying, Arise, and take the young child and his mother, and flee into Egypt, and be thou there until I bring thee word: for Herod will seek the young child to destroy him.\\
When he arose, he took the young child and his mother by night, and departed into Egypt:\\
And was there until the death of Herod: that it might be fulfilled which was spoken of the Lord by the prophet, saying, Out of Egypt have I called my son.\\
Then Herod, when he saw that he was mocked of the wise men, was exceeding wroth, and sent forth, and slew all the children that were in Bethlehem, and in all the coasts thereof, from two years old and under, according to the time which he had diligently enquired of the wise men.\\
Then was fulfilled that which was spoken by Jeremy the prophet, saying,\\
In Rama was there a voice heard, lamentation, and weeping, and great mourning, Rachel weeping for her children, and would not be comforted, because they are not.\\
But when Herod was dead, behold, an angel of the Lord appeareth in a dream to Joseph in Egypt,\\
Saying, Arise, and take the young child and his mother, and go into the land of Israel: for they are dead which sought the young child's life.\\
And he arose, and took the young child and his mother, and came into the land of Israel.\\
But when he heard that Archelaus did reign in Judaea in the room of his father Herod, he was afraid to go thither: notwithstanding, being warned of God in a dream, he turned aside into the parts of Galilee:\\
And he came and dwelt in a city called Nazareth: that it might be fulfilled which was spoken by the prophets, He shall be called a Nazarene.\\
\end{minipage}}
\vspace*{\fill}
\newpage\huge
\vspace*{\fill}
\singlespacing %for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 2:13 -- 2:23.}\\
他們走後，忽然主的使者在 約瑟夢中向他顯現，說：「起來！帶着小孩子和他母親逃往 埃及，住在那裏，等我的指示；因為 希律要搜尋那小孩子來殺害他。」\\
約瑟就起來，連夜帶着小孩子和他母親往 埃及去，\\
住在那裏，直到 希律死了。這是要應驗主藉先知所說的話：「我從 埃及召我的兒子出來。」\\
希律見自己被博學之士愚弄，極其憤怒，差人將 伯利恆城裏和四境所有的男孩，根據他向博學之士仔細查問到的時間，凡兩歲以內的，都殺盡了。\\
這就應驗了 耶利米先知所說的話：\\
「在 拉瑪聽見號咷大哭的聲音，\\
是 拉結哭她兒女；\\
她不肯受安慰，\\
因為他們都不在了。」\\
希律死了以後，在 埃及，忽然主的使者在 約瑟夢中向他顯現，\\
說：「起來，帶着小孩子和他母親回 以色列地去！因為要殺害這小孩子的人已經死了。」\\
約瑟就起來，帶着小孩子和他母親進入 以色列地去。\\
但是他因聽見 亞基老繼承他父親 希律作了 猶太王，怕到那裏去；又在夢中得到主的指示，就往 加利利境內去了。\\
他們到了一座城，名叫 拿撒勒，就住在那裏。這是要應驗先知所說的話：「他將稱為 拿撒勒人。」 \\
\end{CJK}
\end{minipage}}
\vspace*{\fill}
\end{document}
