\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.2in,bottom=0.2in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 4 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 25 зач., VIII, 5-13.}\\
Когда же вошел Иисус в Капернаум, к Нему подошел сотник и просил Его:
\\
Господи! слуга мой лежит дома в расслаблении и жестоко страдает.
\\
Иисус говорит ему: Я приду и исцелю его.
\\
Сотник же, отвечая, сказал: Господи! я недостоин, чтобы Ты вошел под кров мой, но скажи только слово, и выздоровеет слуга мой;
\\
ибо я и подвластный человек, но, имея у себя в подчинении воинов, говорю одному: пойди, и идет; и другому: приди, и приходит; и слуге моему: сделай то, и делает.
\\
Услышав сие, Иисус удивился и сказал идущим за Ним: истинно говорю вам, и в Израиле не нашел Я такой веры.
\\
Говорю же вам, что многие придут с востока и запада и возлягут с Авраамом, Исааком и Иаковом в Царстве Небесном;
\\
а сыны царства извержены будут во тьму внешнюю: там будет плач и скрежет зубов.
\\
И сказал Иисус сотнику: иди, и, как ты веровал, да будет тебе. И выздоровел слуга его в тот час.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 8:5--8:13.}\\
And when Jesus was entered into Capernaum, there came unto him a centurion, beseeching him,\\
And saying, Lord, my servant lieth at home sick of the palsy, grievously tormented.\\
And Jesus saith unto him, I will come and heal him.\\
The centurion answered and said, Lord, I am not worthy that thou shouldest come under my roof: but speak the word only, and my servant shall be healed.\\
For I am a man under authority, having soldiers under me: and I say to this man, Go, and he goeth; and to another, Come, and he cometh; and to my servant, Do this, and he doeth it.\\
When Jesus heard it, he marvelled, and said to them that followed, Verily I say unto you, I have not found so great faith, no, not in Israel.\\
And I say unto you, That many shall come from the east and west, and shall sit down with Abraham, and Isaac, and Jacob, in the kingdom of heaven.\\
But the children of the kingdom shall be cast out into outer darkness: there shall be weeping and gnashing of teeth.\\
And Jesus said unto the centurion, Go thy way; and as thou hast believed, so be it done unto thee. And his servant was healed in the selfsame hour.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 8:5--8:13.}\\
耶穌進了迦百農、有一個百夫長進前來、求他說、\\
主阿、我的僕人害癱瘓病、躺在家裡、甚是疼苦。\\
耶穌說、我去醫治他。\\
百夫長回答說、主阿、你到我舍下、我不敢當．只要你說一句話、我的僕人就必好了。\\
因為我在人的權下、也有兵在我以下．對這個說、去、他就去．對那個說、來、他就來．對我的僕人說、你作這事、他就去作。\\
耶穌聽見就希奇、對跟從的人說、我實在告訴你們、這麼大的信心、就是在以色列中、我也沒有遇見過。\\
我又告訴你們、從東從西、將有許多人來、在天國裡與亞伯拉罕、以撒、雅各、一同坐席．\\
惟有本國的子民、竟被趕到外邊黑暗裡去．在那裡必要哀哭切齒了。\\
耶穌對百夫長說、你回去罷．照你的信心、給你成全了。那時、他的僕人就好了。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
