\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.05in,bottom=0.05in,left=-0.05in,right=0.3in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{\vspace{-4.5ex}Divine Liturgy\\Reading from The Gospels\vspace{-0.5ex}}
\author{Week 9 after the Pentecost\vspace{
-7.5ex%for author
}}
\date{\vspace{
-10ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 59 зач., XIV, 22-34.}\\
И тотчас понудил Иисус учеников Своих войти в лодку и отправиться прежде Его на другую сторону, пока Он отпустит народ.
\\
И, отпустив народ, Он взошел на гору помолиться наедине; и вечером оставался там один.
\\
А лодка была уже на средине моря, и ее било волнами, потому что ветер был противный.
\\
В четвертую же стражу ночи пошел к ним Иисус, идя по морю.
\\
И ученики, увидев Его идущего по морю, встревожились и говорили: это призрак; и от страха вскричали.
\\
Но Иисус тотчас заговорил с ними и сказал: ободритесь; это Я, не бойтесь.
\\
Петр сказал Ему в ответ: Господи! если это Ты, повели мне прийти к Тебе по воде.
\\
Он же сказал: иди. И, выйдя из лодки, Петр пошел по воде, чтобы подойти к Иисусу,
\\
но, видя сильный ветер, испугался и, начав утопать, закричал: Господи! спаси меня.
\\
Иисус тотчас простер руку, поддержал его и говорит ему: маловерный! зачем ты усомнился?
\\
И, когда вошли они в лодку, ветер утих.
\\
Бывшие же в лодке подошли, поклонились Ему и сказали: истинно Ты Сын Божий.
\\
И, переправившись, прибыли в землю Геннисаретскую.
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 14:22--14:34.}\\
And straightway Jesus constrained his disciples to get into a ship, and to go before him unto the other side, while he sent the multitudes away.\\
And when he had sent the multitudes away, he went up into a mountain apart to pray: and when the evening was come, he was there alone.\\
But the ship was now in the midst of the sea, tossed with waves: for the wind was contrary.\\
And in the fourth watch of the night Jesus went unto them, walking on the sea.\\
And when the disciples saw him walking on the sea, they were troubled, saying, It is a spirit; and they cried out for fear.\\
But straightway Jesus spake unto them, saying, Be of good cheer; it is I; be not afraid.\\
And Peter answered him and said, Lord, if it be thou, bid me come unto thee on the water.\\
And he said, Come. And when Peter was come down out of the ship, he walked on the water, to go to Jesus.\\
But when he saw the wind boisterous, he was afraid; and beginning to sink, he cried, saying, Lord, save me.\\
And immediately Jesus stretched forth his hand, and caught him, and said unto him, O thou of little faith, wherefore didst thou doubt?\\
And when they were come into the ship, the wind ceased.\\
Then they that were in the ship came and worshipped him, saying, Of a truth thou art the Son of God.\\
And when they were gone over, they came into the land of Gennesaret.
\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.05}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 14:22--14:34.}\\
耶穌隨即催門徒上船、先渡到那邊去、等他叫眾人散開。\\
散了眾人以後、他就獨自上山去禱告．到了晚上、只有他一人在那裡。\\
那時船在海中、因風不順、被浪搖撼。\\
夜裡四更天、耶穌在海面上走、往門徒那裡去。\\
門徒看見他在海面上走、就驚慌了、說、是個鬼怪．便害怕、喊叫起來。\\
耶穌連忙對他們說、你們放心．是我、不要怕。\\
彼得說、主、如果是你、請叫我從水面上走到你那裡去。\\
耶穌說、你來罷。彼得就從船上下去、在水面上走、要到耶穌那裡去．\\
只因見風甚大、就害怕．將要沉下去、便喊著說、主阿、救我。\\
耶穌趕緊伸手拉住他、說、你這小信的人哪、為甚麼疑惑呢。\\
他們上了船、風就住了。\\
在船上的人都拜他說、你真是　神的兒子了。\\
他們過了海、來到革尼撒勒地方。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
