\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.2in,bottom=-0.0in,left=0.1in,right=0.4in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{\vspace{-4ex}Divine Liturgy\\Reading from The Gospels\vspace{-0ex}}
\author{Week 12 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-13ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 63 зач., XII, 2-12.}\\
Нет ничего сокровенного, что не открылось бы, и тайного, чего не узнали бы.
\\
Посему, что вы сказали в темноте, то услышится во свете; и что говорили на ухо внутри дома, то будет провозглашено на кровлях.
\\
Говорю же вам, друзьям Моим: не бойтесь убивающих тело и потом не могущих ничего более сделать;
\\
но скажу вам, кого бояться: бойтесь того, кто, по убиении, может ввергнуть в геенну: ей, говорю вам, того бойтесь.
\\
Не пять ли малых птиц продаются за два ассария? и ни одна из них не забыта у Бога.
\\
А у вас и волосы на голове все сочтены. Итак не бойтесь: вы дороже многих малых птиц.
\\
Сказываю же вам: всякого, кто исповедает Меня пред человеками, и Сын Человеческий исповедает пред Ангелами Божиими;
\\
а кто отвергнется Меня пред человеками, тот отвержен будет пред Ангелами Божиими.
\\
И всякому, кто скажет слово на Сына Человеческого, прощено будет; а кто скажет хулу на Святаго Духа, тому не простится.
\\
Когда же приведут вас в синагоги, к начальствам и властям, не заботьтесь, как или что отвечать, или что говорить,
\\
ибо Святый Дух научит вас в тот час, что должно говорить.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 12:2--12:12.}\\
For there is nothing covered, that shall not be revealed; neither hid, that shall not be known.\\
Therefore whatsoever ye have spoken in darkness shall be heard in the light; and that which ye have spoken in the ear in closets shall be proclaimed upon the housetops.\\
And I say unto you my friends, Be not afraid of them that kill the body, and after that have no more that they can do.\\
But I will forewarn you whom ye shall fear: Fear him, which after he hath killed hath power to cast into hell; yea, I say unto you, Fear him.\\
Are not five sparrows sold for two farthings, and not one of them is forgotten before God?\\
But even the very hairs of your head are all numbered. Fear not therefore: ye are of more value than many sparrows.\\
Also I say unto you, Whosoever shall confess me before men, him shall the Son of man also confess before the angels of God:\\
But he that denieth me before men shall be denied before the angels of God.\\
And whosoever shall speak a word against the Son of man, it shall be forgiven him: but unto him that blasphemeth against the Holy Ghost it shall not be forgiven.\\
And when they bring you unto the synagogues, and unto magistrates, and powers, take ye no thought how or what thing ye shall answer, or what ye shall say:\\
For the Holy Ghost shall teach you in the same hour what ye ought to say.
\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 12:2--12:12.}\\
掩蓋的事、沒有不露出來的．隱藏的事、沒有不被人知道的。\\
因此你們在暗中所說的、將要在明處被人聽見．在內室附耳所說的、將要在房上被人宣揚。\\
我的朋友、我對你們說、那殺身體以後、不能再作甚麼的、不要怕他們。\\
我要指示你們當怕的是誰．當怕那殺了以後、又有權柄丟在地獄裡的．我實在告訴你們、正要怕他。\\
五個麻雀、不是賣二分銀子麼．但在　神面前、一個也不忘記。\\
就是你們的頭髮也都被數過了．不要懼怕、你們比許多麻雀還貴重。\\
我又告訴你們、凡在人面前認我的、人子在　神的使者面前也必認他．\\
在人面前不認我的、人子在　神的使者面前也必不認他。\\
凡說話干犯人子的、還可得赦免、惟獨褻瀆聖靈的、總不得赦免。\\
人帶你們到會堂、並官府、和有權柄的人面前、不要思慮怎麼分訴、說甚麼話．\\
因為正在那時候、聖靈要指教你們當說的話。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
