\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.3in,bottom=0.2in,left=0.3in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 28 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\LARGE%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\LARGE%for eng/rus
\textbf{Лк., 85 зач., XVII, 12-19.}\\
И когда входил Он в одно селение, встретили Его десять человек прокаженных, которые остановились вдали
\\
и громким голосом говорили: Иисус Наставник! помилуй нас.
\\
Увидев их, Он сказал им: пойдите, покажитесь священникам. И когда они шли, очистились.
\\
Один же из них, видя, что исцелен, возвратился, громким голосом прославляя Бога,
\\
и пал ниц к ногам Его, благодаря Его; и это был Самарянин.
\\
Тогда Иисус сказал: не десять ли очистились? где же девять?
\\
как они не возвратились воздать славу Богу, кроме сего иноплеменника?
\\
И сказал ему: встань, иди; вера твоя спасла тебя.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 17:12--17:19.}\\
And as he entered into a certain village, there met him ten men that were lepers, which stood afar off:\\
And they lifted up their voices, and said, Jesus, Master, have mercy on us.\\
And when he saw them, he said unto them, Go shew yourselves unto the priests. And it came to pass, that, as they went, they were cleansed.\\
And one of them, when he saw that he was healed, turned back, and with a loud voice glorified God,\\
And fell down on his face at his feet, giving him thanks: and he was a Samaritan.\\
And Jesus answering said, Were there not ten cleansed? but where are the nine?\\
There are not found that returned to give glory to God, save this stranger.\\
And he said unto him, Arise, go thy way: thy faith hath made thee whole.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 17:12--17:19.}\\
進入一個村子、有十個長大痲瘋的迎面而來、遠遠的站著。\\
高聲說、耶穌、夫子、可憐我們罷。\\
耶穌看見、就對他們說、你們去把身體給祭司察看。他們去的時候就潔淨了。\\
內中有一個見自己已經好了、就回來大聲歸榮耀與　神．\\
又俯伏在耶穌腳前感謝他．這人是撒瑪利亞人。\\
耶穌說、潔淨了的不是十個人麼．那九個在哪裡呢。\\
除了這外族人、再沒有別人回來歸榮耀與　神麼。\\
就對那人說、起來走罷．你的信救了你了。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
