%simple
\documentclass[12pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 24 after the Pentecost (Theotokos)\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 54 зач., X, 38-42; XI, 27-28.}\\
В продолжение пути их пришел Он в одно селение; здесь женщина, именем Марфа, приняла Его в дом свой;
\\
у неё была сестра, именем Мария, которая села у ног Иисуса и слушала слово Его.
\\
Марфа же заботилась о большом угощении и, подойдя, сказала: Господи! или Тебе нужды нет, что сестра моя одну меня оставила служить? скажи ей, чтобы помогла мне.
\\
Иисус же сказал ей в ответ: Марфа! Марфа! ты заботишься и суетишься о многом,
\\
а одно только нужно; Мария же избрала благую часть, которая не отнимется у неё.
\\
Он сказал в ответ: возлюби Господа Бога твоего всем сердцем твоим, и всею душею твоею, и всею крепостию твоею, и всем разумением твоим, и ближнего твоего, как самого себя.
\\
Иисус сказал ему: правильно ты отвечал; так поступай, и будешь жить.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 10:38--10:42, 10:27--10:28.}\\
Now it came to pass, as they went, that he entered into a certain village: and a certain woman named Martha received him into her house.\\
And she had a sister called Mary, which also sat at Jesus' feet, and heard his word.\\
But Martha was cumbered about much serving, and came to him, and said, Lord, dost thou not care that my sister hath left me to serve alone? bid her therefore that she help me.\\
And Jesus answered and said unto her, Martha, Martha, thou art careful and troubled about many things:\\
But one thing is needful: and Mary hath chosen that good part, which shall not be taken away from her.\\
And he answering said, Thou shalt love the Lord thy God with all thy heart, and with all thy soul, and with all thy strength, and with all thy mind; and thy neighbour as thyself.\\
And he said unto him, Thou hast answered right: this do, and thou shalt live.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 10:38--10:42, 10:27--10:28.}\\
他們走路的時候、耶穌進了一個村莊．有一個女人名叫馬大、接他到自己家裡。\\
他有一個妹子名叫馬利亞、在耶穌腳前坐著聽他的道。\\
馬大伺候的事多、心裡忙亂、就進前來說、主阿、我的妹子留下我一個人伺候、你不在意麼．請吩咐他來幫助我。\\
耶穌回答說、馬大、馬大、你為許多的事、思慮煩擾．\\
但是不可少的只有一件．馬利亞已經選擇那上好的福分、是不能奪去的。\\
他回答說、『你要盡心、盡性、盡力、盡意、愛主你的　神．又要愛鄰舍如同自己。』\\
耶穌說、你回答的是．你這樣行、就必得永生。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
