\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 12 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 79 зач., XIX, 16-26.}\\
И вот, некто, подойдя, сказал Ему: Учитель благий! что сделать мне доброго, чтобы иметь жизнь вечную?
\\
Он же сказал ему: что ты называешь Меня благим? Никто не благ, как только один Бог. Если же хочешь войти в жизнь вечную, соблюди заповеди.
\\
Говорит Ему: какие? Иисус же сказал: не убивай; не прелюбодействуй; не кради; не лжесвидетельствуй;
\\
почитай отца и мать; и: люби ближнего твоего, как самого себя.
\\
Юноша говорит Ему: всё это сохранил я от юности моей; чего еще недостает мне?
\\
Иисус сказал ему: если хочешь быть совершенным, пойди, продай имение твое и раздай нищим; и будешь иметь сокровище на небесах; и приходи и следуй за Мною.
\\
Услышав слово сие, юноша отошел с печалью, потому что у него было большое имение.
\\
Иисус же сказал ученикам Своим: истинно говорю вам, что трудно богатому войти в Царство Небесное;
\\
и еще говорю вам: удобнее верблюду пройти сквозь игольные уши, нежели богатому войти в Царство Божие.
\\
Услышав это, ученики Его весьма изумились и сказали: так кто же может спастись?
\\
А Иисус, воззрев, сказал им: человекам это невозможно, Богу же всё возможно.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 19:16--19:26.}\\
And, behold, one came and said unto him, Good Master, what good thing shall I do, that I may have eternal life?\\
And he said unto him, Why callest thou me good? there is none good but one, that is, God: but if thou wilt enter into life, keep the commandments.\\
He saith unto him, Which? Jesus said, Thou shalt do no murder, Thou shalt not commit adultery, Thou shalt not steal, Thou shalt not bear false witness,\\
Honour thy father and thy mother: and, Thou shalt love thy neighbour as thyself.\\
The young man saith unto him, All these things have I kept from my youth up: what lack I yet?\\
Jesus said unto him, If thou wilt be perfect, go and sell that thou hast, and give to the poor, and thou shalt have treasure in heaven: and come and follow me.\\
But when the young man heard that saying, he went away sorrowful: for he had great possessions.\\
Then said Jesus unto his disciples, Verily I say unto you, That a rich man shall hardly enter into the kingdom of heaven.\\
And again I say unto you, It is easier for a camel to go through the eye of a needle, than for a rich man to enter into the kingdom of God.\\
When his disciples heard it, they were exceedingly amazed, saying, Who then can be saved?\\
But Jesus beheld them, and said unto them, With men this is impossible; but with God all things are possible.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 19:16--19:26.}\\
有一個人來見耶穌說、夫子、〔有古卷作良善的夫子〕我該作甚麼善事、纔能得永生。\\
耶穌對他說、你為甚麼以善事問我呢、只有一位是善的、〔有古卷作你為什麼稱我是良善的除了　神以外沒有一個良善的〕你若要進入永生、就當遵守誡命。\\
他說、甚麼誡命．耶穌說、就是不可殺人、不可姦淫、不可偷盜、不可作假見證、\\
當孝敬父母．又當愛人如己。\\
那少年人說、這一切我都遵守了．還缺少甚麼呢。\\
耶穌說、你若願意作完全人、可去變賣你所有的、分給窮人、就必有財寶在天上、你還要來跟從我。\\
那少年人聽見這話、就憂憂愁愁的走了．因為他的產業很多。\\
耶穌對門徒說、我實在告訴你們、財主進天國是難的。\\
我又告訴你們、駱駝穿過鍼的眼、比財主進　神的國還容易呢。\\
門徒聽見這話、就希奇得很、說、這樣誰能得救呢。\\
耶穌看著他們說、在人這是不能的．在　神凡事都能。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
