%simple
\documentclass[12pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 29 after the Pentecost (enlisted)\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 93 зач., XVIII, 35-43.}\\
Когда же подходил Он к Иерихону, один слепой сидел у дороги, прося милостыни,
\\
и, услышав, что мимо него проходит народ, спросил: что это такое?
\\
Ему сказали, что Иисус Назорей идет.
\\
Тогда он закричал: Иисус, Сын Давидов! помилуй меня.
\\
Шедшие впереди заставляли его молчать; но он еще громче кричал: Сын Давидов! помилуй меня.
\\
Иисус, остановившись, велел привести его к Себе: и, когда тот подошел к Нему, спросил его:
\\
чего ты хочешь от Меня? Он сказал: Господи! чтобы мне прозреть.
\\
Иисус сказал ему: прозри! вера твоя спасла тебя.
\\
И он тотчас прозрел и пошел за Ним, славя Бога; и весь народ, видя это, воздал хвалу Богу.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 18:35--18:43.}\\
And it came to pass, that as he was come nigh unto Jericho, a certain blind man sat by the way side begging:\\
And hearing the multitude pass by, he asked what it meant.\\
And they told him, that Jesus of Nazareth passeth by.\\
And he cried, saying, Jesus, thou Son of David, have mercy on me.\\
And they which went before rebuked him, that he should hold his peace: but he cried so much the more, Thou Son of David, have mercy on me.\\
And Jesus stood, and commanded him to be brought unto him: and when he was come near, he asked him,\\
Saying, What wilt thou that I shall do unto thee? And he said, Lord, that I may receive my sight.\\
And Jesus said unto him, Receive thy sight: thy faith hath saved thee.\\
And immediately he received his sight, and followed him, glorifying God: and all the people, when they saw it, gave praise unto God.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.4}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 18:35--18:43.}\\
耶穌將近耶利哥的時候、有一個瞎子坐在路旁討飯。\\
聽見許多人經過、就問是甚麼事。\\
他們告訴他、是拿撒勒人耶穌經過。\\
他就呼叫說、大衛的子孫耶穌阿、可憐我罷。\\
在前頭走的人、就責備他、不許他作聲．他卻越發喊叫說、大衛的子孫、可憐我罷。\\
耶穌站住、吩咐把他領過來．到了跟前、就問他說、\\
你要我為你作甚麼．他說、主阿、我要能看見。\\
耶穌說、你可以看見．你的信救了你了。\\
瞎子立刻看見了、就跟隨耶穌、一路歸榮耀與　神．眾人看見這事、也讚美　神。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
