\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 2 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 18 зач., VI, 22-33.}\\
Светильник для тела есть око. Итак, если око твое будет чисто, то всё тело твое будет светло;
\\
если же око твое будет худо, то всё тело твое будет темно. Итак, если свет, который в тебе, тьма, то какова же тьма?
\\
Посему говорю вам: не заботьтесь для души вашей, что вам есть и что пить, ни для тела вашего, во что одеться. Душа не больше ли пищи, и тело одежды?
\\
Взгляните на птиц небесных: они ни сеют, ни жнут, ни собирают в житницы; и Отец ваш Небесный питает их. Вы не гораздо ли лучше их?
\\
Да и кто из вас, заботясь, может прибавить себе росту хотя на один локоть?
\\
И об одежде что заботитесь? Посмотрите на полевые лилии, как они растут: ни трудятся, ни прядут;
\\
но говорю вам, что и Соломон во всей славе своей не одевался так, как всякая из них;
\\
если же траву полевую, которая сегодня есть, а завтра будет брошена в печь, Бог так одевает, кольми паче вас, маловеры!
\\
Итак не заботьтесь и не говорите: что нам есть? или что пить? или во что одеться?
\\
потому что всего этого ищут язычники, и потому что Отец ваш Небесный знает, что вы имеете нужду во всем этом.
\\
Ищите же прежде Царства Божия и правды Его, и это все приложится вам.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 6:22--6:33.}\\
The light of the body is the eye: if therefore thine eye be single, thy whole body shall be full of light.\\
But if thine eye be evil, thy whole body shall be full of darkness. If therefore the light that is in thee be darkness, how great is that darkness!\\
No man can serve two masters: for either he will hate the one, and love the other; or else he will hold to the one, and despise the other. Ye cannot serve God and mammon.\\
Therefore I say unto you, Take no thought for your life, what ye shall eat, or what ye shall drink; nor yet for your body, what ye shall put on. Is not the life more than meat, and the body than raiment?\\
Behold the fowls of the air: for they sow not, neither do they reap, nor gather into barns; yet your heavenly Father feedeth them. Are ye not much better than they?\\
Which of you by taking thought can add one cubit unto his stature?\\
And why take ye thought for raiment? Consider the lilies of the field, how they grow; they toil not, neither do they spin:\\
And yet I say unto you, That even Solomon in all his glory was not arrayed like one of these.\\
Wherefore, if God so clothe the grass of the field, which to day is, and to morrow is cast into the oven, shall he not much more clothe you, O ye of little faith?\\
Therefore take no thought, saying, What shall we eat? or, What shall we drink? or, Wherewithal shall we be clothed?\\
(For after all these things do the Gentiles seek:) for your heavenly Father knoweth that ye have need of all these things.\\
But seek ye first the kingdom of God, and his righteousness; and all these things shall be added unto you.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 6:22--6:33.}\\
眼睛就是身上的燈．你的眼睛若瞭亮、全身就光明。\\
你的眼睛若昏花、全身就黑暗．你裡頭的光若黑暗了、那黑暗是何等大呢。\\
一個人不能事奉兩個主．不是惡這個愛那個、就是重這個輕那個．你們不能又事奉　神、又事奉瑪門。〔瑪門是財利的意思〕\\
所以我告訴你們、不要為生命憂慮、喫甚麼、喝甚麼．為身體憂慮穿甚麼．生命不勝於飲食麼、身體不勝於衣裳麼。\\
你們看那天上的飛鳥、也不種、也不收、也不積蓄在倉裡、你們的天父尚且養活他．你們不比飛鳥貴重得多麼。\\
你們那一個能用思慮、使壽數多加一刻呢。〔或作使身量多加一肘呢〕\\
何必為衣裳憂慮呢．你想野地裡的百合花、怎麼長起來、他也不勞苦、也不紡線．\\
然而我告訴你們、就是所羅門極榮華的時候、他所穿戴的、還不如這花一朵呢。\\
你們這小信的人哪、野地裡的草、今天還在、明天就丟在爐裡、　神還給他這樣的妝飾、何況你們呢。\\
所以不要憂慮、說、喫甚麼、喝甚麼、穿甚麼。\\
這都是外邦人所求的．你們需用的這一切東西、你們的天父是知道的。\\
你們要先求他的國、和他的義這些東西都要加給你們了。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
