%simple
\documentclass[12pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week before the Great Lent\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 17 зач., VI, 14-21.}\\
Ибо если вы будете прощать людям согрешения их, то простит и вам Отец ваш Небесный,
\\
а если не будете прощать людям согрешения их, то и Отец ваш не простит вам согрешений ваших.
\\
Также, когда поститесь, не будьте унылы, как лицемеры, ибо они принимают на себя мрачные лица, чтобы показаться людям постящимися. Истинно говорю вам, что они уже получают награду свою.
\\
А ты, когда постишься, помажь голову твою и умой лице твое,
\\
чтобы явиться постящимся не пред людьми, но пред Отцом твоим, Который втайне; и Отец твой, видящий тайное, воздаст тебе явно.
\\
Не собирайте себе сокровищ на земле, где моль и ржа истребляют и где воры подкапывают и крадут,
\\
но собирайте себе сокровища на небе, где ни моль, ни ржа не истребляют и где воры не подкапывают и не крадут,
\\
ибо где сокровище ваше, там будет и сердце ваше.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 6:14--6:21.}\\
For if ye forgive men their trespasses, your heavenly Father will also forgive you:\\
But if ye forgive not men their trespasses, neither will your Father forgive your trespasses.\\
Moreover when ye fast, be not, as the hypocrites, of a sad countenance: for they disfigure their faces, that they may appear unto men to fast. Verily I say unto you, They have their reward.\\
But thou, when thou fastest, anoint thine head, and wash thy face;\\
That thou appear not unto men to fast, but unto thy Father which is in secret: and thy Father, which seeth in secret, shall reward thee openly.\\
Lay not up for yourselves treasures upon earth, where moth and rust doth corrupt, and where thieves break through and steal:\\
But lay up for yourselves treasures in heaven, where neither moth nor rust doth corrupt, and where thieves do not break through nor steal:\\
For where your treasure is, there will your heart be also.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.2}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 6:14--6:21.}\\
你們饒恕人的過犯、你們的天父也必饒恕你們的過犯。\\
你們不饒恕人的過犯、你們的天父也必不饒恕你們的過犯。\\
你們禁食的時候、不可像那假冒為善的人、臉上帶著愁容．因為他們把臉弄得難看、故意叫人看出他們是禁食．我實在告訴你們、他們已經得了他們的賞賜。\\
你禁食的時候、要梳頭洗臉、\\
不叫人看出你禁食來、只叫你暗中的父看見．你父在暗中察看、必然報答你。\\
不要為自己積儹財寶在地上、地上有蟲子咬、能鏽壞、也有賊挖窟窿來偷．\\
只要積儹財寶在天上、天上沒有蟲子咬、不能鏽壞、也沒有賊挖窟窿來偷．\\
因為你的財寶在那裡、你的心也在那裡。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
