\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.3in,bottom=0.3in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 8 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 58 зач., XIV, 14-22.}\\
И, выйдя, Иисус увидел множество людей и сжалился над ними, и исцелил больных их.
\\
Когда же настал вечер, приступили к Нему ученики Его и сказали: место здесь пустынное и время уже позднее; отпусти народ, чтобы они пошли в селения и купили себе пищи.
\\
Но Иисус сказал им: не нужно им идти, вы дайте им есть.
\\
Они же говорят Ему: у нас здесь только пять хлебов и две рыбы.
\\
Он сказал: принесите их Мне сюда.
\\
И велел народу возлечь на траву и, взяв пять хлебов и две рыбы, воззрел на небо, благословил и, преломив, дал хлебы ученикам, а ученики народу.
\\
И ели все и насытились; и набрали оставшихся кусков двенадцать коробов полных;
\\
а евших было около пяти тысяч человек, кроме женщин и детей.
\\
И тотчас понудил Иисус учеников Своих войти в лодку и отправиться прежде Его на другую сторону, пока Он отпустит народ.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 14:14--14:22.}\\
And Jesus went forth, and saw a great multitude, and was moved with compassion toward them, and he healed their sick.\\
And when it was evening, his disciples came to him, saying, This is a desert place, and the time is now past; send the multitude away, that they may go into the villages, and buy themselves victuals.\\
But Jesus said unto them, They need not depart; give ye them to eat.\\
And they say unto him, We have here but five loaves, and two fishes.\\
He said, Bring them hither to me.\\
And he commanded the multitude to sit down on the grass, and took the five loaves, and the two fishes, and looking up to heaven, he blessed, and brake, and gave the loaves to his disciples, and the disciples to the multitude.\\
And they did all eat, and were filled: and they took up of the fragments that remained twelve baskets full.\\
And they that had eaten were about five thousand men, beside women and children.\\
And straightway Jesus constrained his disciples to get into a ship, and to go before him unto the other side, while he sent the multitudes away.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 14:14--14:22.}\\
耶穌出來、見有許多的人、就憐憫他們、治好了他們的病人。\\
天將晚的時候、門徒進前來說、這是野地、時候已經過了．請叫眾人散開、他們好往村子裡去、自己買喫的。\\
耶穌說、不用他們去、你們給他們喫罷。\\
門徒說、我們這裡只有五個餅、兩條魚。\\
耶穌說、拿過來給我。\\
於是吩咐眾人坐在草地上．就拿著這五個餅、兩條魚、望著天、祝福、擘開餅、遞給門徒．門徒又遞給眾人。\\
他們都喫、並且喫飽了．把剩下的零碎收拾起來、裝滿了十二個籃子。\\
喫的人除了婦女孩子、約有五千。\\
耶穌隨即催門徒上船、先渡到那邊去、等他叫眾人散開。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
