\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 26 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 53 зач., X, 25-37.}\\
И вот, один законник встал и, искушая Его, сказал: Учитель! что мне делать, чтобы наследовать жизнь вечную?
\\
Он же сказал ему: в законе что написано? как читаешь?
\\
Он сказал в ответ: возлюби Господа Бога твоего всем сердцем твоим, и всею душею твоею, и всею крепостию твоею, и всем разумением твоим, и ближнего твоего, как самого себя.
\\
Иисус сказал ему: правильно ты отвечал; так поступай, и будешь жить.
\\
Но он, желая оправдать себя, сказал Иисусу: а кто мой ближний?
\\
На это сказал Иисус: некоторый человек шел из Иерусалима в Иерихон и попался разбойникам, которые сняли с него одежду, изранили его и ушли, оставив его едва живым.
\\
По случаю один священник шел тою дорогою и, увидев его, прошел мимо.
\\
Также и левит, быв на том месте, подошел, посмотрел и прошел мимо.
\\
Самарянин же некто, проезжая, нашел на него и, увидев его, сжалился
\\
и, подойдя, перевязал ему раны, возливая масло и вино; и, посадив его на своего осла, привез его в гостиницу и позаботился о нем;
\\
а на другой день, отъезжая, вынул два динария, дал содержателю гостиницы и сказал ему: позаботься о нем; и если издержишь что более, я, когда возвращусь, отдам тебе.
\\
Кто из этих троих, думаешь ты, был ближний попавшемуся разбойникам?
\\
Он сказал: оказавший ему милость. Тогда Иисус сказал ему: иди, и ты поступай так же.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 10:25--10:37.}\\
And, behold, a certain lawyer stood up, and tempted him, saying, Master, what shall I do to inherit eternal life?\\
He said unto him, What is written in the law? how readest thou?\\
And he answering said, Thou shalt love the Lord thy God with all thy heart, and with all thy soul, and with all thy strength, and with all thy mind; and thy neighbour as thyself.\\
And he said unto him, Thou hast answered right: this do, and thou shalt live.\\
But he, willing to justify himself, said unto Jesus, And who is my neighbour?\\
And Jesus answering said, A certain man went down from Jerusalem to Jericho, and fell among thieves, which stripped him of his raiment, and wounded him, and departed, leaving him half dead.\\
And by chance there came down a certain priest that way: and when he saw him, he passed by on the other side.\\
And likewise a Levite, when he was at the place, came and looked on him, and passed by on the other side.\\
But a certain Samaritan, as he journeyed, came where he was: and when he saw him, he had compassion on him,\\
And went to him, and bound up his wounds, pouring in oil and wine, and set him on his own beast, and brought him to an inn, and took care of him.\\
And on the morrow when he departed, he took out two pence, and gave them to the host, and said unto him, Take care of him; and whatsoever thou spendest more, when I come again, I will repay thee.\\
Which now of these three, thinkest thou, was neighbour unto him that fell among the thieves?\\
And he said, He that shewed mercy on him. Then said Jesus unto him, Go, and do thou likewise.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.1}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 10:25--10:37.}\\
有一個律法師、起來試探耶穌說、夫子、我該作甚麼纔可以承受永生。\\
耶穌對他說、律法上寫的是甚麼．你念的是怎樣呢。\\
他回答說、『你要盡心、盡性、盡力、盡意、愛主你的　神．又要愛鄰舍如同自己。』\\
耶穌說、你回答的是．你這樣行、就必得永生。\\
那人要顯明自己有理、就對耶穌說、誰是我的鄰舍呢。\\
耶穌回答說、有一個人從耶路撒冷下耶利哥去、落在強盜手中、他們剝去他的衣裳、把他打個半死、就丟下他走了。\\
偶然有一個祭司、從這條路下來．看見他就從那邊過去了。\\
又有一個利未人、來到這地方、看見他、也照樣從那邊過去了。\\
惟有一個撒瑪利亞人、行路來到那裡．看見他就動了慈心、\\
上前用油和酒倒在他的傷處、包裹好了、扶他騎上自己的牲口、帶到店裡去照應他。\\
第二天拿出二錢銀子來、交給店主說、你且照應他．此外所費用的、我回來必還你。\\
你想這三個人、那一個是落在強盜手中的鄰舍呢。\\
他說、是憐憫他的。耶穌說、你去照樣行罷。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
