\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 1 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 38 зач., X, 32-33, 37-38; XIX, 27-30.}\\
Итак всякого, кто исповедает Меня пред людьми, того исповедаю и Я пред Отцем Моим Небесным;
\\
а кто отречется от Меня пред людьми, отрекусь от того и Я пред Отцем Моим Небесным.
\\
Кто любит отца или мать более, нежели Меня, не достоин Меня; и кто любит сына или дочь более, нежели Меня, не достоин Меня;
\\
и кто не берет креста своего и следует за Мною, тот не достоин Меня.
\\
Тогда Петр, отвечая, сказал Ему: вот, мы оставили всё и последовали за Тобою; что же будет нам?\\
 Иисус же сказал им: истинно говорю вам, что вы, последовавшие за Мною,- в пакибытии, когда сядет Сын Человеческий на престоле славы Своей, сядете и вы на двенадцати престолах судить двенадцать колен Израилевых.\\
И всякий, кто оставит до́мы, или братьев, или сестер, или отца, или мать, или жену, или детей, или зе́мли, ради имени Моего, получит во сто крат и наследует жизнь вечную.\\
 Многие же будут первые последними, и последние первыми.
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}
\textbf{Matthew 10:32--10:33, 10:37--10:38, 19:27--19:30.}\\
Whosoever therefore shall confess me before men, him will I confess also before my Father which is in heaven.\\
But whosoever shall deny me before men, him will I also deny before my Father which is in heaven.\\
He that loveth father or mother more than me is not worthy of me: and he that loveth son or daughter more than me is not worthy of me.\\
And he that taketh not his cross, and followeth after me, is not worthy of me.\\
Then answered Peter and said unto him, Behold, we have forsaken all, and followed thee; what shall we have therefore?\\
And Jesus said unto them, Verily I say unto you, That ye which have followed me, in the regeneration when the Son of man shall sit in the throne of his glory, ye also shall sit upon twelve thrones, judging the twelve tribes of Israel.\\
And every one that hath forsaken houses, or brethren, or sisters, or father, or mother, or wife, or children, or lands, for my name's sake, shall receive an hundredfold, and shall inherit everlasting life.\\
But many that are first shall be last; and the last shall be first.
\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 10:32--10:33, 10:37--10:38, 19:27--19:30.}\\
凡在人面前認我的、我在我天上的父面前、也必認他。\\
凡在人面前不認我的、我在我天上的父面前、也必不認他。\\
愛父母過於愛我的、不配作我的門徒、愛兒女過於愛我的、不配作我的門徒。\\
不背著他的十字架跟從我的、也不配作我的門徒。\\
彼得就對他說、看哪、我們已經撇下所有的跟從你、將來我們要得甚麼呢。
耶穌說、我實在告訴你們、你們這跟從我的人、到復興的時候、人子坐在他榮耀的寶座上、你們也要坐在十二個寶座上、審判以色列十二個支派。
凡為我的名撇下房屋、或是弟兄、姐妹、父親、母親、〔有古卷添妻子〕兒女、田地的、必要得著百倍、並且承受永生。
然而有許多在前的將要在後、在後的將要在前。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
