\documentclass[14pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 33 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 8 зач., IV, 12-17.}\\
Услышав же Иисус, что Иоанн отдан под стражу, удалился в Галилею
\\
и, оставив Назарет, пришел и поселился в Капернауме приморском, в пределах Завулоновых и Неффалимовых,
\\
да сбудется реченное через пророка Исаию, который говорит:
\\
земля Завулонова и земля Неффалимова, на пути приморском, за Иорданом, Галилея языческая,
\\
народ, сидящий во тьме, увидел свет великий, и сидящим в стране и тени смертной воссиял свет.
\\
С того времени Иисус начал проповедовать и говорить: покайтесь, ибо приблизилось Царство Небесное.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 4:12--4:17.}\\
Now when Jesus had heard that John was cast into prison, he departed into Galilee;\\
And leaving Nazareth, he came and dwelt in Capernaum, which is upon the sea coast, in the borders of Zabulon and Nephthalim:\\
That it might be fulfilled which was spoken by Esaias the prophet, saying,\\
The land of Zabulon, and the land of Nephthalim, by the way of the sea, beyond Jordan, Galilee of the Gentiles;\\
The people which sat in darkness saw great light; and to them which sat in the region and shadow of death light is sprung up.\\
From that time Jesus began to preach, and to say, Repent: for the kingdom of heaven is at hand.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 4:12--4:17.}\\
耶穌聽見約翰下了監、就退到加利利去．\\
後又離開拿撒勒、往迦百農去、就住在那裡．那地方靠海、在西布倫和拿弗他利的邊界上。\\
這是要應驗先知以賽亞的話、\\
說、『西布倫地、拿弗他利地、就是沿海的路、約但河外、外邦人的加利利地。\\
那坐在黑暗裡的百姓、看見了大光、坐在死蔭之地的人、有光發現照著他們。』\\
從那時候耶穌就傳起道來、說、天國近了、你們應當悔改。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
