\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.0in,bottom=0.1in,left=0.0in,right=0.3in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 4 after Easter\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Ин., 14 зач., V, 1-15.}\\
После сего был праздник Иудейский, и пришел Иисус в Иерусалим.
\\
В них лежало великое множество больных, слепых, хромых, иссохших, ожидающих движения воды,
\\
ибо Ангел Господень по временам сходил в купальню и возмущал воду, и кто первый входил в нее по возмущении воды, тот выздоравливал, какою бы ни был одержим болезнью.
\\
Тут был человек, находившийся в болезни тридцать восемь лет.
\\
Иисус, увидев его лежащего и узнав, что он лежит уже долгое время, говорит ему: хочешь ли быть здоров?
\\
Больной отвечал Ему: так, Господи; но не имею человека, который опустил бы меня в купальню, когда возмутится вода; когда же я прихожу, другой уже сходит прежде меня.
\\
Иисус говорит ему: встань, возьми постель твою и ходи.
\\
И он тотчас выздоровел, и взял постель свою и пошел. Было же это в день субботний.
\\
Посему Иудеи говорили исцеленному: сегодня суббота; не должно тебе брать постели.
\\
Он отвечал им: Кто меня исцелил, Тот мне сказал: возьми постель твою и ходи.
\\
Его спросили: кто Тот Человек, Который сказал тебе: возьми постель твою и ходи?
\\
Исцеленный же не знал, кто Он, ибо Иисус скрылся в народе, бывшем на том месте.
\\
Потом Иисус встретил его в храме и сказал ему: вот, ты выздоровел; не греши больше, чтобы не случилось с тобою чего хуже.
\\
Человек сей пошел и объявил Иудеям, что исцеливший его есть Иисус.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{John 5:1--5:15.}\\
After this there was a feast of the Jews; and Jesus went up to Jerusalem.\\
Now there is at Jerusalem by the sheep market a pool, which is called in the Hebrew tongue Bethesda, having five porches.\\
In these lay a great multitude of impotent folk, of blind, halt, withered, waiting for the moving of the water.\\
For an angel went down at a certain season into the pool, and troubled the water: whosoever then first after the troubling of the water stepped in was made whole of whatsoever disease he had.\\
And a certain man was there, which had an infirmity thirty and eight years.\\
When Jesus saw him lie, and knew that he had been now a long time in that case, he saith unto him, Wilt thou be made whole?\\
The impotent man answered him, Sir, I have no man, when the water is troubled, to put me into the pool: but while I am coming, another steppeth down before me.\\
Jesus saith unto him, Rise, take up thy bed, and walk.\\
And immediately the man was made whole, and took up his bed, and walked: and on the same day was the sabbath.\\
The Jews therefore said unto him that was cured, It is the sabbath day: it is not lawful for thee to carry thy bed.\\
He answered them, He that made me whole, the same said unto me, Take up thy bed, and walk.\\
Then asked they him, What man is that which said unto thee, Take up thy bed, and walk?\\
And he that was healed wist not who it was: for Jesus had conveyed himself away, a multitude being in that place.\\
Afterward Jesus findeth him in the temple, and said unto him, Behold, thou art made whole: sin no more, lest a worse thing come unto thee.\\
The man departed, and told the Jews that it was Jesus, which had made him whole.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{0.95}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{約翰福音 5:1--5:15.}\\
這事以後、到了猶太人的一個節期．耶穌就上耶路撒冷去。\\
在耶路撒冷、靠近羊門有一個池子、希伯來話叫作畢士大、旁邊有五個廊子。\\
裡面躺著瞎眼的、瘸腿的、血氣枯乾的、許多病人。〔有古卷在此有等候水動〕\\
〔因為有天使按時下池子攪動那水水動之後誰先下去無論害甚麼病就痊愈了〕\\
在那裡有一個人、病了三十八年。\\
耶穌看見他躺著、知道他病了許久、就問他說、你要痊愈麼。\\
病人回答說、先生、水動的時候、沒有人把我放在池子裡．我正去的時候、就有別人比我先下去。\\
耶穌對他說、起來、拿你的褥子走罷。\\
那人立刻痊愈、就拿起褥子來走了。\\
那天是安息日、所以猶太人對那醫好的人說、今天是安息日、你拿褥子是不可的。\\
他卻回答說、那使我痊愈的、對我說、拿你的褥子走罷。\\
他們問他說、對你說拿褥子走的、是甚麼人。\\
那醫好的人不知道是誰．因為那裡的人多、耶穌已經躲開了。\\
後來耶穌在殿裡遇見他、對他說、你已經痊愈了．不要再犯罪、恐怕你遭遇的更加利害。\\
那人就去告訴猶太人、使他痊愈的是耶穌。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
