%simple
\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.1in,bottom=0.0in,left=0.0in,right=0.4in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week Holy Saturday\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
%\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 115 зач., XXVIII, 1-20.}\\
По прошествии же субботы, на рассвете первого дня недели, пришла Мария Магдалина и другая Мария посмотреть гроб.
\\
И вот, сделалось великое землетрясение, ибо Ангел Господень, сошедший с небес, приступив, отвалил камень от двери гроба и сидел на нем;
\\
вид его был, как молния, и одежда его бела, как снег;
\\
устрашившись его, стерегущие пришли в трепет и стали, как мертвые;
\\
Ангел же, обратив речь к женщинам, сказал: не бойтесь, ибо знаю, что вы ищете Иисуса распятого;
\\
Его нет здесь - Он воскрес, как сказал. Подойдите, посмотрите место, где лежал Господь,
\\
и пойдите скорее, скажите ученикам Его, что Он воскрес из мертвых и предваряет вас в Галилее; там Его увидите. Вот, я сказал вам.
\\
И, выйдя поспешно из гроба, они со страхом и радостью великою побежали возвестить ученикам Его.
\\
Когда же шли они возвестить ученикам Его, и се Иисус встретил их и сказал: радуйтесь! И они, приступив, ухватились за ноги Его и поклонились Ему.
\\
Тогда говорит им Иисус: не бойтесь; пойдите, возвестите братьям Моим, чтобы шли в Галилею, и там они увидят Меня.
\\
Когда же они шли, то некоторые из стражи, войдя в город, объявили первосвященникам о всем бывшем.
\\
И сии, собравшись со старейшинами и сделав совещание, довольно денег дали воинам,
\\
и сказали: скажите, что ученики Его, придя ночью, украли Его, когда мы спали;
\\
и, если слух об этом дойдет до правителя, мы убедим его, и вас от неприятности избавим.
\\
Они, взяв деньги, поступили, как научены были; и пронеслось слово сие между иудеями до сего дня.
\\
Одиннадцать же учеников пошли в Галилею, на гору, куда повелел им Иисус,
\\
и, увидев Его, поклонились Ему, а иные усомнились.
\\
И приблизившись Иисус сказал им: дана Мне всякая власть на небе и на земле.
\\
Итак идите, научите все народы, крестя их во имя Отца и Сына и Святаго Духа,
\\
уча их соблюдать всё, что Я повелел вам; и се, Я с вами во все дни до скончания века. Аминь.
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 28:1--28:20.}\\
In the end of the sabbath, as it began to dawn toward the first day of the week, came Mary Magdalene and the other Mary to see the sepulchre.\\
And, behold, there was a great earthquake: for the angel of the Lord descended from heaven, and came and rolled back the stone from the door, and sat upon it.\\
His countenance was like lightning, and his raiment white as snow:\\
And for fear of him the keepers did shake, and became as dead men.\\
And the angel answered and said unto the women, Fear not ye: for I know that ye seek Jesus, which was crucified.\\
He is not here: for he is risen, as he said. Come, see the place where the Lord lay.\\
And go quickly, and tell his disciples that he is risen from the dead; and, behold, he goeth before you into Galilee; there shall ye see him: lo, I have told you.\\
And they departed quickly from the sepulchre with fear and great joy; and did run to bring his disciples word.\\
And as they went to tell his disciples, behold, Jesus met them, saying, All hail. And they came and held him by the feet, and worshipped him.\\
Then said Jesus unto them, Be not afraid: go tell my brethren that they go into Galilee, and there shall they see me.\\
Now when they were going, behold, some of the watch came into the city, and shewed unto the chief priests all the things that were done.\\
And when they were assembled with the elders, and had taken counsel, they gave large money unto the soldiers,\\
Saying, Say ye, His disciples came by night, and stole him away while we slept.\\
And if this come to the governor's ears, we will persuade him, and secure you.\\
So they took the money, and did as they were taught: and this saying is commonly reported among the Jews until this day.\\
Then the eleven disciples went away into Galilee, into a mountain where Jesus had appointed them.\\
And when they saw him, they worshipped him: but some doubted.\\
And Jesus came and spake unto them, saying, All power is given unto me in heaven and in earth.\\
Go ye therefore, and teach all nations, baptizing them in the name of the Father, and of the Son, and of the Holy Ghost:\\
Teaching them to observe all things whatsoever I have commanded you: and, lo, I am with you alway, even unto the end of the world. Amen.
\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{0.9}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 28:1--28:20.}\\
安息日將盡、七日的頭一日、天快亮的時候、抹大拉的馬利亞、和那個馬利亞、來看墳墓。\\
忽然地大震動．因為有主的使者、從天上下來、把石頭滾開、坐在上面。\\
他的像貌如同閃電、衣服潔白如雪。\\
看守的人、就因他嚇得渾身亂戰、甚至和死人一樣。\\
天使對婦女說、不要害怕、我知道你們是尋找那釘十字架的耶穌。\\
他不在這裡、照他所說的、已經復活了．你們來看安放主的地方。\\
快去告訴他的門徒說、他從死裡復活了．並且在你們以先往加利利去、在那裡你們要見他．看哪．我已經告訴你們了。\\
婦女們就急忙離開墳墓、又害怕、又大大的歡喜、跑去要報給他的門徒。\\
忽然耶穌遇見他們、說、願你們平安。他們就上前抱住他的腳拜他。\\
耶穌對他們說、不要害怕、你們去告訴我的弟兄、叫他們往加利利去、在那裡必見我。\\
他們去的時候、看守的兵、有幾個進城去、將所經歷的事、都報給祭司長。\\
祭司長和長老聚集商議、就拿許多銀錢給兵丁說、\\
你們要這樣說、夜間我們睡覺的時候、他的門徒來把他偷去了。\\
倘若這話被巡撫聽見、有我們勸他、保你們無事。\\
兵丁受了銀錢、就照所囑咐他們的去行．這話就傳說在猶太人中間、直到今日。\\
十一個門徒往加利利去、到了耶穌約定的山上。\\
他們見了耶穌就拜他．然而還有人疑惑。\\
耶穌進前來、對他們說、天上地下所有的權柄、都賜給我了。\\
所以你們要去、使萬民作我的門徒、奉父子聖靈的名、給他們施洗．〔或作給他們施洗歸於父子聖靈的名〕\\
凡我所吩咐你們的、都教訓他們遵守我就常與你們同在、直到世界的末了。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
