\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.0in,bottom=0.0in,left=0.2in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 7 after Easter\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Ин., 56 зач., XVII, 1-13.}\\
После сих слов Иисус возвел очи Свои на небо и сказал: Отче! пришел час, прославь Сына Твоего, да и Сын Твой прославит Тебя,
\\
так как Ты дал Ему власть над всякою плотью, да всему, что Ты дал Ему, даст Он жизнь вечную.
\\
Сия же есть жизнь вечная, да знают Тебя, единого истинного Бога, и посланного Тобою Иисуса Христа.
\\
Я прославил Тебя на земле, совершил дело, которое Ты поручил Мне исполнить.
\\
И ныне прославь Меня Ты, Отче, у Тебя Самого славою, которую Я имел у Тебя прежде бытия мира.
\\
Я открыл имя Твое человекам, которых Ты дал Мне от мира; они были Твои, и Ты дал их Мне, и они сохранили слово Твое.
\\
Ныне уразумели они, что все, что Ты дал Мне, от Тебя есть,
\\
ибо слова, которые Ты дал Мне, Я передал им, и они приняли, и уразумели истинно, что Я исшел от Тебя, и уверовали, что Ты послал Меня.
\\
Я о них молю: не о всем мире молю, но о тех, которых Ты дал Мне, потому что они Твои.
\\
И все Мое Твое, и Твое Мое; и Я прославился в них.
\\
Я уже не в мире, но они в мире, а Я к Тебе иду. Отче Святый! соблюди их во имя Твое, тех, которых Ты Мне дал, чтобы они были едино, как и Мы.
\\
Когда Я был с ними в мире, Я соблюдал их во имя Твое; тех, которых Ты дал Мне, Я сохранил, и никто из них не погиб, кроме сына погибели, да сбудется Писание.
\\
Ныне же к Тебе иду, и сие говорю в мире, чтобы они имели в себе радость Мою совершенную.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{John 17:1--17:13.}\\
These words spake Jesus, and lifted up his eyes to heaven, and said, Father, the hour is come; glorify thy Son, that thy Son also may glorify thee:\\
As thou hast given him power over all flesh, that he should give eternal life to as many as thou hast given him.\\
And this is life eternal, that they might know thee the only true God, and Jesus Christ, whom thou hast sent.\\
I have glorified thee on the earth: I have finished the work which thou gavest me to do.\\
And now, O Father, glorify thou me with thine own self with the glory which I had with thee before the world was.\\
I have manifested thy name unto the men which thou gavest me out of the world: thine they were, and thou gavest them me; and they have kept thy word.\\
Now they have known that all things whatsoever thou hast given me are of thee.\\
For I have given unto them the words which thou gavest me; and they have received them, and have known surely that I came out from thee, and they have believed that thou didst send me.\\
I pray for them: I pray not for the world, but for them which thou hast given me; for they are thine.\\
And all mine are thine, and thine are mine; and I am glorified in them.\\
And now I am no more in the world, but these are in the world, and I come to thee. Holy Father, keep through thine own name those whom thou hast given me, that they may be one, as we are.\\
While I was with them in the world, I kept them in thy name: those that thou gavest me I have kept, and none of them is lost, but the son of perdition; that the scripture might be fulfilled.\\
And now come I to thee; and these things I speak in the world, that they might have my joy fulfilled in themselves.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{約翰福音 17:1--17:13.}\\
耶穌說了這話、就舉目望天說、父阿、時候到了．願你榮耀你的兒子、使兒子也榮耀你．\\
正如你曾賜給他權柄、管理凡有血氣的、叫他將永生賜給你所賜給他的人。\\
認識你獨一的真　神、並且認識你所差來的耶穌基督、這就是永生。\\
我在地上已經榮耀你、你所託付我的事、我已成全了。\\
父阿、現在求你使我同你享榮耀、就是未有世界以先、我同你所有的榮耀。\\
你從世上賜給我的人、我已將你的名顯明與他們．他們本是你的、你將他們賜給我、他們也遵守了你的道。\\
如今他們知道、凡你所賜給我的、都是從你那裡來的．\\
因為你所賜給我的道、我已經賜給他們．他們也領受了、又確實知道、我是從你出來的、並且信你差了我來。\\
我為他們祈求．不為世人祈求、卻為你所賜給我的人祈求、因他們本是你的。\\
凡是我的都是你的、你的也是我的．並且我因他們得了榮耀。\\
從今以後、我不在世上、他們卻在世上、我往你那裡去。聖父阿、求你因你所賜給我的名保守他們、叫他們合而為一像我們一樣。\\
我與他們同在的時候、因你所賜給我的名、保守了他們、我也護衛了他們、其中除了那滅亡之子、沒有一個滅亡的．好叫經上的話得應驗。\\
現在我往你那裡去．我還在世上說這話、是叫他們心裡充滿我的喜樂。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
