\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.2in,bottom=0.2in,left=0.2in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{\vspace{-1ex}Divine Liturgy\\Reading from The Gospels}
\author{Week 10 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 72 зач., XVII, 14-23.}\\
Когда они пришли к народу, то подошел к Нему человек и, преклоняя пред Ним колени,
\\
сказал: Господи! помилуй сына моего; он в новолуния беснуется и тяжко страдает, ибо часто бросается в огонь и часто в воду,
\\
я приводил его к ученикам Твоим, и они не могли исцелить его.
\\
Иисус же, отвечая, сказал: о, род неверный и развращенный! доколе буду с вами? доколе буду терпеть вас? приведите его ко Мне сюда.
\\
И запретил ему Иисус, и бес вышел из него; и отрок исцелился в тот час.
\\
Тогда ученики, приступив к Иисусу наедине, сказали: почему мы не могли изгнать его?
\\
Иисус же сказал им: по неверию вашему; ибо истинно говорю вам: если вы будете иметь веру с горчичное зерно и скажете горе сей: "перейди отсюда туда", и она перейдет; и ничего не будет невозможного для вас;
\\
сей же род изгоняется только молитвою и постом.
\\
Во время пребывания их в Галилее, Иисус сказал им: Сын Человеческий предан будет в руки человеческие,
\\
и убьют Его, и в третий день воскреснет. И они весьма опечалились.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 17:14--17:23.}\\
And when they were come to the multitude, there came to him a certain man, kneeling down to him, and saying,\\
Lord, have mercy on my son: for he is lunatick, and sore vexed: for ofttimes he falleth into the fire, and oft into the water.\\
And I brought him to thy disciples, and they could not cure him.\\
Then Jesus answered and said, O faithless and perverse generation, how long shall I be with you? how long shall I suffer you? bring him hither to me.\\
And Jesus rebuked the devil; and he departed out of him: and the child was cured from that very hour.\\
Then came the disciples to Jesus apart, and said, Why could not we cast him out?\\
And Jesus said unto them, Because of your unbelief: for verily I say unto you, If ye have faith as a grain of mustard seed, ye shall say unto this mountain, Remove hence to yonder place; and it shall remove; and nothing shall be impossible unto you.\\
Howbeit this kind goeth not out but by prayer and fasting.\\
And while they abode in Galilee, Jesus said unto them, The Son of man shall be betrayed into the hands of men:\\
And they shall kill him, and the third day he shall be raised again. And they were exceeding sorry.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 17:14--17:23.}\\
耶穌和門徒到了眾人那裡、有一個人來見耶穌、跪下、說、\\
主阿、憐憫我的兒子．他害癲癇的病很苦、屢次跌在火裡、屢次跌在水裡。\\
我帶他到你門徒那裡、他們卻不能醫治他。\\
耶穌說、噯、這又不信又悖謬的世代阿、我在你們這裡要到幾時呢．我忍耐你們要到幾時呢．把他帶到我這裡來罷。\\
耶穌斥責那鬼、鬼就出來．從此孩子就痊愈了。\\
門徒暗暗的到耶穌跟前說、我們為甚麼不能趕出那鬼呢。\\
耶穌說、是因你們的信心小．我實在告訴你們、你們若有信心像一粒芥菜種、就是對這座山說、你從這邊挪到那邊、他也必挪去．並且你們沒有一件不能作的事了。\\
至於這一類的鬼、若不禱告禁食、他就不出來。〔或作不能趕他出來〕\\
他們還住在加利利的時候、耶穌對門徒說、人子將要被交在人手裡．\\
他們要殺害他、第三日他要復活。門徒就大大的憂愁。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
