\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[margin=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 23 after the Pentecost\vspace{-3ex}}
\date{\vspace{-5ex}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
	\topskip0pt\vspace*{\fill}
\Large
\onehalfspacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 66 зач., XII, 16-21.}\\
И сказал им притчу: у одного богатого человека был хороший урожай в поле;\\
и он рассуждал сам с собою: что мне делать? некуда мне собрать плодов моих?\\
И сказал: вот что сделаю: сломаю житницы мои и построю бо́льшие, и соберу туда весь хлеб мой и всё добро мое,\\
и скажу душе моей: душа! много добра лежит у тебя на многие годы: покойся, ешь, пей, веселись.\\
Но Бог сказал ему: безумный! в сию ночь душу твою возьмут у тебя; кому же достанется то, что ты заготовил?\\
Так бывает с тем, кто собирает сокровища для себя, а не в Бога богатеет. \\
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 12:16 -- 12:21.}\\
And he spake a parable unto them, saying, The ground of a certain rich man brought forth plentifully:\\
And he thought within himself, saying, What shall I do, because I have no room where to bestow my fruits?\\
And he said, This will I do: I will pull down my barns, and build greater; and there will I bestow all my fruits and my goods.\\
And I will say to my soul, Soul, thou hast much goods laid up for many years; take thine ease, eat, drink, and be merry.\\
But God said unto him, Thou fool, this night thy soul shall be required of thee: then whose shall those things be, which thou hast provided?\\
So is he that layeth up treasure for himself, and is not rich toward God.\\
\end{minipage}}
	\vspace*{\fill}
\newpage\Huge
\doublespacing %for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 12:16 -- 12:21.}\\
然後他用比喻對他們說：「有一個財主，田地出產豐富。\\
他自己心裏想：『我的出產沒有地方儲藏，怎麼辦呢？』\\
就說：『我要這麼辦：要把我的倉庫拆了，另蓋更大的，在那裏好儲藏我一切的糧食和財物，\\
然後要對我自己說：你這個人哪，你有許多財物積存，可供多年享用，只管安安逸逸吃喝快樂吧！』\\
上帝卻對他說：『無知的人哪！今夜就要你的性命，你所預備的要歸誰呢？』\\
凡為自己積財，在上帝面前卻不富足的，也是這樣。」 \\
\end{CJK}
\end{minipage}}
\end{document}
