\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.2in,bottom=0.2in,left=0.2in,right=0.4in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{\vspace{-5ex}Divine Liturgy\\Reading from The Gospels\vspace{-1ex}}
\author{Week 31 after the Pentecost\vspace{
-6ex%for author
}}
\date{\vspace{
-8ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\normalfont%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 1 зач., I, 1-25.}\\
Родословие Иисуса Христа, Сына Давидова, Сына Авраамова.
\\
Авраам родил Исаака; Исаак родил Иакова; Иаков родил Иуду и братьев его;
\\
Иуда родил Фареса и Зару от Фамари; Фарес родил Есрома; Есром родил Арама;
\\
Арам родил Аминадава; Аминадав родил Наассона; Наассон родил Салмона;
\\
Салмон родил Вооза от Рахавы; Вооз родил Овида от Руфи; Овид родил Иессея;
\\
Иессей родил Давида царя; Давид царь родил Соломона от бывшей за Уриею;
\\
Соломон родил Ровоама; Ровоам родил Авию; Авия родил Асу;
\\
Аса родил Иосафата; Иосафат родил Иорама; Иорам родил Озию;
\\
Озия родил Иоафама; Иоафам родил Ахаза; Ахаз родил Езекию;
\\
Езекия родил Манассию; Манассия родил Амона; Амон родил Иосию;
\\
Иосия родил Иоакима; Иоаким родил Иехонию и братьев его, перед переселением в Вавилон.
\\
По переселении же в Вавилон, Иехония родил Салафииля; Салафииль родил Зоровавеля;
\\
Зоровавель родил Авиуда; Авиуд родил Елиакима; Елиаким родил Азора;
\\
Азор родил Садока; Садок родил Ахима; Ахим родил Елиуда;
\\
Елиуд родил Елеазара; Елеазар родил Матфана; Матфан родил Иакова;
\\
Иаков родил Иосифа, мужа Марии, от Которой родился Иисус, называемый Христос.
\\
Итак всех родов от Авраама до Давида четырнадцать родов; и от Давида до переселения в Вавилон четырнадцать родов; и от переселения в Вавилон до Христа четырнадцать родов.
\\
Рождество Иисуса Христа было так: по обручении Матери Его Марии с Иосифом, прежде нежели сочетались они, оказалось, что Она имеет во чреве от Духа Святаго.
\\
Иосиф же муж Ее, будучи праведен и не желая огласить Ее, хотел тайно отпустить Ее.
\\
Но когда он помыслил это,- се, Ангел Господень явился ему во сне и сказал: Иосиф, сын Давидов! не бойся принять Марию, жену твою, ибо родившееся в Ней есть от Духа Святаго;
\\
родит же Сына, и наречешь Ему имя Иисус, ибо Он спасет людей Своих от грехов их.
\\
А все сие произошло, да сбудется реченное Господом через пророка, который говорит:
\\
се, Дева во чреве приимет и родит Сына, и нарекут имя Ему Еммануил, что значит: с нами Бог.
\\
Встав от сна, Иосиф поступил, как повелел ему Ангел Господень, и принял жену свою,
\\
и не знал Ее, как наконец Она родила Сына Своего первенца, и он нарек Ему имя: Иисус.
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 1:1--1:25.}\\
The book of the generation of Jesus Christ, the son of David, the son of Abraham.\\
Abraham begat Isaac; and Isaac begat Jacob; and Jacob begat Judas and his brethren;\\
And Judas begat Phares and Zara of Thamar; and Phares begat Esrom; and Esrom begat Aram;\\
And Aram begat Aminadab; and Aminadab begat Naasson; and Naasson begat Salmon;\\
And Salmon begat Booz of Rachab; and Booz begat Obed of Ruth; and Obed begat Jesse;\\
And Jesse begat David the king; and David the king begat Solomon of her that had been the wife of Urias;\\
And Solomon begat Roboam; and Roboam begat Abia; and Abia begat Asa;\\
And Asa begat Josaphat; and Josaphat begat Joram; and Joram begat Ozias;\\
And Ozias begat Joatham; and Joatham begat Achaz; and Achaz begat Ezekias;\\
And Ezekias begat Manasses; and Manasses begat Amon; and Amon begat Josias;\\
And Josias begat Jechonias and his brethren, about the time they were carried away to Babylon:\\
And after they were brought to Babylon, Jechonias begat Salathiel; and Salathiel begat Zorobabel;\\
And Zorobabel begat Abiud; and Abiud begat Eliakim; and Eliakim begat Azor;\\
And Azor begat Sadoc; and Sadoc begat Achim; and Achim begat Eliud;\\
And Eliud begat Eleazar; and Eleazar begat Matthan; and Matthan begat Jacob;\\
And Jacob begat Joseph the husband of Mary, of whom was born Jesus, who is called Christ.\\
So all the generations from Abraham to David are fourteen generations; and from David until the carrying away into Babylon are fourteen generations; and from the carrying away into Babylon unto Christ are fourteen generations.\\
Now the birth of Jesus Christ was on this wise: When as his mother Mary was espoused to Joseph, before they came together, she was found with child of the Holy Ghost.\\
Then Joseph her husband, being a just man, and not willing to make her a publick example, was minded to put her away privily.\\
But while he thought on these things, behold, the angel of the Lord appeared unto him in a dream, saying, Joseph, thou son of David, fear not to take unto thee Mary thy wife: for that which is conceived in her is of the Holy Ghost.\\
And she shall bring forth a son, and thou shalt call his name JESUS: for he shall save his people from their sins.\\
Now all this was done, that it might be fulfilled which was spoken of the Lord by the prophet, saying,\\
Behold, a virgin shall be with child, and shall bring forth a son, and they shall call his name Emmanuel, which being interpreted is, God with us.\\
Then Joseph being raised from sleep did as the angel of the Lord had bidden him, and took unto him his wife:\\
And knew her not till she had brought forth her firstborn son: and he called his name JESUS.
\end{minipage}}
\vspace*{\fill}
\newpage
\LARGE%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 1:1--1:25.}\\
亞伯拉罕的後裔、大衛的子孫、耶穌基督的家譜．〔後裔子孫原文都作兒子下同〕\\
亞伯拉罕生以撒．以撒生雅各．雅各生猶大和他的弟兄．\\
猶大從他瑪氏生法勒斯和謝拉．法勒斯生希斯崙．希斯崙生亞蘭．\\
亞蘭生亞米拿達．亞米拿達生拿順．拿順生撒門．\\
撒門從喇合氏生波阿斯．波阿斯從路得氏生俄備得．俄備得生耶西．\\
耶西生大衛王。大衛從烏利亞的妻子生所羅門．\\
所羅門生羅波安．羅波安生亞比雅．亞比雅生亞撒．\\
亞撒生約沙法．約沙法生約蘭．約蘭生烏西亞．\\
烏西亞生約坦．約坦生亞哈斯．亞哈斯生希西家．\\
希西家生瑪拿西．瑪拿西生亞們．亞們生約西亞．\\
百姓被遷到巴比倫的時候、約西亞生耶哥尼雅和他的弟兄。\\
遷到巴比倫之後、耶哥尼雅生撒拉鐵．撒拉鐵生所羅巴伯．\\
所羅巴伯生亞比玉．亞比玉生以利亞敬．以利亞敬生亞所．\\
亞所生撒督．撒督生亞金．亞金生以律．\\
以律生以利亞撒．以利亞撒生馬但．馬但生雅各．\\
雅各生約瑟、就是馬利亞的丈夫．那稱為基督的耶穌、是從馬利亞生的。\\
這樣、從亞伯拉罕到大衛、共有十四代．從大衛到遷至巴比倫的時候、也有十四代．從遷至巴比倫的時候到基督、又有十四代。\\
耶穌基督降生的事、記在下面．他母親馬利亞已經許配了約瑟、還沒有迎娶、馬利亞就從聖靈懷了孕。\\
他丈夫約瑟是個義人、不願意明明的羞辱他、想要暗暗的把他休了。\\
正思念這事的時候、有主的使者向他夢中顯現、說、大衛的子孫約瑟、不要怕、只管娶過你的妻子馬利亞來．因他所懷的孕、是從聖靈來的。\\
他將要生一個兒子．你要給他起名叫耶穌．因他要將自己的百姓從罪惡裡救出來。\\
這一切的事成就、是要應驗主藉先知所說的話、\\
說、『必有童女、懷孕生子、人要稱他的名為以馬內利。』（以馬內利翻出來、就是　神與我們同在。）\\
約瑟醒了、起來、就遵著主使者的吩咐、把妻子娶過來．\\
只是沒有和他同房、等他生了兒子、〔有古卷作等他生了頭胎的兒子〕就給他起名叫耶穌。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
