\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.2in,bottom=0.2in,left=0.3in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 11 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 77 зач., XVIII, 23-35.}\\
Посему Царство Небесное подобно царю, который захотел сосчитаться с рабами своими;
\\
а как он не имел, чем заплатить, то государь его приказал продать его, и жену его, и детей, и всё, что он имел, и заплатить;
\\
тогда раб тот пал, и, кланяясь ему, говорил: государь! потерпи на мне, и всё тебе заплачу.
\\
Государь, умилосердившись над рабом тем, отпустил его и долг простил ему.
\\
Раб же тот, выйдя, нашел одного из товарищей своих, который должен был ему сто динариев, и, схватив его, душил, говоря: отдай мне, что должен.
\\
Тогда товарищ его пал к ногам его, умолял его и говорил: потерпи на мне, и всё отдам тебе.
\\
Но тот не захотел, а пошел и посадил его в темницу, пока не отдаст долга.
\\
Товарищи его, видев происшедшее, очень огорчились и, придя, рассказали государю своему всё бывшее.
\\
Тогда государь его призывает его и говорит: злой раб! весь долг тот я простил тебе, потому что ты упросил меня;
\\
не надлежало ли и тебе помиловать товарища твоего, как и я помиловал тебя?
\\
И, разгневавшись, государь его отдал его истязателям, пока не отдаст ему всего долга.
\\
Так и Отец Мой Небесный поступит с вами, если не простит каждый из вас от сердца своего брату своему согрешений его.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 18:23--18:35.}\\
Therefore is the kingdom of heaven likened unto a certain king, which would take account of his servants.\\
And when he had begun to reckon, one was brought unto him, which owed him ten thousand talents.\\
But forasmuch as he had not to pay, his lord commanded him to be sold, and his wife, and children, and all that he had, and payment to be made.\\
The servant therefore fell down, and worshipped him, saying, Lord, have patience with me, and I will pay thee all.\\
Then the lord of that servant was moved with compassion, and loosed him, and forgave him the debt.\\
But the same servant went out, and found one of his fellowservants, which owed him an hundred pence: and he laid hands on him, and took him by the throat, saying, Pay me that thou owest.\\
And his fellowservant fell down at his feet, and besought him, saying, Have patience with me, and I will pay thee all.\\
And he would not: but went and cast him into prison, till he should pay the debt.\\
So when his fellowservants saw what was done, they were very sorry, and came and told unto their lord all that was done.\\
Then his lord, after that he had called him, said unto him, O thou wicked servant, I forgave thee all that debt, because thou desiredst me:\\
Shouldest not thou also have had compassion on thy fellowservant, even as I had pity on thee?\\
And his lord was wroth, and delivered him to the tormentors, till he should pay all that was due unto him.\\
So likewise shall my heavenly Father do also unto you, if ye from your hearts forgive not every one his brother their trespasses.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 18:23--18:35.}\\
天國好像一個王、要和他僕人算賬。\\
纔算的時候、有人帶了一個欠一千萬銀子的來。\\
因為他沒有甚麼償還之物、主人吩咐把他和他妻子兒女、並一切所有的都賣了償還。\\
那僕人就俯伏拜他說、主阿、寬容我將來我都要還清。\\
那僕人的主人、就動了慈心、把他釋放了、並且免了他的債。\\
那僕人出來、遇見他的一個同伴、欠他十兩銀子、便揪著他、掐住他的喉嚨、說、你把所欠的還我。\\
他的同伴就俯伏央求他、說、寬容我罷、將來我必還清。\\
他不肯、竟去把他下在監裡、等他還了所欠的債。\\
眾同伴看見他所作的事、就甚憂愁、去把這事都告訴了主人。\\
於是主人叫了他來、對他說、你這惡奴才、你央求我、我就把你所欠的都免了．\\
你不應當憐恤你的同伴、像我憐恤你麼。\\
主人就大怒、把他交給掌刑的、等他還清了所欠的債。\\
你們各人、若不從心裡饒恕你的弟兄、我天父也要這樣待你們了。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
