\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[margin=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week about the Pharisee and the Publican (Liturgy)\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\doublespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 89 зач., XVIII, 10-14.}\\
два человека вошли в храм помолиться: один фарисей, а другой мытарь.\\
Фарисей, став, молился сам в себе так: Боже! благодарю Тебя, что я не таков, как прочие люди, грабители, обидчики, прелюбодеи, или как этот мытарь:\\
пощусь два раза в неделю, даю десятую часть из всего, что́ приобретаю.\\
Мытарь же, стоя вдали, не смел даже поднять глаз на небо; но, ударяя себя в грудь, говорил: Боже! будь милостив ко мне грешнику!\\
Сказываю вам, что сей пошел оправданным в дом свой более, нежели тот: ибо всякий, возвышающий сам себя, унижен будет, а унижающий себя возвысится. \\
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 18:10 -- 18:14.}\\
Two men went up into the temple to pray; the one a Pharisee, and the other a publican.\\
The Pharisee stood and prayed thus with himself, God, I thank thee, that I am not as other men are, extortioners, unjust, adulterers, or even as this publican.\\
I fast twice in the week, I give tithes of all that I possess.\\
And the publican, standing afar off, would not lift up so much as his eyes unto heaven, but smote upon his breast, saying, God be merciful to me a sinner.\\
I tell you, this man went down to his house justified rather than the other: for every one that exalteth himself shall be abased; and he that humbleth himself shall be exalted.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.5}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 18:10 -- 18:14.}\\
「有兩個人上聖殿去禱告，一個是法利賽人，一個是稅吏。 \\
法利賽人獨自站着，自言自語地禱告說：『上帝啊，我感謝你，我不像別人勒索、不義、姦淫，也不像這個稅吏。 \\
我每週禁食兩次，凡我所得的都獻上十分之一。』 \\
那稅吏遠遠地站着，連舉目望天也不敢，只捶着胸，說：『上帝啊，開恩可憐我這個罪人！』 \\
我告訴你們，這人回家去比那人倒算為義了。因為凡自高的，必降為卑；自甘卑微的，必升為高。」 \\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
