\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[margin=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\date{Week 20 after the Pentecost\vspace{-3ex}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\large
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus test
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 38 зач., VIII, 26-39.}\\
И приплыли в страну Гадаринскую, лежащую против Галилеи.\\
Когда же вышел Он на берег, встретил Его один человек из города, одержимый бесами с давнего времени, и в одежду не одевавшийся, и живший не в доме, а в гробах.\\
Он, увидев Иисуса, вскричал, пал пред Ним и громким голосом сказал: что́ Тебе до меня, Иисус, Сын Бога Всевышнего? умоляю Тебя, не мучь меня.\\
Ибо Иисус повелел нечистому духу выйти из сего человека, потому что он долгое время мучил его, так что его связывали цепями и узами, сберегая его; но он разрывал узы и был гоним бесом в пустыни.\\
Иисус спросил его: как тебе имя? Он сказал: легион,- потому что много бесов вошло в него.\\
И они просили Иисуса, чтобы не повелел им идти в бездну.\\
Тут же на горе паслось большое стадо свиней; и бесы просили Его, чтобы позволил им войти в них. Он позволил им.\\
Бесы, выйдя из человека, вошли в свиней, и бросилось стадо с крутизны в озеро и потонуло.\\
Пастухи, видя происшедшее, побежали и рассказали в городе и в селениях.\\
И вышли видеть происшедшее; и, придя к Иисусу, нашли человека, из которого вышли бесы, сидящего у ног Иисуса, одетого и в здравом уме; и ужаснулись.\\
Видевшие же рассказали им, как исцелился бесновавшийся.\\
И просил Его весь народ Гадаринской окрестности удалиться от них, потому что они объяты были великим страхом. Он вошел в лодку и возвратился.\\
Человек же, из которого вышли бесы, просил Его, чтобы быть с Ним. Но Иисус отпустил его, сказав:\\
возвратись в дом твой и расскажи, что́ сотворил тебе Бог. Он пошел и проповедовал по всему городу, что сотворил ему Иисус. \\
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 8:26 -- 8:39.}\\
And they arrived at the country of the Gadarenes, which is over against Galilee.\\
And when he went forth to land, there met him out of the city a certain man, which had devils long time, and ware no clothes, neither abode in any house, but in the tombs.\\
When he saw Jesus, he cried out, and fell down before him, and with a loud voice said, What have I to do with thee, Jesus, thou Son of God most high? I beseech thee, torment me not.\\
(For he had commanded the unclean spirit to come out of the man. For oftentimes it had caught him: and he was kept bound with chains and in fetters; and he brake the bands, and was driven of the devil into the wilderness.)\\
And Jesus asked him, saying, What is thy name? And he said, Legion: because many devils were entered into him.\\
And they besought him that he would not command them to go out into the deep.\\
And there was there an herd of many swine feeding on the mountain: and they besought him that he would suffer them to enter into them. And he suffered them.\\
Then went the devils out of the man, and entered into the swine: and the herd ran violently down a steep place into the lake, and were choked.\\
When they that fed them saw what was done, they fled, and went and told it in the city and in the country.\\
Then they went out to see what was done; and came to Jesus, and found the man, out of whom the devils were departed, sitting at the feet of Jesus, clothed, and in his right mind: and they were afraid.\\
They also which saw it told them by what means he that was possessed of the devils was healed.\\
Then the whole multitude of the country of the Gadarenes round about besought him to depart from them; for they were taken with great fear: and he went up into the ship, and returned back again.\\
Now the man out of whom the devils were departed besought him that he might be with him: but Jesus sent him away, saying,\\
Return to thine own house, and shew how great things God hath done unto thee. And he went his way, and published throughout the whole city how great things Jesus had done unto him.\\
\end{minipage}}
\newpage\huge
\singlespacing %for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 8:26 -- 8:39.}\\
他們到了 格拉森(註)人的地區，就在 加利利的對面。\\
耶穌上了岸，就有城裏一個被鬼附的人迎着他走來。這個人好久不穿衣服，不住在屋子裏，而住在墳墓裏。\\
他看見耶穌，就喊叫着俯伏在他面前，大聲說：「至高上帝的兒子耶穌，你為甚麼干擾我？我求你，不要叫我受苦！」\\
這是因耶穌曾吩咐污靈從這人身上出來。原來這污靈屢次抓住他；他常被人看守，又被鐵鏈和腳鐐捆鎖，他竟把鎖鏈掙斷，被鬼趕到曠野去。\\
耶穌問他：「你的名字叫甚麼？」他說：「 羣」；這是因為附着他的鬼多。\\
鬼就央求耶穌不要命令他們到無底坑裏去。\\
那裏有一大羣豬正在山坡上吃食，鬼央求耶穌准他們進入豬裏；耶穌准了他們。\\
於是鬼從那人出來，進入豬裏，那羣豬就闖下山崖，投進湖裏，淹死了。\\
放豬的看見這事就逃跑了，去告訴城裏和鄉下的人。\\
眾人出來，要看發生了甚麼事；到了耶穌那裏，發現那人坐在耶穌腳前，鬼已離開了他，穿着衣服，神智清醒，他們就害怕。\\
看見這事的人把被鬼附的人怎麼得醫治的事告訴他們。\\
格拉森周圍地區的人，因為害怕得很，都求耶穌離開他們；耶穌就上船回去了。\\
鬼已從身上出去的那人懇求要和耶穌在一起，耶穌卻打發他回去，說：\\
「你回家去，傳講上帝為你做了多麼大的事。」他就走遍全城，傳揚耶穌為他做了多麼大的事。 \\
\end{CJK}
\end{minipage}}
\end{document}
