%simple
\documentclass[12pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.2in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 32 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 94 зач., XIX, 1–10.}\\
Потом Иисус вошел в Иерихон и проходил через него.
\\
И вот, некто, именем Закхей, начальник мытарей и человек богатый,
\\
искал видеть Иисуса, кто Он, но не мог за народом, потому что мал был ростом,
\\
и, забежав вперед, взлез на смоковницу, чтобы увидеть Его, потому что Ему надлежало проходить мимо нее.
\\
Иисус, когда пришел на это место, взглянув, увидел его и сказал ему: Закхей! сойди скорее, ибо сегодня надобно Мне быть у тебя в доме.
\\
И он поспешно сошел и принял Его с радостью.
\\
И все, видя то, начали роптать, и говорили, что Он зашел к грешному человеку;
\\
Закхей же, став, сказал Господу: Господи! половину имения моего я отдам нищим, и, если кого чем обидел, воздам вчетверо.
\\
Иисус сказал ему: ныне пришло спасение дому сему, потому что и он сын Авраама,
\\
ибо Сын Человеческий пришел взыскать и спасти погибшее.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 19:1--19:10.}\\
And Jesus entered and passed through Jericho.\\
And, behold, there was a man named Zacchaeus, which was the chief among the publicans, and he was rich.\\
And he sought to see Jesus who he was; and could not for the press, because he was little of stature.\\
And he ran before, and climbed up into a sycomore tree to see him: for he was to pass that way.\\
And when Jesus came to the place, he looked up, and saw him, and said unto him, Zacchaeus, make haste, and come down; for to day I must abide at thy house.\\
And he made haste, and came down, and received him joyfully.\\
And when they saw it, they all murmured, saying, That he was gone to be guest with a man that is a sinner.\\
And Zacchaeus stood, and said unto the Lord; Behold, Lord, the half of my goods I give to the poor; and if I have taken any thing from any man by false accusation, I restore him fourfold.\\
And Jesus said unto him, This day is salvation come to this house, forsomuch as he also is a son of Abraham.\\
For the Son of man is come to seek and to save that which was lost.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.2}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 19:1--19:10.}\\
耶穌進了耶利哥、正經過的時候、\\
有一個人名叫撒該、作稅吏長、是個財主。\\
他要看看耶穌是怎樣的人．只因人多、他的身量又矮、所以不得看見。\\
就跑到前頭、爬上桑樹、要看耶穌、因為耶穌必從那裡經過。\\
耶穌到了那裡、抬頭一看、對他說、撒該、快下來、今天我必住在你家裡。\\
他就急忙下來、歡歡喜喜的接待耶穌。\\
眾人看見、都私下議論說、他竟到罪人家裡去住宿。\\
撒該站著、對主說、主阿、我把所有的一半給窮人．我若訛詐了誰、就還他四倍。\\
耶穌說、今天救恩到了這家、因為他也是亞伯拉罕的子孫。\\
人子來、為要尋找拯救失喪的人。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
