\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 6 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\onehalfspacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 29 зач., IX, 1-8.}\\
Тогда Он, войдя в лодку, переправился обратно и прибыл в Свой город.
\\
И вот, принесли к Нему расслабленного, положенного на постели. И, видя Иисус веру их, сказал расслабленному: дерзай, чадо! прощаются тебе грехи твои.
\\
При сем некоторые из книжников сказали сами в себе: Он богохульствует.
\\
Иисус же, видя помышления их, сказал: для чего вы мыслите худое в сердцах ваших?
\\
ибо что легче сказать: прощаются тебе грехи, или сказать: встань и ходи?
\\
Но чтобы вы знали, что Сын Человеческий имеет власть на земле прощать грехи,- тогда говорит расслабленному: встань, возьми постель твою, и иди в дом твой.
\\
И он встал, взял постель свою и пошел в дом свой.
\\
Народ же, видев это, удивился и прославил Бога, давшего такую власть человекам.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 9:1--9:8.}\\
And he entered into a ship, and passed over, and came into his own city.\\
And, behold, they brought to him a man sick of the palsy, lying on a bed: and Jesus seeing their faith said unto the sick of the palsy; Son, be of good cheer; thy sins be forgiven thee.\\
And, behold, certain of the scribes said within themselves, This man blasphemeth.\\
And Jesus knowing their thoughts said, Wherefore think ye evil in your hearts?\\
For whether is easier, to say, Thy sins be forgiven thee; or to say, Arise, and walk?\\
But that ye may know that the Son of man hath power on earth to forgive sins, (then saith he to the sick of the palsy,) Arise, take up thy bed, and go unto thine house.\\
And he arose, and departed to his house.\\
But when the multitudes saw it, they marvelled, and glorified God, which had given such power unto men.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.4}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 9:1--9:8.}\\
耶穌上了船、渡過海、來到自己的城裡。\\
有人用褥子抬著一個癱子、到耶穌跟前來．耶穌見他們的信心、就對癱子說、小子、放心罷．你的罪赦了。\\
有幾個文士心裡說、這個人說僭妄的話了。\\
耶穌知道他們的心意、就說、你們為甚麼心裡懷著惡念呢．\\
或說、你的罪赦了．或說、你起來行走．那一樣容易呢。\\
但要叫你們知道人子在地上有赦罪的權柄、就對癱子說、起來、拿你的褥子回家去罷。\\
那人就起來、回家去了。\\
眾人看見都驚奇、就歸榮耀與　神．因為他將這樣的權柄賜給人。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
