%simple
\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week Week 4 after Easter (Martyr)\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 24 зач., VI, 17-23.}\\
И, сойдя с ними, стал Он на ровном месте, и множество учеников Его, и много народа из всей Иудеи и Иерусалима и приморских мест Тирских и Сидонских,
\\
которые пришли послушать Его и исцелиться от болезней своих, также и страждущие от нечистых духов; и исцелялись.
\\
И весь народ искал прикасаться к Нему, потому что от Него исходила сила и исцеляла всех.
\\
И Он, возведя очи Свои на учеников Своих, говорил: Блаженны нищие духом, ибо ваше есть Царствие Божие.
\\
Блаженны алчущие ныне, ибо насытитесь. Блаженны плачущие ныне, ибо воссмеетесь.
\\
Блаженны вы, когда возненавидят вас люди и когда отлучат вас, и будут поносить, и пронесут имя ваше, как бесчестное, за Сына Человеческого.
\\
Возрадуйтесь в тот день и возвеселитесь, ибо велика вам награда на небесах. Так поступали с пророками отцы их.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 6:17--6:23.}\\
And he came down with them, and stood in the plain, and the company of his disciples, and a great multitude of people out of all Judaea and Jerusalem, and from the sea coast of Tyre and Sidon, which came to hear him, and to be healed of their diseases;\\
And they that were vexed with unclean spirits: and they were healed.\\
And the whole multitude sought to touch him: for there went virtue out of him, and healed them all.\\
And he lifted up his eyes on his disciples, and said, Blessed be ye poor: for yours is the kingdom of God.\\
Blessed are ye that hunger now: for ye shall be filled. Blessed are ye that weep now: for ye shall laugh.\\
Blessed are ye, when men shall hate you, and when they shall separate you from their company, and shall reproach you, and cast out your name as evil, for the Son of man's sake.\\
Rejoice ye in that day, and leap for joy: for, behold, your reward is great in heaven: for in the like manner did their fathers unto the prophets.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 6:17--6:23.}\\
耶穌和他們下了山、站在一塊平地上．同站的有許多門徒、又有許多百姓、從猶太全地、和耶路撒冷、並推羅西頓的海邊來．都要聽他講道、又指望醫治他們的病．\\
還有被污鬼纏磨的、也得了醫治。\\
眾人都想要摸他．因為有能力從他身上發出來、醫好了他們。\\
耶穌舉目看著門徒說、你們貧窮的人有福了．因為　神的國是你們的。\\
你們飢餓的人有福了．因為你們將要飽足。你們哀哭的人有福了．因為你們將要喜笑。\\
人為人子恨惡你們、拒絕你們、辱罵你們、棄掉你們的名、以為是惡、你們就有福了。\\
當那日你們要歡喜跳躍．因為你們在天上的賞賜是大的．他們的祖宗待先知也是這樣。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
