\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[margin=0.4in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week about the Pharisee and the Publican (Martyrs)\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\onehalfspacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 105-106 зач., XXI, 8-19.}\\
Он сказал: берегитесь, чтобы вас не ввели в заблуждение, ибо многие придут под именем Моим, говоря, что это Я; и это время близко: не ходите вслед их.\\
Когда же услышите о войнах и смятениях, не ужасайтесь, ибо этому надлежит быть прежде; но не тотчас конец.\\
Тогда сказал им: восстанет народ на народ, и царство на царство;\\
будут большие землетрясения по местам, и глады, и моры, и ужасные явления, и великие знамения с неба.\\
Прежде же всего того возложат на вас руки и будут гнать вас, предавая в синагоги и в темницы, и поведут пред царей и правителей за имя Мое;\\
будет же это вам для свидетельства.\\
Итак положите себе на сердце не обдумывать заранее, что отвечать,\\
ибо Я дам вам уста и премудрость, которой не возмогут противоречить ни противостоять все, противящиеся вам.\\
Преданы также будете и родителями, и братьями, и родственниками, и друзьями, и некоторых из вас умертвят;\\
и будете ненавидимы всеми за имя Мое,\\
но и волос с головы вашей не пропадет,-\\
терпением вашим спасайте души ваши. \\
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 21:8 -- 21:19.}\\
And he said, Take heed that ye be not deceived: for many shall come in my name, saying, I am Christ; and the time draweth near: go ye not therefore after them.\\
But when ye shall hear of wars and commotions, be not terrified: for these things must first come to pass; but the end is not by and by.\\
Then said he unto them, Nation shall rise against nation, and kingdom against kingdom:\\
And great earthquakes shall be in divers places, and famines, and pestilences; and fearful sights and great signs shall there be from heaven.\\
But before all these, they shall lay their hands on you, and persecute you, delivering you up to the synagogues, and into prisons, being brought before kings and rulers for my name's sake.\\
And it shall turn to you for a testimony.\\
Settle it therefore in your hearts, not to meditate before what ye shall answer:\\
For I will give you a mouth and wisdom, which all your adversaries shall not be able to gainsay nor resist.\\
And ye shall be betrayed both by parents, and brethren, and kinsfolks, and friends; and some of you shall they cause to be put to death.\\
And ye shall be hated of all men for my name's sake.\\
But there shall not an hair of your head perish.\\
In your patience possess ye your souls.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 21:8 -- 21:19.}\\
耶穌說：「你們要謹慎，不要受迷惑，因為將有好些人冒我的名來，說『我是基督』，又說『時候近了』，你們不要跟從他們！ \\
當你們聽見打仗和動亂的事，不要驚惶；因為這些事必須先發生，但終結不會立刻就到。」 \\
於是耶穌對他們說：「民要攻打民，國要攻打國， \\
將有大地震，多處必有饑荒、瘟疫，又有可怕的異象和大神蹟從天上顯現。 \\
但這一切的事以前，有人要下手拿你們，迫害你們，把你們交給會堂，並且關在監裏，又為我名的緣故拉你們到君王和統治者面前。 \\
但這些事終必成為你們作見證的機會。 \\
所以，你們要立定心意，不要預先考慮怎樣申辯； \\
因為我必賜你們口才和智慧，是你們一切敵人所敵不住、駁不倒的。 \\
連你們的父母、兄弟、親族、朋友也要把你們交給官府；你們中間也將有被他們害死的。 \\
你們要為我的名被眾人憎恨。 \\
然而，你們連一根頭髮也不會損失。 \\
你們憑着堅忍，就必保全性命。」 \\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
