\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 13 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 87 зач., XXI, 33-42.}\\
Выслушайте другую притчу: был некоторый хозяин дома, который насадил виноградник, обнес его оградою, выкопал в нем точило, построил башню и, отдав его виноградарям, отлучился.
\\
Когда же приблизилось время плодов, он послал своих слуг к виноградарям взять свои плоды;
\\
виноградари, схватив слуг его, иного прибили, иного убили, а иного побили камнями.
\\
Опять послал он других слуг, больше прежнего; и с ними поступили так же.
\\
Наконец, послал он к ним своего сына, говоря: постыдятся сына моего.
\\
Но виноградари, увидев сына, сказали друг другу: это наследник; пойдем, убьем его и завладеем наследством его.
\\
И, схватив его, вывели вон из виноградника и убили.
\\
Итак, когда придет хозяин виноградника, что сделает он с этими виноградарями?
\\
Говорят Ему: злодеев сих предаст злой смерти, а виноградник отдаст другим виноградарям, которые будут отдавать ему плоды во времена свои.
\\
Иисус говорит им: неужели вы никогда не читали в Писании: камень, который отвергли строители, тот самый сделался главою угла? Это от Господа, и есть дивно в очах наших?
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 21:33--21:42.}\\
Hear another parable: There was a certain householder, which planted a vineyard, and hedged it round about, and digged a winepress in it, and built a tower, and let it out to husbandmen, and went into a far country:\\
And when the time of the fruit drew near, he sent his servants to the husbandmen, that they might receive the fruits of it.\\
And the husbandmen took his servants, and beat one, and killed another, and stoned another.\\
Again, he sent other servants more than the first: and they did unto them likewise.\\
But last of all he sent unto them his son, saying, They will reverence my son.\\
But when the husbandmen saw the son, they said among themselves, This is the heir; come, let us kill him, and let us seize on his inheritance.\\
And they caught him, and cast him out of the vineyard, and slew him.\\
When the lord therefore of the vineyard cometh, what will he do unto those husbandmen?\\
They say unto him, He will miserably destroy those wicked men, and will let out his vineyard unto other husbandmen, which shall render him the fruits in their seasons.\\
Jesus saith unto them, Did ye never read in the scriptures, The stone which the builders rejected, the same is become the head of the corner: this is the Lord's doing, and it is marvellous in our eyes?\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 21:33--21:42.}\\
你們再聽一個比喻．有個家主、栽了一個葡萄園、周圍圈上籬笆、裡面挖了一個壓酒池、蓋了一座樓、租給園戶、就往外國去了。\\
收果子的時候近了、就打發僕人、到園戶那裡去收果子。\\
園戶拿住僕人。打了一個、殺了一個、用石頭打死一個。\\
主人又打發別的僕人去、比先前更多．園戶還是照樣待他們。\\
後來打發他的兒子到他們那裡去、意思說、他們必尊敬我的兒子。\\
不料、園戶看見他兒子、就彼此說、這是承受產業的．來罷、我們殺他、佔他的產業。\\
他們就拿住他、推出葡萄園外、殺了。\\
園主來的時候、要怎樣處治這些園戶呢。\\
他們說、要下毒手除滅那些惡人、將葡萄園另租給那按著時候交果子的園戶。\\
耶穌說、經上寫著、『匠人所棄的石頭、已作了房角的頭塊石頭．這是主所作的、在我們眼中看為希奇。』這經你們沒有念過麼。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
