\documentclass[12pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.3in,bottom=0.3in,left=0.3in,right=0.4in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 35 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 91 зач., XVIII, 18-27.}\\
И спросил Его некто из начальствующих: Учитель благий! что мне делать, чтобы наследовать жизнь вечную?
\\
Иисус сказал ему: что ты называешь Меня благим? никто не благ, как только один Бог;
\\
знаешь заповеди: не прелюбодействуй, не убивай, не кради, не лжесвидетельствуй, почитай отца твоего и матерь твою.
\\
Он же сказал: все это сохранил я от юности моей.
\\
Услышав это, Иисус сказал ему: еще одного недостает тебе: все, что имеешь, продай и раздай нищим, и будешь иметь сокровище на небесах, и приходи, следуй за Мною.
\\
Он же, услышав сие, опечалился, потому что был очень богат.
\\
Иисус, видя, что он опечалился, сказал: как трудно имеющим богатство войти в Царствие Божие!
\\
ибо удобнее верблюду пройти сквозь игольные уши, нежели богатому войти в Царствие Божие.
\\
Слышавшие сие сказали: кто же может спастись?
\\
Но Он сказал: невозможное человекам возможно Богу.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 18:18--18:27.}\\
And a certain ruler asked him, saying, Good Master, what shall I do to inherit eternal life?\\
And Jesus said unto him, Why callest thou me good? none is good, save one, that is, God.\\
Thou knowest the commandments, Do not commit adultery, Do not kill, Do not steal, Do not bear false witness, Honour thy father and thy mother.\\
And he said, All these have I kept from my youth up.\\
Now when Jesus heard these things, he said unto him, Yet lackest thou one thing: sell all that thou hast, and distribute unto the poor, and thou shalt have treasure in heaven: and come, follow me.\\
And when he heard this, he was very sorrowful: for he was very rich.\\
And when Jesus saw that he was very sorrowful, he said, How hardly shall they that have riches enter into the kingdom of God!\\
For it is easier for a camel to go through a needle's eye, than for a rich man to enter into the kingdom of God.\\
And they that heard it said, Who then can be saved?\\
And he said, The things which are impossible with men are possible with God.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.2}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 18:18--18:27.}\\
有一個官問耶穌說、良善的夫子、我該作甚麼事、纔可以承受永生。\\
耶穌對他說、你為甚麼稱我是良善的．除了　神一位之外、再沒有良善的。\\
誡命你是曉得的、不可姦淫、不可殺人、不可偷盜、不可作假見證、當孝敬父母。\\
那人說、這一切我從小都遵守了。\\
耶穌聽見了、就說、你還缺少一件．要變賣你一切所有的、分給窮人、就必有財寶在天上．你還要來跟從我。\\
他聽見這話、就甚憂愁、因為他很富足。\\
耶穌看見他就說、有錢財的人進　神的國、是何等的難哪。\\
駱駝穿過鍼的眼、比財主進　神的國、還容易呢。\\
聽見的人說、這樣、誰能得救呢。\\
耶穌說、在人所不能的事、在　神卻能。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
