\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 3 after Easter\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мк., 69 зач., XV, 43 - XVI, 8.}\\
пришел Иосиф из Аримафеи, знаменитый член совета, который и сам ожидал Царствия Божия, осмелился войти к Пилату, и просил тела Иисусова.
\\
Пилат удивился, что Он уже умер, и, призвав сотника, спросил его, давно ли умер?
\\
И, узнав от сотника, отдал тело Иосифу.
\\
Он, купив плащаницу и сняв Его, обвил плащаницею, и положил Его во гробе, который был высечен в скале, и привалил камень к двери гроба.
\\
Мария же Магдалина и Мария Иосиева смотрели, где Его полагали.
\\
По прошествии субботы Мария Магдалина и Мария Иаковлева и Саломия купили ароматы, чтобы идти помазать Его.
\\
И весьма рано, в первый день недели, приходят ко гробу, при восходе солнца,
\\
и говорят между собою: кто отвалит нам камень от двери гроба?
\\
И, взглянув, видят, что камень отвален; а он был весьма велик.
\\
И, войдя во гроб, увидели юношу, сидящего на правой стороне, облеченного в белую одежду; и ужаснулись.
\\
Он же говорит им: не ужасайтесь. Иисуса ищете Назарянина, распятого; Он воскрес, Его нет здесь. Вот место, где Он был положен.
\\
Но идите, скажите ученикам Его и Петру, что Он предваряет вас в Галилее; там Его увидите, как Он сказал вам.
\\
И, выйдя, побежали от гроба; их объял трепет и ужас, и никому ничего не сказали, потому что боялись.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Mark 15:43--16:8.}\\
Joseph of Arimathaea, an honourable counsellor, which also waited for the kingdom of God, came, and went in boldly unto Pilate, and craved the body of Jesus.\\
And Pilate marvelled if he were already dead: and calling unto him the centurion, he asked him whether he had been any while dead.\\
And when he knew it of the centurion, he gave the body to Joseph.\\
And he bought fine linen, and took him down, and wrapped him in the linen, and laid him in a sepulchre which was hewn out of a rock, and rolled a stone unto the door of the sepulchre.\\
And Mary Magdalene and Mary the mother of Joses beheld where he was laid.\\
And when the sabbath was past, Mary Magdalene, and Mary the mother of James, and Salome, had bought sweet spices, that they might come and anoint him.\\
And very early in the morning the first day of the week, they came unto the sepulchre at the rising of the sun.\\
And they said among themselves, Who shall roll us away the stone from the door of the sepulchre?\\
And when they looked, they saw that the stone was rolled away: for it was very great.\\
And entering into the sepulchre, they saw a young man sitting on the right side, clothed in a long white garment; and they were affrighted.\\
And he saith unto them, Be not affrighted: Ye seek Jesus of Nazareth, which was crucified: he is risen; he is not here: behold the place where they laid him.\\
But go your way, tell his disciples and Peter that he goeth before you into Galilee: there shall ye see him, as he said unto you.\\
And they went out quickly, and fled from the sepulchre; for they trembled and were amazed: neither said they any thing to any man; for they were afraid.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬可福音 15:43--16:8.}\\
有亞利馬太的約瑟前來、他是尊貴的議士、也是等候　神國的．他放膽進去見彼拉多、求耶穌的身體。\\
彼拉多詫異耶穌已經死了．便叫百夫長來、問他耶穌死了久不久。\\
既從百夫長得知實情、就把耶穌的屍首賜給約瑟。\\
約瑟買了細麻布、把耶穌取下來、用細麻布裹好、安放在磐石中鑿出來的墳墓裡．又滾過一塊石頭來擋住墓門。\\
抹大拉的馬利亞、和約西的母親馬利亞、都看見安放他的地方。\\
過了安息日、抹大拉的馬利亞、和雅各的母親馬利亞、並撒羅米、買了香膏、要去膏耶穌的身體。\\
七日的第一日清早、出太陽的時候、他們來到墳墓那裡。\\
彼此說、誰給我們把石頭從墓門滾開呢。\\
那石頭原來很大、他們抬頭一看、卻見石頭已經滾開了。\\
他們進了墳墓、看見一個少年人坐在右邊、穿著白袍．就甚驚恐。\\
那少年人對他們說、不要驚恐．你們尋找那釘十字架的拿撒勒人耶穌．他已經復活了、不在這裡．請看安放他的地方。\\
你們可以去告訴他的門徒和彼得說、他在你們以先往加利利去．在那裡你們要見他、正如他從前所告訴你們的。\\
他們就出來、從墳墓那裡逃跑．又發抖、又驚奇、甚麼也不告訴人．因為他們害怕。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
