\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 21 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 83 зач., XVI, 19-31.}\\
Некоторый человек был богат, одевался в порфиру и виссон и каждый день пиршествовал блистательно.
\\
Был также некоторый нищий, именем Лазарь, который лежал у ворот его в струпьях
\\
и желал напитаться крошками, падающими со стола богача, и псы, приходя, лизали струпья его.
\\
Умер нищий и отнесен был Ангелами на лоно Авраамово. Умер и богач, и похоронили его.
\\
И в аде, будучи в муках, он поднял глаза свои, увидел вдали Авраама и Лазаря на лоне его
\\
и, возопив, сказал: отче Аврааме! умилосердись надо мною и пошли Лазаря, чтобы омочил конец перста своего в воде и прохладил язык мой, ибо я мучаюсь в пламени сем.
\\
Но Авраам сказал: чадо! вспомни, что ты получил уже доброе твое в жизни твоей, а Лазарь - злое; ныне же он здесь утешается, а ты страдаешь;
\\
и сверх всего того между нами и вами утверждена великая пропасть, так что хотящие перейти отсюда к вам не могут, также и оттуда к нам не переходят.
\\
Тогда сказал он: так прошу тебя, отче, пошли его в дом отца моего,
\\
ибо у меня пять братьев; пусть он засвидетельствует им, чтобы и они не пришли в это место мучения.
\\
Авраам сказал ему: у них есть Моисей и пророки; пусть слушают их.
\\
Он же сказал: нет, отче Аврааме, но если кто из мертвых придет к ним, покаются.
\\
Тогда Авраам сказал ему: если Моисея и пророков не слушают, то если бы кто и из мертвых воскрес, не поверят.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 16:19--16:31.}\\
There was a certain rich man, which was clothed in purple and fine linen, and fared sumptuously every day:\\
And there was a certain beggar named Lazarus, which was laid at his gate, full of sores,\\
And desiring to be fed with the crumbs which fell from the rich man's table: moreover the dogs came and licked his sores.\\
And it came to pass, that the beggar died, and was carried by the angels into Abraham's bosom: the rich man also died, and was buried;\\
And in hell he lift up his eyes, being in torments, and seeth Abraham afar off, and Lazarus in his bosom.\\
And he cried and said, Father Abraham, have mercy on me, and send Lazarus, that he may dip the tip of his finger in water, and cool my tongue; for I am tormented in this flame.\\
But Abraham said, Son, remember that thou in thy lifetime receivedst thy good things, and likewise Lazarus evil things: but now he is comforted, and thou art tormented.\\
And beside all this, between us and you there is a great gulf fixed: so that they which would pass from hence to you cannot; neither can they pass to us, that would come from thence.\\
Then he said, I pray thee therefore, father, that thou wouldest send him to my father's house:\\
For I have five brethren; that he may testify unto them, lest they also come into this place of torment.\\
Abraham saith unto him, They have Moses and the prophets; let them hear them.\\
And he said, Nay, father Abraham: but if one went unto them from the dead, they will repent.\\
And he said unto him, If they hear not Moses and the prophets, neither will they be persuaded, though one rose from the dead.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 16:19--16:31.}\\
有一個財主、穿著紫色袍和細麻布衣服、天天奢華宴樂。\\
又有一個討飯的、名叫拉撒路、渾身生瘡、被人放在財主門口、\\
要得財主桌子上掉下來的零碎充飢．並且狗來餂他的瘡。\\
後來那討飯的死了、被天使帶去放在亞伯拉罕的懷裡．財主也死了、並且埋葬了。\\
他在陰間受痛苦、舉目遠遠的望見亞伯拉罕、又望見拉撒路在他懷裡．\\
就喊著說、我祖亞伯拉罕哪、可憐我罷、打發拉撒路來、用指頭尖蘸點水、涼涼我的舌頭．因為我在這火焰裡、極其痛苦。\\
亞伯拉罕說、兒阿、你該回想你生前享過福、拉撒路也受過苦．如今他在這裡得安慰、你倒受痛苦。\\
不但這樣、並且在你我之間、有深淵限定、以致人要從這邊過到你們那邊、是不能的、要從那邊過到我們這邊、也是不能的。\\
財主說、我祖阿、既是這樣、求你打發拉撒路到我父家去．\\
因為我還有五個弟兄．他可以對他們作見證、免得他們也來到這痛苦的地方。\\
亞伯拉罕說、他們有摩西和先知的話、可以聽從。\\
他說、我祖亞伯拉罕哪、不是的．若有一個從死裡復活的、到他們那裡去的、他們必要悔改。\\
亞伯拉罕說、若不聽從摩西和先知的話、就是有一個從死裡復活的、他們也是不聽勸。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
