\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[left=-0.1in,right=0.3in,top=0.2in,bottom=0.1in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week about the Last Judgement\vspace{
-3ex%for author
}}
\date{\vspace{
-8ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 106 зач., XXV, 31-46.}\\
Когда же приидет Сын Человеческий во славе Своей и все святые Ангелы с Ним, тогда сядет на престоле славы Своей,\\
и соберутся пред Ним все народы; и отделит одних от других, как пастырь отделяет овец от козлов;\\
и поставит овец по правую Свою сторону, а козлов - по левую.\\
Тогда скажет Царь тем, которые по правую сторону Его: приидите, благословенные Отца Моего, наследуйте Царство, уготованное вам от создания мира:\\
ибо алкал Я, и вы дали Мне есть; жаждал, и вы напоили Меня; был странником, и вы приняли Меня;\\
был наг, и вы одели Меня; был болен, и вы посетили Меня; в темнице был, и вы пришли ко Мне.\\
Тогда праведники скажут Ему в ответ: Господи! когда мы видели Тебя алчущим, и накормили? или жаждущим, и напоили?\\
когда мы видели Тебя странником, и приняли? или нагим, и одели?\\
когда мы видели Тебя больным, или в темнице, и пришли к Тебе?\\
И Царь скажет им в ответ: истинно говорю вам: так как вы сделали это одному из сих братьев Моих меньших, то сделали Мне.\\
Тогда скажет и тем, которые по левую сторону: идите от Меня, проклятые, в огонь вечный, уготованный диаволу и ангелам его:\\
ибо алкал Я, и вы не дали Мне есть; жаждал, и вы не напоили Меня;\\
был странником, и не приняли Меня; был наг, и не одели Меня; болен и в темнице, и не посетили Меня.\\
Тогда и они скажут Ему в ответ: Господи! когда мы видели Тебя алчущим, или жаждущим, или странником, или нагим, или больным, или в темнице, и не послужили Тебе?\\
Тогда скажет им в ответ: истинно говорю вам: так как вы не сделали этого одному из сих меньших, то не сделали Мне.\\
И пойдут сии в му́ку вечную, а праведники в жизнь вечную. \\
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 25:31 -- 25:46.}\\
When the Son of man shall come in his glory, and all the holy angels with him, then shall he sit upon the throne of his glory:\\
And before him shall be gathered all nations: and he shall separate them one from another, as a shepherd divideth his sheep from the goats:\\
And he shall set the sheep on his right hand, but the goats on the left.\\
Then shall the King say unto them on his right hand, Come, ye blessed of my Father, inherit the kingdom prepared for you from the foundation of the world:\\
For I was an hungred, and ye gave me meat: I was thirsty, and ye gave me drink: I was a stranger, and ye took me in:\\
Naked, and ye clothed me: I was sick, and ye visited me: I was in prison, and ye came unto me.\\
Then shall the righteous answer him, saying, Lord, when saw we thee an hungred, and fed thee? or thirsty, and gave thee drink?\\
When saw we thee a stranger, and took thee in? or naked, and clothed thee?\\
Or when saw we thee sick, or in prison, and came unto thee?\\
And the King shall answer and say unto them, Verily I say unto you, Inasmuch as ye have done it unto one of the least of these my brethren, ye have done it unto me.\\
Then shall he say also unto them on the left hand, Depart from me, ye cursed, into everlasting fire, prepared for the devil and his angels:\\
For I was an hungred, and ye gave me no meat: I was thirsty, and ye gave me no drink:\\
I was a stranger, and ye took me not in: naked, and ye clothed me not: sick, and in prison, and ye visited me not.\\
Then shall they also answer him, saying, Lord, when saw we thee an hungred, or athirst, or a stranger, or naked, or sick, or in prison, and did not minister unto thee?\\
Then shall he answer them, saying, Verily I say unto you, Inasmuch as ye did it not to one of the least of these, ye did it not to me.\\
And these shall go away into everlasting punishment: but the righteous into life eternal.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 25:31 -- 25:46.}\\
當人子在他榮耀裡、同著眾天使降臨的時候、要坐在他榮耀的寶座上．\\
萬民都要聚集在他面前．他要把他們分別出來、好像牧羊的分別綿羊山羊一般．\\
把綿羊安置在右邊、山羊在左邊。\\
於是王要向那右邊的說、你們這蒙我父賜福的、可來承受那創世以來為你們所預備的國。\\
因為我餓了、你們給我喫．渴了、你們給我喝．我作客旅、你們留我住．\\
我赤身露體、你們給我穿．我病了、你們看顧我．我在監裡、你們來看我。\\
義人就回答說、主阿、我們甚麼時候見你餓了給你喫、渴了給你喝．\\
甚麼時候見你作客旅留你住、或是赤身露體給你穿．\\
又甚麼時候見你病了、或是在監裡、來看你呢。\\
王要回答說、我實在告訴你們、這些事你們既作在我這弟兄中一個最小的身上、就是作在我身上了。\\
王又要向那左邊的說、你們這被咒詛的人、離開我、進入那為魔鬼和他的使者所預備的永火裡去。\\
因為我餓了、你們不給我喫．渴了、你們不給我喝．\\
我作客旅、你們不留我住．我赤身露體、你們不給我穿．我病了、我在監裡、你們不來看顧我。\\
他們也要回答說、主阿、我們甚麼時候見你餓了、或渴了、或作客旅、或赤身露體、或病了、或在監裡、不伺候你呢。\\
王要回答說、我實在告訴你們、這些事你們既不作在我這弟兄中一個最小的身上、就是不作在我身上了。\\
這些人要往永刑裡去．那些義人要往永生裡去。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
