\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.1in,bottom=0.1in,left=0.4in,right=0.4in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels\vspace{-1ex}}
\author{Week 5 of the Great Lent\vspace{
-6ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.48\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мк., 47 зач., X, 32-45.}\\
Когда были они на пути, восходя в Иерусалим, Иисус шел впереди их, а они ужасались и, следуя за Ним, были в страхе. || Подозвав двенадцать, Он опять начал им говорить о том, что; будет с Ним:
\\
вот, мы восходим в Иерусалим, и Сын Человеческий предан будет первосвященникам и книжникам, и осудят Его на смерть, и предадут Его язычникам,
\\
и поругаются над Ним, и будут бить Его, и оплюют Его, и убьют Его; и в третий день воскреснет.
\\
Тогда подошли к Нему сыновья Зеведеевы Иаков и Иоанн и сказали: Учитель! мы желаем, чтобы Ты сделал нам, о чем попросим.
\\
Он сказал им: что хотите, чтобы Я сделал вам?
\\
Они сказали Ему: дай нам сесть у Тебя, одному по правую сторону, а другому по левую в славе Твоей.
\\
Но Иисус сказал им: не знаете, чего просите. Можете ли пить чашу, которую Я пью, и креститься крещением, которым Я крещусь?
\\
Они отвечали: можем. Иисус же сказал им: чашу, которую Я пью, будете пить, и крещением, которым Я крещусь, будете креститься;
\\
а дать сесть у Меня по правую сторону и по левую - не от Меня зависит, но кому уготовано.
\\
И, услышав, десять начали негодовать на Иакова и Иоанна.
\\
Иисус же, подозвав их, сказал им: вы знаете, что почитающиеся князьями народов господствуют над ними, и вельможи их властвуют ими.
\\
Но между вами да не будет так: а кто хочет быть бо&льшим между вами, да будем вам слугою;
\\
и кто хочет быть первым между вами, да будет всем рабом.
\\
Ибо и Сын Человеческий не для того пришел, чтобы Ему служили, но чтобы послужить и отдать душу Свою для искупления многих.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Mark 10:32--10:45.}\\
And they were in the way going up to Jerusalem; and Jesus went before them: and they were amazed; and as they followed, they were afraid. And he took again the twelve, and began to tell them what things should happen unto him,\\
Saying, Behold, we go up to Jerusalem; and the Son of man shall be delivered unto the chief priests, and unto the scribes; and they shall condemn him to death, and shall deliver him to the Gentiles:\\
And they shall mock him, and shall scourge him, and shall spit upon him, and shall kill him: and the third day he shall rise again.\\
And James and John, the sons of Zebedee, come unto him, saying, Master, we would that thou shouldest do for us whatsoever we shall desire.\\
And he said unto them, What would ye that I should do for you?\\
They said unto him, Grant unto us that we may sit, one on thy right hand, and the other on thy left hand, in thy glory.\\
But Jesus said unto them, Ye know not what ye ask: can ye drink of the cup that I drink of? and be baptized with the baptism that I am baptized with?\\
And they said unto him, We can. And Jesus said unto them, Ye shall indeed drink of the cup that I drink of; and with the baptism that I am baptized withal shall ye be baptized:\\
But to sit on my right hand and on my left hand is not mine to give; but it shall be given to them for whom it is prepared.\\
And when the ten heard it, they began to be much displeased with James and John.\\
But Jesus called them to him, and saith unto them, Ye know that they which are accounted to rule over the Gentiles exercise lordship over them; and their great ones exercise authority upon them.\\
But so shall it not be among you: but whosoever will be great among you, shall be your minister:\\
And whosoever of you will be the chiefest, shall be servant of all.\\
For even the Son of man came not to be ministered unto, but to minister, and to give his life a ransom for many.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬可福音 10:32--10:45.}\\
他們行路上耶路撒冷去．耶穌在前頭走、門徒就希奇、跟從的人也害怕．耶穌又叫過十二個門徒來、把自己將要遭遇的事、告訴他們說、\\
看哪、我們上耶路撒冷去、人子將要被交給祭司長和文士、他們要定他死罪、交給外邦人。\\
他們要戲弄他、吐唾沫在他臉上、鞭打他、殺害他．過了三天、他要復活。\\
西庇太的兒子雅各、約翰進前來、對耶穌說、夫子、我們無論求你甚麼、願你給我們作。\\
耶穌說、要我給你們作甚麼。\\
他們說、賜我們在你的榮耀裡、一個坐在你右邊、一個坐在你左邊。\\
耶穌說、你們不知道所求的是甚麼。我所喝的杯．你們能喝麼．我所受的洗、你們能受麼。\\
他們說、我們能。耶穌說、我所喝的杯、你們也要喝．我所受的洗、你們也要受．\\
只是坐在我的左右、不是我可以賜的．乃是為誰預備的、就賜給誰。\\
那十個門徒聽見、就惱怒雅各、約翰。\\
耶穌叫他們來對他們說、你們知道、外邦人有尊為君王的、治理他們．有大臣操權管束他們。\\
只是在你們中間、不是這樣．你們中間、誰願為大、就必作你們的用人．\\
在你們中間、誰願為首、就必作眾人的僕人。\\
因為人子來、並不是要受人的服事、乃是要服事人、並且要捨命、作多人的贖價。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
