\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 17 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 17 зач., V, 1-11.}\\
Однажды, когда народ теснился к Нему, чтобы слышать слово Божие, а Он стоял у озера Геннисаретского,
\\
увидел Он две лодки, стоящие на озере; а рыболовы, выйдя из них, вымывали сети.
\\
Войдя в одну лодку, которая была Симонова, Он просил его отплыть несколько от берега и, сев, учил народ из лодки.
\\
Когда же перестал учить, сказал Симону: отплыви на глубину и закиньте сети свои для лова.
\\
Симон сказал Ему в ответ: Наставник! мы трудились всю ночь и ничего не поймали, но по слову Твоему закину сеть.
\\
Сделав это, они поймали великое множество рыбы, и даже сеть у них прорывалась.
\\
И дали знак товарищам, находившимся на другой лодке, чтобы пришли помочь им; и пришли, и наполнили обе лодки, так что они начинали тонуть.
\\
Увидев это, Симон Петр припал к коленям Иисуса и сказал: выйди от меня, Господи! потому что я человек грешный.
\\
Ибо ужас объял его и всех, бывших с ним, от этого лова рыб, ими пойманных;
\\
также и Иакова и Иоанна, сыновей Зеведеевых, бывших товарищами Симону. И сказал Симону Иисус: не бойся; отныне будешь ловить человеков.
\\
И, вытащив обе лодки на берег, оставили всё и последовали за Ним.
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 5:1--5:11.}\\
And it came to pass, that, as the people pressed upon him to hear the word of God, he stood by the lake of Gennesaret,\\
And saw two ships standing by the lake: but the fishermen were gone out of them, and were washing their nets.\\
And he entered into one of the ships, which was Simon's, and prayed him that he would thrust out a little from the land. And he sat down, and taught the people out of the ship.\\
Now when he had left speaking, he said unto Simon, Launch out into the deep, and let down your nets for a draught.\\
And Simon answering said unto him, Master, we have toiled all the night, and have taken nothing: nevertheless at thy word I will let down the net.\\
And when they had this done, they inclosed a great multitude of fishes: and their net brake.\\
And they beckoned unto their partners, which were in the other ship, that they should come and help them. And they came, and filled both the ships, so that they began to sink.\\
When Simon Peter saw it, he fell down at Jesus' knees, saying, Depart from me; for I am a sinful man, O Lord.\\
For he was astonished, and all that were with him, at the draught of the fishes which they had taken:\\
And so was also James, and John, the sons of Zebedee, which were partners with Simon. And Jesus said unto Simon, Fear not; from henceforth thou shalt catch men.\\
And when they had brought their ships to land, they forsook all, and followed him.
\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 5:1--5:11.}\\
耶穌站在革尼撒勒湖邊、眾人擁擠他、要聽　神的道。\\
他見有兩隻船灣在湖邊．打魚的人卻離開船、洗網去了。\\
有一隻船、是西門的、耶穌就上去、請他把船撐開、稍微離岸、就坐下、從船上教訓眾人。\\
講完了、對西門說、把船開到水深之處、下網打魚。\\
西門說、夫子、我們整夜勞力、並沒有打著甚麼．但依從你的話、我就下網。\\
他們下了網、就圈住許多魚、網險些裂開．\\
便招呼那隻船上的同伴來幫助。他們就來把魚裝滿了兩隻船、甚至船要沉下去。\\
西門彼得看見、就俯伏在耶穌膝前、說、主阿、離開我、我是個罪人。\\
他和一切同在的人、都驚訝這一網所打的魚．\\
他的夥伴西庇太的兒子、雅各、約翰、也是這樣。耶穌對西門說、不要怕、從今以後、你要得人了。\\
他們把兩隻船攏了岸、就撇下所有的跟從了耶穌。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
