\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 18 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мк., 37 зач., VIII, 34 - IX, 1.}\\
И, подозвав народ с учениками Своими, сказал им: || кто хочет идти за Мною, отвергнись себя, и возьми крест свой, и следуй за Мною.
\\
Ибо кто хочет душу свою сберечь, тот потеряет ее, а кто потеряет душу свою ради Меня и Евангелия, тот сбережет ее.
\\
Ибо какая польза человеку, если он приобретет весь мир, а душе своей повредит?
\\
Или какой выкуп даст человек за душу свою?
\\
Ибо кто постыдится Меня и Моих слов в роде сем прелюбодейном и грешном, того постыдится и Сын Человеческий, когда приидет в славе Отца Своего со святыми Ангелами.
\\
И сказал им: истинно говорю вам: есть некоторые из стоящих здесь, которые не вкусят смерти, как уже увидят Царствие Божие, пришедшее в силе.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Mark 8:34--9:1.}\\
And when he had called the people unto him with his disciples also, he said unto them, Whosoever will come after me, let him deny himself, and take up his cross, and follow me.\\
For whosoever will save his life shall lose it; but whosoever shall lose his life for my sake and the gospel's, the same shall save it.\\
For what shall it profit a man, if he shall gain the whole world, and lose his own soul?\\
Or what shall a man give in exchange for his soul?\\
Whosoever therefore shall be ashamed of me and of my words in this adulterous and sinful generation; of him also shall the Son of man be ashamed, when he cometh in the glory of his Father with the holy angels.\\
And he said unto them, Verily I say unto you, That there be some of them that stand here, which shall not taste of death, till they have seen the kingdom of God come with power.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬可福音 8:34--9:1.}\\
於是叫眾人和門徒來、對他們說、若有人要跟從我、就當捨己、背起他的十字架來跟從我。\\
因為凡要救自己生命的、〔生命或作靈魂下同〕必喪掉生命．凡為我和福音喪掉生命的、必救了生命。\\
人就是賺得全世界、賠上自己的生命、有甚麼益處呢。\\
人還能拿什麼換生命呢。\\
凡在這淫亂罪惡的世代、把我和我的道當作可恥的、人子在他父的榮耀裡、同聖天使降臨的時候、也要把那人當作可恥的。\\
耶穌又對他們說、我實在告訴你們、站在這裡的、有人在沒嘗死味以前、必要看見　神的國大有能力臨到。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
