\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[bottom=0.3in,left=0.5in,right=0.5in,top=0.1in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{\vspace{-4ex}Divine Liturgy\\Reading from The Gospels\vspace{-1.5ex}}
\author{Christmas\vspace{-4.5ex}}
\date{\vspace{-6ex}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\large
\onehalfspacing %\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 3 зач., II, 1-12.}\\
Когда же Иисус родился в Вифлееме Иудейском во дни царя Ирода, пришли в Иерусалим волхвы* с востока и говорят:\\
где родившийся Царь Иудейский? ибо мы видели звезду Его на востоке и пришли поклониться Ему.\\
Услышав это, Ирод царь встревожился, и весь Иерусалим с ним.\\
И, собрав всех первосвященников и книжников народных, спрашивал у них: где должно родиться Христу?\\
Они же сказали ему: в Вифлееме Иудейском, ибо так написано через пророка:\\
и ты, Вифлеем, земля Иудина, ничем не меньше воеводств Иудиных, ибо из тебя произойдет Вождь, Который упасет народ Мой, Израиля.\\
Тогда Ирод, тайно призвав волхвов, выведал от них время появления звезды\\
и, послав их в Вифлеем, сказал: пойдите, тщательно разведайте о Младенце и, когда найдете, известите меня, чтобы и мне пойти поклониться Ему.\\
Они, выслушав царя, пошли. И се, звезда, которую видели они на востоке, шла перед ними, как наконец пришла и остановилась над местом, где был Младенец.\\
Увидев же звезду, они возрадовались радостью весьма великою,\\
и, войдя в дом, увидели Младенца с Мариею, Матерью Его, и, пав, поклонились Ему; и, открыв сокровища свои, принесли Ему дары: золото, ладан и смирну.\\
И, получив во сне откровение не возвращаться к Ироду, иным путем отошли в страну свою. \\
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 2:1 -- 2:12.}\\
Now when Jesus was born in Bethlehem of Judaea in the days of Herod the king, behold, there came wise men from the east to Jerusalem,\\
Saying, Where is he that is born King of the Jews? for we have seen his star in the east, and are come to worship him.\\
When Herod the king had heard these things, he was troubled, and all Jerusalem with him.\\
And when he had gathered all the chief priests and scribes of the people together, he demanded of them where Christ should be born.\\
And they said unto him, In Bethlehem of Judaea: for thus it is written by the prophet,\\
And thou Bethlehem, in the land of Juda, art not the least among the princes of Juda: for out of thee shall come a Governor, that shall rule my people Israel.\\
Then Herod, when he had privily called the wise men, enquired of them diligently what time the star appeared.\\
And he sent them to Bethlehem, and said, Go and search diligently for the young child; and when ye have found him, bring me word again, that I may come and worship him also.\\
When they had heard the king, they departed; and, lo, the star, which they saw in the east, went before them, till it came and stood over where the young child was.\\
When they saw the star, they rejoiced with exceeding great joy.\\
And when they were come into the house, they saw the young child with Mary his mother, and fell down, and worshipped him: and when they had opened their treasures, they presented unto him gifts; gold, and frankincense, and myrrh.\\
And being warned of God in a dream that they should not return to Herod, they departed into their own country another way.\\
\end{minipage}}
\newpage\huge
\vspace*{\fill}
\singlespacing %for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 2:1 -- 2:12.}\\
在 希律作王的時候，耶穌生在 猶太的 伯利恆。有幾個博學之士(註)從東方來到 耶路撒冷，說：\\
「那生下來作 猶太人之王的在哪裏？我們在東方看見他的星，特來拜他。」\\
希律王聽見了，就心裏不安； 耶路撒冷全城的人也都不安。\\
他就召集了祭司長和民間的文士，問他們：「基督該生在哪裏？」\\
他們說：「在 猶太的 伯利恆。因為有先知記着：\\
『 猶大地的 伯利恆啊，\\
你在 猶大諸城中並不是最小的；\\
因為將來有一位統治者要從你那裏出來，\\
牧養我 以色列民。』」\\
於是， 希律暗地裏召了博學之士來，查問那星是甚麼時候出現的，\\
就派他們往 伯利恆去，說：「你們去仔細尋訪那小孩子，找到了就來報信，我也好去拜他。」\\
他們聽了王的話就去了。忽然，在東方所看到的那顆星在前面引領他們，一直行到小孩子所在地方的上方就停住了。\\
他們看見那星，就非常歡喜；\\
進了房子，看見小孩子和他母親 馬利亞，就俯伏拜那小孩子，揭開寶盒，拿出黃金、乳香、沒藥，作為禮物獻給他。\\
因為在夢中得到主的指示，不要回去見 希律，他們就從別的路回自己的家鄉去了。 \\
\end{CJK}
\end{minipage}}
\vspace*{\fill}
\end{document}
