\documentclass[12pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.0in,bottom=0.0in,left=0.3in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 20 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 26 зач., VI, 31-36.}\\
И как хотите, чтобы с вами поступали люди, так и вы поступайте с ними.
\\
И если любите любящих вас, какая вам за то благодарность? ибо и грешники любящих их любят.
\\
И если делаете добро тем, которые вам делают добро, какая вам за то благодарность? ибо и грешники то же делают.
\\
И если взаймы даёте тем, от которых надеетесь получить обратно, какая вам за то благодарность? ибо и грешники дают взаймы грешникам, чтобы получить обратно столько же.
\\
Но вы любите врагов ваших, и благотворите, и взаймы давайте, не ожидая ничего; и будет вам награда великая, и будете сынами Всевышнего; ибо Он благ и к неблагодарным и злым.
\\
Итак, будьте милосерды, как и Отец ваш милосерд.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 6:31--6:36.}\\
And as ye would that men should do to you, do ye also to them likewise.\\
For if ye love them which love you, what thank have ye? for sinners also love those that love them.\\
And if ye do good to them which do good to you, what thank have ye? for sinners also do even the same.\\
And if ye lend to them of whom ye hope to receive, what thank have ye? for sinners also lend to sinners, to receive as much again.\\
But love ye your enemies, and do good, and lend, hoping for nothing again; and your reward shall be great, and ye shall be the children of the Highest: for he is kind unto the unthankful and to the evil.\\
Be ye therefore merciful, as your Father also is merciful.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 6:31--6:36.}\\
你們願意人怎樣待你們、你們也要怎樣待人。\\
你們若單愛那愛你們的人、有甚麼可酬謝的呢．就是罪人也愛那愛他們的人。\\
你們若善待那善待你們的人、有甚麼可酬謝的呢．就是罪人也是這樣行。\\
你們若借給人、指望從他收回、有甚麼可酬謝的呢．就是罪人也借給罪人、要如數收回。\\
你們倒要愛仇敵、也要善待他們、並要借給人不指望償還．你們的賞賜就必大了、你們也必作至高者的兒子．因為他恩待那忘恩的和作惡的。\\
你們要慈悲、像你們的父慈悲一樣。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
