\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.2in,bottom=0.2in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 5 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 28 зач., VIII, 28 - IX, 1.}\\
И вот, они закричали: что Тебе до нас, Иисус, Сын Божий? пришел Ты сюда прежде времени мучить нас.
\\
Вдали же от них паслось большое стадо свиней.
\\
И бесы просили Его: если выгонишь нас, то пошли нас в стадо свиней.
\\
И Он сказал им: идите. И они, выйдя, пошли в стадо свиное. И вот, всё стадо свиней бросилось с крутизны в море и погибло в воде.
\\
Пастухи же побежали и, придя в город, рассказали обо всем, и о том, что было с бесноватыми.
\\
И вот, весь город вышел навстречу Иисусу; и, увидев Его, просили, чтобы Он отошел от пределов их.
\\
Тогда Он, войдя в лодку, переправился обратно и прибыл в Свой город.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 8:28--9:1.}\\
And when he was come to the other side into the country of the Gergesenes, there met him two possessed with devils, coming out of the tombs, exceeding fierce, so that no man might pass by that way.\\
And, behold, they cried out, saying, What have we to do with thee, Jesus, thou Son of God? art thou come hither to torment us before the time?\\
And there was a good way off from them an herd of many swine feeding.\\
So the devils besought him, saying, If thou cast us out, suffer us to go away into the herd of swine.\\
And he said unto them, Go. And when they were come out, they went into the herd of swine: and, behold, the whole herd of swine ran violently down a steep place into the sea, and perished in the waters.\\
And they that kept them fled, and went their ways into the city, and told every thing, and what was befallen to the possessed of the devils.\\
And, behold, the whole city came out to meet Jesus: and when they saw him, they besought him that he would depart out of their coasts.\\
And he entered into a ship, and passed over, and came into his own city.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 8:28--9:1.}\\
耶穌既渡到那邊去、來到加大拉人的地方、就有兩個被鬼附的人、從墳塋裡出來迎著他、極其兇猛、甚至沒有人能從那條路上經過。\\
他們喊著說、　神的兒子、我們與你有甚麼相干．時候還沒有到、你就上這裡來叫我們受苦麼。\\
離他們很遠、有一大群豬喫食。\\
鬼就央求耶穌說、若把我們趕出去、就打發我們進入豬群罷。\\
耶穌說、去罷．鬼就出來、進入豬群．全群忽然闖下山崖、投在海裡淹死了。\\
放豬的就逃跑進城、將這一切事、和被鬼附的人所遭遇的、都告訴人。\\
合城的人、都出來迎見耶穌．既見了、就央求他離開他們的境界。\\
耶穌上了船、渡過海、來到自己的城裡。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
