\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.1in,bottom=0.3in,right=0.5in,left=0.0in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 4 of the Great Lent\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мк., 40 зач., IX, 17-31.}\\
Один из народа сказал в ответ: Учитель! я привел к Тебе сына моего, одержимого духом немым:\\
где ни схватывает его, повергает его на землю, и он испускает пену, и скрежещет зубами своими, и цепенеет. Говорил я ученикам Твоим, чтобы изгнали его, и они не могли.\\
Отвечая ему, Иисус сказал: о, род неверный! доколе буду с вами? доколе буду терпеть вас? Приведите его ко Мне.\\
И привели его к Нему. Как скоро бесноватый увидел Его, дух сотряс его; он упал на землю и валялся, испуская пену.\\
И спросил Иисус отца его: как давно это сделалось с ним? Он сказал: с детства;\\
и многократно дух бросал его и в огонь и в воду, чтобы погубить его; но, если что можешь, сжалься над нами и помоги нам.\\
Иисус сказал ему: если сколько-нибудь можешь веровать, всё возможно верующему.\\
И тотчас отец отрока воскликнул со слезами: верую, Господи! помоги моему неверию.\\
Иисус, видя, что сбегается народ, запретил духу нечистому, сказав ему: дух немой и глухой! Я повелеваю тебе, выйди из него и впредь не входи в него.\\
И, вскрикнув и сильно сотрясши его, вышел; и он сделался, как мертвый, так что многие говорили, что он умер.\\
Но Иисус, взяв его за руку, поднял его; и он встал.\\
И как вошел Иисус в дом, ученики Его спрашивали Его наедине: почему мы не могли изгнать его?\\
И сказал им: сей род не может выйти иначе, как от молитвы и поста.\\
Выйдя оттуда, проходили через Галилею; и Он не хотел, чтобы кто узнал.\\
Ибо учил Своих учеников и говорил им, что Сын Человеческий предан будет в руки человеческие и убьют Его, и, по убиении, в третий день воскреснет. \\
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Mark 9:17--9:31.}\\
And one of the multitude answered and said, Master, I have brought unto thee my son, which hath a dumb spirit;\\
And wheresoever he taketh him, he teareth him: and he foameth, and gnasheth with his teeth, and pineth away: and I spake to thy disciples that they should cast him out; and they could not.\\
He answereth him, and saith, O faithless generation, how long shall I be with you? how long shall I suffer you? bring him unto me.\\
And they brought him unto him: and when he saw him, straightway the spirit tare him; and he fell on the ground, and wallowed foaming.\\
And he asked his father, How long is it ago since this came unto him? And he said, Of a child.\\
And ofttimes it hath cast him into the fire, and into the waters, to destroy him: but if thou canst do any thing, have compassion on us, and help us.\\
Jesus said unto him, If thou canst believe, all things are possible to him that believeth.\\
And straightway the father of the child cried out, and said with tears, Lord, I believe; help thou mine unbelief.\\
When Jesus saw that the people came running together, he rebuked the foul spirit, saying unto him, Thou dumb and deaf spirit, I charge thee, come out of him, and enter no more into him.\\
And the spirit cried, and rent him sore, and came out of him: and he was as one dead; insomuch that many said, He is dead.\\
But Jesus took him by the hand, and lifted him up; and he arose.\\
And when he was come into the house, his disciples asked him privately, Why could not we cast him out?\\
And he said unto them, This kind can come forth by nothing, but by prayer and fasting.\\
And they departed thence, and passed through Galilee; and he would not that any man should know it.\\
For he taught his disciples, and said unto them, The Son of man is delivered into the hands of men, and they shall kill him; and after that he is killed, he shall rise the third day.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬可福音 9:17--9:31.}\\
眾人中間有一個人回答說、夫子、我帶了我的兒子到你這裡來、他被啞巴鬼附著．\\
無論在那裡、鬼捉弄他、把他摔倒、他就口中流沫、咬牙切齒、身體枯乾、我請過你的門徒把鬼趕出去、他們卻是不能。\\
耶穌說、噯、不信的世代阿、我在你們這裡要到幾時呢．我忍耐你們要到幾時呢．把他帶到我這裡來罷。\\
他們就帶了他來。他一見耶穌、鬼便叫他重重的抽瘋．倒在地上、翻來覆去、口中流沫。\\
耶穌問他父親說、他得這病、有多少日子呢．回答說、從小的時候。\\
鬼屢次把他扔在火裡、水裡、要滅他．你若能作甚麼、求你憐憫我們、幫助我們。\\
耶穌對他說、你若能信、在信的人、凡事都能。\\
孩子的父親立時喊著說、我信．但我信不足、求主幫助。〔有古卷作立時流淚的喊著說〕\\
耶穌看見眾人都跑上來、就斥責那污鬼、說、你這聾啞的鬼、我吩咐你從他裡頭出來、再不要進去。\\
那鬼喊叫、使孩子大大的抽了一陣瘋、就出來了．孩子好像死了一般。以致眾人多半說、他是死了。\\
但耶穌拉著他的手、扶他起來、他就站起來了。\\
耶穌進了屋子、門徒就暗暗的問他說、我們為甚麼不能趕出他去呢。\\
耶穌說、非用禱告、〔有古卷在此有禁食二字〕這一類的鬼、總不能出來。〔或作不能趕他出來〕\\
他們離開那地方、經過加利利．耶穌不願意人知道。\\
於是教訓門徒、說、人子將要被交在人手裡、他們要殺害他．被殺以後、過三天他要復活。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
