\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week about the Pharisee and the Publician\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Ин., 1 зач., I, 1-17.}\\
В начале было Слово, и Слово было у Бога, и Слово было Бог.
\\
Оно было в начале у Бога.
\\
Все чрез Него начало быть, и без Него ничто не начало быть, что начало быть.
\\
В Нем была жизнь, и жизнь была свет человеков.
\\
И свет во тьме светит, и тьма не объяла его.
\\
Был человек, посланный от Бога; имя ему Иоанн.
\\
Он пришел для свидетельства, чтобы свидетельствовать о Свете, дабы все уверовали чрез него.
\\
Он не был свет, но был послан, чтобы свидетельствовать о Свете.
\\
Был Свет истинный, Который просвещает всякого человека, приходящего в мир.
\\
В мире был, и мир чрез Него начал быть, и мир Его не познал.
\\
Пришел к своим, и свои Его не приняли.
\\
А тем, которые приняли Его, верующим во имя Его, дал власть быть чадами Божиими,
\\
которые ни от крови, ни от хотения плоти, ни от хотения мужа, но от Бога родились.
\\
И Слово стало плотию, и обитало с нами, полное благодати и истины; и мы видели славу Его, славу, как Единородного от Отца.
\\
Иоанн свидетельствует о Нем и, восклицая, говорит: Сей был Тот, о Котором я сказал, что Идущий за мною стал впереди меня, потому что был прежде меня.
\\
И от полноты Его все мы приняли и благодать на благодать,
\\
ибо закон дан чрез Моисея; благодать же и истина произошли чрез Иисуса Христа.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{John 1:1--1:17.}\\
In the beginning was the Word, and the Word was with God, and the Word was God.\\
The same was in the beginning with God.\\
All things were made by him; and without him was not any thing made that was made.\\
In him was life; and the life was the light of men.\\
And the light shineth in darkness; and the darkness comprehended it not.\\
There was a man sent from God, whose name was John.\\
The same came for a witness, to bear witness of the Light, that all men through him might believe.\\
He was not that Light, but was sent to bear witness of that Light.\\
That was the true Light, which lighteth every man that cometh into the world.\\
He was in the world, and the world was made by him, and the world knew him not.\\
He came unto his own, and his own received him not.\\
But as many as received him, to them gave he power to become the sons of God, even to them that believe on his name:\\
Which were born, not of blood, nor of the will of the flesh, nor of the will of man, but of God.\\
And the Word was made flesh, and dwelt among us, (and we beheld his glory, the glory as of the only begotten of the Father,) full of grace and truth.\\
John bare witness of him, and cried, saying, This was he of whom I spake, He that cometh after me is preferred before me: for he was before me.\\
And of his fulness have all we received, and grace for grace.\\
For the law was given by Moses, but grace and truth came by Jesus Christ.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{約翰福音 1:1--1:17.}\\
太初有道、道與　神同在、道就是　神。\\
這道太初與　神同在。\\
萬物是藉著他造的．凡被造的、沒有一樣不是藉著他造的。\\
生命在他裡頭．這生命就是人的光。\\
光照在黑暗裡、黑暗卻不接受光。\\
有一個人、是從　神那裡差來的、名叫約翰。\\
這人來、為要作見證、就是為光作見證、叫眾人因他可以信。\\
他不是那光、乃是要為光作見證。\\
那光是真光、照亮一切生在世上的人。\\
他在世界、世界也是藉著他造的、世界卻不認識他。\\
他到自己的地方來、自己的人倒不接待他。\\
凡接待他的、就是信他名的人、他就賜他們權柄、作　神的兒女。\\
這等人不是從血氣生的、不是從情慾生的、也不是從人意生的、乃是從　神生的。\\
道成了肉身、住在我們中間、充充滿滿的有恩典有真理。我們也見過他的榮光、正是父獨生子的榮光。\\
約翰為他作見證、喊著說、這就是我曾說、那在我以後來的、反成了在我以前的．因他本來在我以前。\\
從他豐滿的恩典裡我們都領受了、而且恩上加恩。\\
律法本是藉著摩西傳的、恩典和真理、都是由耶穌基督來的。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
