\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.0in,bottom=0.0in,left=-0.15in,right=0.25in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{\vspace{-4ex}Divine Liturgy\\Reading from The Gospels\vspace{-1.5ex}}
\author{Week 5 after Easter\vspace{
-7.5ex%for author
}}
\date{\vspace{
-6.5ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
%\small%for eng/rus
\fontsize{0.5cm}{1em}
\footnotesize
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.46\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Ин., 12 зач., IV, 5-42.}\\
Итак приходит Он в город Самарийский, называемый Сихарь, близ участка земли, данного Иаковом сыну своему Иосифу.
\\
Там был колодезь Иаковлев. Иисус, утрудившись от пути, сел у колодезя. Было около шестого часа.
\\
Приходит женщина из Самарии почерпнуть воды. Иисус говорит ей: дай Мне пить.
\\
Ибо ученики Его отлучились в город купить пищи.
\\
Женщина Самарянская говорит Ему: как ты, будучи Иудей, просишь пить у меня, Самарянки? ибо Иудеи с Самарянами не сообщаются.
\\
Иисус сказал ей в ответ: если бы ты знала дар Божий и Кто говорит тебе: дай Мне пить, то ты сама просила бы у Него, и Он дал бы тебе воду живую.
\\
Женщина говорит Ему: господин! тебе и почерпнуть нечем, а колодезь глубок; откуда же у тебя вода живая?
\\
Неужели ты больше отца нашего Иакова, который дал нам этот колодезь и сам из него пил, и дети его, и скот его?
\\
Иисус сказал ей в ответ: всякий, пьющий воду сию, возжаждет опять,
\\
а кто будет пить воду, которую Я дам ему, тот не будет жаждать вовек; но вода, которую Я дам ему, сделается в нем источником воды, текущей в жизнь вечную.
\\
Женщина говорит Ему: господин! дай мне этой воды, чтобы мне не иметь жажды и не приходить сюда черпать.
\\
Иисус говорит ей: пойди, позови мужа твоего и приди сюда.
\\
Женщина сказала в ответ: у меня нет мужа. Иисус говорит ей: правду ты сказала, что у тебя нет мужа,
\\
ибо у тебя было пять мужей, и тот, которого ныне имеешь, не муж тебе; это справедливо ты сказала.
\\
Женщина говорит Ему: Господи! вижу, что Ты пророк.
\\
Отцы наши поклонялись на этой горе, а вы говорите, что место, где должно поклоняться, находится в Иерусалиме.
\\
Иисус говорит ей: поверь Мне, что наступает время, когда и не на горе сей, и не в Иерусалиме будете поклоняться Отцу.
\\
Вы не знаете, чему кланяетесь, а мы знаем, чему кланяемся, ибо спасение от Иудеев.
\\
Но настанет время и настало уже, когда истинные поклонники будут поклоняться Отцу в духе и истине, ибо таких поклонников Отец ищет Себе.
\\
Бог есть дух, и поклоняющиеся Ему должны поклоняться в духе и истине.
\\
Женщина говорит Ему: знаю, что придет Мессия, то есть Христос; когда Он придет, то возвестит нам все.
\\
Иисус говорит ей: это Я, Который говорю с тобою.
\\
В это время пришли ученики Его, и удивились, что Он разговаривал с женщиною; однако ж ни один не сказал: чего Ты требуешь? или: о чем говоришь с нею?
\\
Тогда женщина оставила водонос свой и пошла в город, и говорит людям:
\\
пойдите, посмотрите Человека, Который сказал мне все, что я сделала: не Он ли Христос?
\\
Они вышли из города и пошли к Нему.
\\
Между тем ученики просили Его, говоря: Равви! ешь.
\\
Но Он сказал им: у Меня есть пища, которой вы не знаете.
\\
Посему ученики говорили между собою: разве кто принес Ему есть?
\\
Иисус говорит им: Моя пища есть творить волю Пославшего Меня и совершить дело Его.
\\
Не говорите ли вы, что еще четыре месяца, и наступит жатва? А Я говорю вам: возведите очи ваши и посмотрите на нивы, как они побелели и поспели к жатве.
\\
Жнущий получает награду и собирает плод в жизнь вечную, так что и сеющий и жнущий вместе радоваться будут,
\\
ибо в этом случае справедливо изречение: один сеет, а другой жнет.
\\
Я послал вас жать то, над чем вы не трудились: другие трудились, а вы вошли в труд их.
\\
И многие Самаряне из города того уверовали в Него по слову женщины, свидетельствовавшей, что Он сказал ей все, что она сделала.
\\
И потому, когда пришли к Нему Самаряне, то просили Его побыть у них; и Он пробыл там два дня.
\\
И еще большее число уверовали по Его слову.
\\
А женщине той говорили: уже не по твоим речам веруем, ибо сами слышали и узнали, что Он истинно Спаситель мира, Христос.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.46\textwidth}

\textbf{John 4:5--4:42.}\\
Then cometh he to a city of Samaria, which is called Sychar, near to the parcel of ground that Jacob gave to his son Joseph.\\
Now Jacob's well was there. Jesus therefore, being wearied with his journey, sat thus on the well: and it was about the sixth hour.\\
There cometh a woman of Samaria to draw water: Jesus saith unto her, Give me to drink.\\
(For his disciples were gone away unto the city to buy meat.)\\
Then saith the woman of Samaria unto him, How is it that thou, being a Jew, askest drink of me, which am a woman of Samaria? for the Jews have no dealings with the Samaritans.\\
Jesus answered and said unto her, If thou knewest the gift of God, and who it is that saith to thee, Give me to drink; thou wouldest have asked of him, and he would have given thee living water.\\
The woman saith unto him, Sir, thou hast nothing to draw with, and the well is deep: from whence then hast thou that living water?\\
Art thou greater than our father Jacob, which gave us the well, and drank thereof himself, and his children, and his cattle?\\
Jesus answered and said unto her, Whosoever drinketh of this water shall thirst again:\\
But whosoever drinketh of the water that I shall give him shall never thirst; but the water that I shall give him shall be in him a well of water springing up into everlasting life.\\
The woman saith unto him, Sir, give me this water, that I thirst not, neither come hither to draw.\\
Jesus saith unto her, Go, call thy husband, and come hither.\\
The woman answered and said, I have no husband. Jesus said unto her, Thou hast well said, I have no husband:\\
For thou hast had five husbands; and he whom thou now hast is not thy husband: in that saidst thou truly.\\
The woman saith unto him, Sir, I perceive that thou art a prophet.\\
Our fathers worshipped in this mountain; and ye say, that in Jerusalem is the place where men ought to worship.\\
Jesus saith unto her, Woman, believe me, the hour cometh, when ye shall neither in this mountain, nor yet at Jerusalem, worship the Father.\\
Ye worship ye know not what: we know what we worship: for salvation is of the Jews.\\
But the hour cometh, and now is, when the true worshippers shall worship the Father in spirit and in truth: for the Father seeketh such to worship him.\\
God is a Spirit: and they that worship him must worship him in spirit and in truth.\\
The woman saith unto him, I know that Messias cometh, which is called Christ: when he is come, he will tell us all things.\\
Jesus saith unto her, I that speak unto thee am he.\\
And upon this came his disciples, and marvelled that he talked with the woman: yet no man said, What seekest thou? or, Why talkest thou with her?\\
The woman then left her waterpot, and went her way into the city, and saith to the men,\\
Come, see a man, which told me all things that ever I did: is not this the Christ?\\
Then they went out of the city, and came unto him.\\
In the mean while his disciples prayed him, saying, Master, eat.\\
But he said unto them, I have meat to eat that ye know not of.\\
Therefore said the disciples one to another, Hath any man brought him ought to eat?\\
Jesus saith unto them, My meat is to do the will of him that sent me, and to finish his work.\\
Say not ye, There are yet four months, and then cometh harvest? behold, I say unto you, Lift up your eyes, and look on the fields; for they are white already to harvest.\\
And he that reapeth receiveth wages, and gathereth fruit unto life eternal: that both he that soweth and he that reapeth may rejoice together.\\
And herein is that saying true, One soweth, and another reapeth.\\
I sent you to reap that whereon ye bestowed no labour: other men laboured, and ye are entered into their labours.\\
And many of the Samaritans of that city believed on him for the saying of the woman, which testified, He told me all that ever I did.\\
So when the Samaritans were come unto him, they besought him that he would tarry with them: and he abode there two days.\\
And many more believed because of his own word;\\
And said unto the woman, Now we believe, not because of thy saying: for we have heard him ourselves, and know that this is indeed the Christ, the Saviour of the world.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Large%for chi
\vspace*{\fill}
\begin{spacing}{0.93}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{約翰福音 4:5--4:42.}\\
於是到了撒瑪利亞的一座城、名叫敘加、靠近雅各給他兒子約瑟的那塊地。\\
在那裡有雅各井。耶穌因走路困乏、就坐在井旁．那時約有午正。\\
有一個撒瑪利亞的婦人來打水．耶穌對他說、請你給我水喝。\\
那時門徒進城買食物去了。\\
撒瑪利亞的婦人對他說、你既是猶太人、怎麼向我一個撒瑪利亞婦人要水喝呢。原來猶太人和撒瑪利亞人沒有來往。\\
耶穌回答說、你若知道　神的恩賜、和對你說給我水喝的是誰、你必早求他、他也必早給了你活水。\\
婦人說、先生沒有打水的器具、井又深、你從那裡得活水呢。\\
我們的祖宗雅各、將這井留給我們．他自己和兒子並牲畜、也都喝這井裡的水、難道你比他還大麼。\\
耶穌回答說、凡喝這水的、還要再渴．\\
人若喝我所賜的水就永遠不渴．我所賜的水、要在他裡頭成為泉源、直湧到永生。\\
婦人說、先生、請把這水賜給我、叫我不渴、也不用來這麼遠打水。\\
耶穌說、你去叫你丈夫也到這裡來。\\
婦人說、我沒有丈夫。耶穌說、你說沒有丈夫、是不錯的．\\
你已經有五個丈夫．你現在有的、並不是你的丈夫．你這話是真的．\\
婦人說、先生、我看出你是先知。\\
我們的祖宗在這山上禮拜．你們倒說、應當禮拜的地方是在耶路撒冷。\\
耶穌說、婦人、你當信我、時候將到、你們拜父、也不在這山上、也不在耶路撒冷。\\
你們所拜的、你們不知道．我們所拜的、我們知道．因為救恩是從猶太人出來的。\\
時候將到、如今就是了、那真正拜父的、要用心靈和誠實拜他、因為父要這樣的人拜他。\\
　神是個靈．〔或無個字〕所以拜他的、必須用心靈和誠實拜他。\\
婦人說、我知道彌賽亞、（就是那稱為基督的）要來．他來了、必將一切的事都告訴我們。\\
耶穌說、這和你說話的就是他。\\
當下門徒回來、就希奇耶穌和一個婦人說話．只是沒有人說、你是要甚麼．或說、你為甚麼和他說話。\\
那婦人就留下水罐子、往城裡去、對眾人說、\\
你們來看、有一個人將我素來所行的一切事、都給我說出來了、莫非這就是基督麼。\\
眾人就出城往耶穌那裡去。\\
這其間、門徒對耶穌說、拉比、請喫。\\
耶穌說、我有食物喫、是你們不知道的。\\
門徒就彼此對問說、莫非有人拿甚麼給他喫麼。\\
耶穌說、我的食物就是遵行差我來者的旨意、作成他的工。\\
你們豈不說、到收割的時候、還有四個月麼．我告訴你們、舉目向田觀看、莊稼已經熟了、〔原文作發白〕可以收割了。\\
收割的人得工價、積蓄五穀到永生．叫撒種的和收割的一同快樂。\\
俗語說、那人撒種、這人收割、這話可見是真的。\\
我差你們去收你們所沒有勞苦的．別人勞苦、你們享受他們所勞苦的。\\
那城裡有好些撒瑪利亞人信了耶穌、因為那婦人作見證說、他將我素來所行的一切事、都給我說出來了．\\
於是撒瑪利亞人來見耶穌、求他在他們那裡住下．他便在那裡住了兩天。\\
因耶穌的話、信的人就更多了．\\
便對婦人說、現在我們信、不是因為你的話、是我們親自聽見了、知道這真是救世主。\\
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
