\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.1in,bottom=0.01in,left=0.1in,right=0.4in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{\vspace{-4ex} Divine Liturgy\\Reading from The Gospels\vspace{-1ex}}
\author{Week 17 after the Pentecost\vspace{
-2ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\normalsize%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Ин., 60 зач., XIX, 6-11, 13-20, 25-28, 30-35.}\\
Когда же увидели Его первосвященники и служители, то закричали: || распни, распни Его! Пилат говорит им: возьмите Его вы, и распните; ибо я не нахожу в Нем вины.
\\
Иудеи отвечали ему: мы имеем закон, и по закону нашему Он должен умереть, потому что сделал Себя Сыном Божиим.
\\
Пилат, услышав это слово, больше убоялся.
\\
И опять вошел в преторию и сказал Иисусу: откуда Ты? Но Иисус не дал ему ответа.
\\
Пилат говорит Ему: мне ли не отвечаешь? не знаешь ли, что я имею власть распять Тебя и власть имею отпустить Тебя?
\\
Иисус отвечал: ты не имел бы надо Мною никакой власти, если бы не было дано тебе свыше; посему более греха на том, кто предал Меня тебе.
\\
Пилат, услышав это слово, вывел вон Иисуса и сел на судилище, на месте, называемом Лифостронон, а по-еврейски Гаввафа.\\
Тогда была пятница перед Пасхою, и час шестый. И сказал Пилат Иудеям: се, Царь ваш!
\\
Но они закричали: возьми, возьми, распни Его! Пилат говорит им: Царя ли вашего распну? Первосвященники отвечали: нет у нас царя, кроме кесаря.
\\
Тогда наконец он предал Его им на распятие. И взяли Иисуса и повели.
\\
И, неся крест Свой, Он вышел на место, называемое Лобное, по-еврейски Голгофа;
\\
там распяли Его и с Ним двух других, по ту и по другую сторону, а посреди Иисуса.
\\
Пилат же написал и надпись, и поставил на кресте. Написано было: Иисус Назорей, Царь Иудейский.
\\
Эту надпись читали многие из Иудеев, потому что место, где был распят Иисус, было недалеко от города, и написано было по-еврейски, по-гречески, по-римски.
\\
При кресте Иисуса стояли Матерь Его и сестра Матери Его, Мария Клеопова, и Мария Магдалина.
\\
Иисус, увидев Матерь и ученика тут стоящего, которого любил, говорит Матери Своей: Жено! се, сын Твой.
\\
Потом говорит ученику: се, Матерь твоя! И с этого времени ученик сей взял Ее к себе.
\\
После того Иисус, зная, что уже все совершилось, да сбудется Писание, говорит: жажду.
\\
Когда же Иисус вкусил уксуса, сказал: совершилось! И, преклонив главу, предал дух.
\\
Но так как тогда была пятница, то Иудеи, дабы не оставить тел на кресте в субботу,- ибо та суббота была день великий,- просили Пилата, чтобы перебить у них голени и снять их.
\\
Итак пришли воины, и у первого перебили голени, и у другого, распятого с Ним.
\\
Но, придя к Иисусу, как увидели Его уже умершим, не перебили у Него голеней,
\\
но один из воинов копьем пронзил Ему ребра, и тотчас истекла кровь и вода.
\\
И видевший засвидетельствовал, и истинно свидетельство его; он знает, что говорит истину, дабы вы поверили.
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.49\textwidth}

\textbf{John 19:6--19:11, 19:13--19:20, 19:25--19:28, 19:30--19:35.}\\
When the chief priests therefore and officers saw him, they cried out, saying, Crucify him, crucify him. Pilate saith unto them, Take ye him, and crucify him: for I find no fault in him.\\
The Jews answered him, We have a law, and by our law he ought to die, because he made himself the Son of God.\\
When Pilate therefore heard that saying, he was the more afraid;\\
And went again into the judgment hall, and saith unto Jesus, Whence art thou? But Jesus gave him no answer.\\
Then saith Pilate unto him, Speakest thou not unto me? knowest thou not that I have power to crucify thee, and have power to release thee?\\
Jesus answered, Thou couldest have no power at all against me, except it were given thee from above: therefore he that delivered me unto thee hath the greater sin.\\
When Pilate therefore heard that saying, he brought Jesus forth, and sat down in the judgment seat in a place that is called the Pavement, but in the Hebrew, Gabbatha.\\
And it was the preparation of the passover, and about the sixth hour: and he saith unto the Jews, Behold your King!\\
But they cried out, Away with him, away with him, crucify him. Pilate saith unto them, Shall I crucify your King? The chief priests answered, We have no king but Caesar.\\
Then delivered he him therefore unto them to be crucified. And they took Jesus, and led him away.\\
And he bearing his cross went forth into a place called the place of a skull, which is called in the Hebrew Golgotha:\\
Where they crucified him, and two other with him, on either side one, and Jesus in the midst.\\
And Pilate wrote a title, and put it on the cross. And the writing was, JESUS OF NAZARETH THE KING OF THE JEWS.\\
This title then read many of the Jews: for the place where Jesus was crucified was nigh to the city: and it was written in Hebrew, and Greek, and Latin.\\
Now there stood by the cross of Jesus his mother, and his mother's sister, Mary the wife of Cleophas, and Mary Magdalene.\\
When Jesus therefore saw his mother, and the disciple standing by, whom he loved, he saith unto his mother, Woman, behold thy son!\\
Then saith he to the disciple, Behold thy mother! And from that hour that disciple took her unto his own home.\\
After this, Jesus knowing that all things were now accomplished, that the scripture might be fulfilled, saith, I thirst.\\
When Jesus therefore had received the vinegar, he said, It is finished: and he bowed his head, and gave up the ghost.\\
The Jews therefore, because it was the preparation, that the bodies should not remain upon the cross on the sabbath day, (for that sabbath day was an high day,) besought Pilate that their legs might be broken, and that they might be taken away.\\
Then came the soldiers, and brake the legs of the first, and of the other which was crucified with him.\\
But when they came to Jesus, and saw that he was dead already, they brake not his legs:\\
But one of the soldiers with a spear pierced his side, and forthwith came there out blood and water.\\
And he that saw it bare record, and his record is true: and he knoweth that he saith true, that ye might believe.
\end{minipage}}
\vspace*{\fill}
\newpage
\Large%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{約翰福音 19:6--19:11, 19:13--19:20, 19:25--19:28, 19:30--19:35.}\\
祭司長和差役看見他、就喊著說、釘他十字架、釘他十字架。彼拉多說、你們自己把他釘十字架罷．我查不出他有甚麼罪來。\\
猶太人回答說、我們有律法、按那律法、他是該死的、因他以自己為　神的兒子。\\
彼拉多聽見這話、越發害怕。\\
又進衙門、對耶穌說、你是那裡來的．耶穌卻不回答。\\
彼拉多說、你不對我說話麼．你豈不知我有權柄釋放你、也有權柄把你釘十字架麼。\\
耶穌回答說、若不是從上頭賜給你的、你就毫無權柄辦我．所以把我交給你的那人、罪更重了。\\
彼拉多聽見這話、就帶耶穌出來、到了一個地方、名叫鋪華石處、希伯來話叫厄巴大、就在那裡坐堂。\\
那日是預備逾越節的日子、約有午正。彼拉多對猶太人說、看哪、這是你們的王。\\
他們喊著說、除掉他、除掉他、釘他在十字架上。彼拉多說、我可以把你們的王釘十字架麼。祭司長回答說、除了該撒、我們沒有王。\\
於是彼拉多將耶穌交給他們去釘十字架。\\
他們就把耶穌帶了去．耶穌背著自己的十字架出來、到了一個地方、名叫髑髏地、希伯來話叫各各他。\\
他們就在那裡釘他在十字架上、還有兩個人和他一同釘著、一邊一個、耶穌在中間。\\
彼拉多又用牌子寫了一個名號、安在十字架上．寫的是猶太人的王、拿撒勒人耶穌。\\
有許多猶太人念這名號．因為耶穌被釘十字架的地方、與城相近、並且是用希伯來、羅馬、希利尼、三樣文字寫的。\\
站在耶穌十字架旁邊的、有他母親、與他母親的姊妹、並革羅罷的妻子馬利亞、和抹大拉的馬利亞。\\
耶穌見母親和他所愛的那門徒站在旁邊、就對他母親說、母親、〔原文作婦人〕看你的兒子。\\
又對那門徒說、看你的母親。從此那門徒就接他到自己家裡去了。\\
這事以後、耶穌知道各樣的事已經成了、為要使經上的話應驗、就說、我渴了。\\
耶穌嘗〔原文作受〕了那醋、就說、成了．便低下頭、將靈魂交付　神了。\\
猶太人因這日是預備日、又因那安息日是個大日、就求彼拉多叫人打斷他們的腿、把他們拿去、免得屍首當安息日留在十字架上。\\
於是兵丁來、把頭一個人的腿、並與耶穌同釘第二個人的腿、都打斷了。\\
只是來到耶穌那裡、見他已經死了、就不打斷他的腿。\\
惟有一個兵拿槍扎他的肋旁、隨即有血和水流出來。\\
看見這事的那人就作見證、他的見證也是真的、並且他知道自己所說的是真的、叫你們也可以信。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
