\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[margin=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 1 of the Great Lent\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Ин., 5 зач., I, 43-51.}\\
На другой день Иисус восхотел идти в Галилею, и находит Филиппа и говорит ему: иди за Мною.\\
Филипп же был из Вифсаиды, из одного города с Андреем и Петром.\\
Филипп находит Нафанаила и говорит ему: мы нашли Того, о Котором писали Моисей в законе и пророки, Иисуса, сына Иосифова, из Назарета.\\
Но Нафанаил сказал ему: из Назарета может ли быть что доброе? Филипп говорит ему: пойди и посмотри.\\
Иисус, увидев идущего к Нему Нафанаила, говорит о нем: вот подлинно Израильтянин, в котором нет лукавства.\\
Нафанаил говорит Ему: почему Ты знаешь меня? Иисус сказал ему в ответ: прежде нежели позвал тебя Филипп, когда ты был под смоковницею, Я видел тебя.\\
Нафанаил отвечал Ему: Равви́! Ты Сын Божий, Ты Царь Израилев.\\
Иисус сказал ему в ответ: ты веришь, потому что Я тебе сказал: Я видел тебя под смоковницею; увидишь больше сего.\\
И говорит ему: истинно, истинно говорю вам: отныне будете видеть небо отверстым и Ангелов Божиих восходящих и нисходящих к Сыну Человеческому. \\
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{John 1:43--1:51.}\\
The day following Jesus would go forth into Galilee, and findeth Philip, and saith unto him, Follow me.\\
Now Philip was of Bethsaida, the city of Andrew and Peter.\\
Philip findeth Nathanael, and saith unto him, We have found him, of whom Moses in the law, and the prophets, did write, Jesus of Nazareth, the son of Joseph.\\
And Nathanael said unto him, Can there any good thing come out of Nazareth? Philip saith unto him, Come and see.\\
Jesus saw Nathanael coming to him, and saith of him, Behold an Israelite indeed, in whom is no guile!\\
Nathanael saith unto him, Whence knowest thou me? Jesus answered and said unto him, Before that Philip called thee, when thou wast under the fig tree, I saw thee.\\
Nathanael answered and saith unto him, Rabbi, thou art the Son of God; thou art the King of Israel.\\
Jesus answered and said unto him, Because I said unto thee, I saw thee under the fig tree, believest thou? thou shalt see greater things than these.\\
And he saith unto him, Verily, verily, I say unto you, Hereafter ye shall see heaven open, and the angels of God ascending and descending upon the Son of man.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.7}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{約翰福音 1:43--1:51.}\\
又次日、耶穌想要往加利利去、遇見腓力、就對他說、來跟從我罷。\\
這腓力是伯賽大人、和安得烈、彼得同城。\\
腓力找著拿但業、對他說、摩西在律法上所寫的、和眾先知所記的那一位、我們遇見了、就是約瑟的兒子拿撒勒人耶穌。\\
拿但業對他說、拿撒勒還能出甚麼好的麼。腓力說、你來看。\\
耶穌看見拿但業來、就指著他說、看哪、這是個真以色列人、他心裡是沒有詭詐的。\\
拿但業對耶穌說、你從那裡知道我呢。耶穌回答說、腓力還沒有招呼你、你在無花果樹底下、我就看見你了。\\
拿但業說、拉比、你是　神的兒子、你是以色列的王。\\
耶穌對他說、因為我說在無花果樹底下看見你、你就信麼．你將要看見比這更大的事。\\
又說、我實實在在的告訴你們、你們將要看見天開了、　神的使者上去下來在人子身上。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
