%simple
\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.3in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{\vspace{-3ex}Divine Liturgy\\Reading from The Gospels}
\author{Week 29 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 4 зач., II, 13-23.}\\
Когда же они отошли,- се, Ангел Господень является во сне Иосифу и говорит: встань, возьми Младенца и Матерь Его и беги в Египет, и будь там, доколе не скажу тебе, ибо Ирод хочет искать Младенца, чтобы погубить Его.
\\
Он встал, взял Младенца и Матерь Его ночью и пошел в Египет,
\\
и там был до смерти Ирода, да сбудется реченное Господом через пророка, который говорит: из Египта воззвал Я Сына Моего.
\\
Тогда Ирод, увидев себя осмеянным волхвами, весьма разгневался, и послал избить всех младенцев в Вифлееме и во всех пределах его, от двух лет и ниже, по времени, которое выведал от волхвов.
\\
Тогда сбылось реченное через пророка Иеремию, который говорит:
\\
глас в Раме слышен, плач и рыдание и вопль великий; Рахиль плачет о детях своих и не хочет утешиться, ибо их нет.
\\
По смерти же Ирода,- се, Ангел Господень во сне является Иосифу в Египте
\\
и говорит: встань, возьми Младенца и Матерь Его и иди в землю Израилеву, ибо умерли искавшие души Младенца.
\\
Он встал, взял Младенца и Матерь Его и пришел в землю Израилеву.
\\
Услышав же, что Архелай царствует в Иудее вместо Ирода, отца своего, убоялся туда идти; но, получив во сне откровение, пошел в пределы Галилейские
\\
и, придя, поселился в городе, называемом Назарет, да сбудется реченное через пророков, что Он Назореем наречется.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 2:13--2:23.}\\
And when they were departed, behold, the angel of the Lord appeareth to Joseph in a dream, saying, Arise, and take the young child and his mother, and flee into Egypt, and be thou there until I bring thee word: for Herod will seek the young child to destroy him.\\
When he arose, he took the young child and his mother by night, and departed into Egypt:\\
And was there until the death of Herod: that it might be fulfilled which was spoken of the Lord by the prophet, saying, Out of Egypt have I called my son.\\
Then Herod, when he saw that he was mocked of the wise men, was exceeding wroth, and sent forth, and slew all the children that were in Bethlehem, and in all the coasts thereof, from two years old and under, according to the time which he had diligently enquired of the wise men.\\
Then was fulfilled that which was spoken by Jeremy the prophet, saying,\\
In Rama was there a voice heard, lamentation, and weeping, and great mourning, Rachel weeping for her children, and would not be comforted, because they are not.\\
But when Herod was dead, behold, an angel of the Lord appeareth in a dream to Joseph in Egypt,\\
Saying, Arise, and take the young child and his mother, and go into the land of Israel: for they are dead which sought the young child's life.\\
And he arose, and took the young child and his mother, and came into the land of Israel.\\
But when he heard that Archelaus did reign in Judaea in the room of his father Herod, he was afraid to go thither: notwithstanding, being warned of God in a dream, he turned aside into the parts of Galilee:\\
And he came and dwelt in a city called Nazareth: that it might be fulfilled which was spoken by the prophets, He shall be called a Nazarene.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 2:13--2:23.}\\
他們去後、有主的使者向約瑟夢中顯現、說、起來、帶著小孩子同他母親、逃往埃及、住在那裡、等我吩咐你．因為希律必尋找小孩子要除滅他。\\
約瑟就起來、夜間帶著小孩子和他母親往埃及去．\\
住在那裡、直到希律死了．這是要應驗主藉先知所說的話、說、『我從埃及召出我的兒子來。』\\
希律見自己被博士愚弄、就大大發怒、差人將伯利恆城裡、並四境所有的男孩、照著他向博士仔細查問的時候、凡兩歲以裡的、都殺盡了。\\
這就應了先知耶利米的話、說、\\
『在拉瑪聽見號咷大哭的聲音、是拉結哭他兒女、不肯受安慰、因為他們都不在了。』\\
希律死了以後、有主的使者、在埃及向約瑟夢中顯現、說、\\
起來、帶著小孩子和他母親往以色列地去．因為要害小孩子性命的人已經死了。\\
約瑟就起來、把小孩子和他母親帶到以色列地去。\\
只因聽見亞基老接著他父親希律作了猶太王、就怕往那裡去．又在夢中被主指示、便往加利利境內去了。\\
到了一座城、名叫拿撒勒、就住在那裡．這是要應驗先知所說、他將稱為拿撒勒人的話了。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
