\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 19 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\LARGE%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 30 зач., VII, 11-16.}\\
После сего Иисус пошел в город, называемый Наин; и с Ним шли многие из учеников Его и множество народа.
\\
Когда же Он приблизился к городским воротам, тут выносили умершего, единственного сына у матери, а она была вдова; и много народа шло с нею из города.
\\
Увидев ее, Господь сжалился над нею и сказал ей: не плачь.
\\
И, подойдя, прикоснулся к одру; несшие остановились, и Он сказал: юноша! тебе говорю, встань!
\\
Мертвый, поднявшись, сел и стал говорить; и отдал его Иисус матери его.
\\
И всех объял страх, и славили Бога, говоря: великий пророк восстал между нами, и Бог посетил народ Свой.
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 7:11--7:16.}\\
And it came to pass the day after, that he went into a city called Nain; and many of his disciples went with him, and much people.\\
Now when he came nigh to the gate of the city, behold, there was a dead man carried out, the only son of his mother, and she was a widow: and much people of the city was with her.\\
And when the Lord saw her, he had compassion on her, and said unto her, Weep not.\\
And he came and touched the bier: and they that bare him stood still. And he said, Young man, I say unto thee, Arise.\\
And he that was dead sat up, and began to speak. And he delivered him to his mother.\\
And there came a fear on all: and they glorified God, saying, That a great prophet is risen up among us; and, That God hath visited his people.
\end{minipage}}
\vspace*{\fill}
\newpage
%\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\fontsize{35}{42}\selectfont
\textbf{路加福音 7:11--7:16.}\\
過了不多時、〔有古卷作次日〕耶穌往一座城去、這城名叫拿因、他的門徒和極多的人與他同行。\\
將近城門、有一個死人被抬出來．這人是他母親獨生的兒子、他母親又是寡婦．有城裡的許多人同著寡婦送殯。\\
主看見那寡婦就憐憫他、對他說、不要哭。\\
於是進前按著杠、抬的人就站住了。耶穌說、少年人、我吩咐你起來。\\
那死人就坐起、並且說話．耶穌便把他交給他母親。\\
眾人都驚奇、歸榮耀與　神說、有大先知在我們中間興起來了．又說、神眷顧了他的百姓。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
