\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.2in,bottom=0.2in,left=0.3in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\def\HUGE{ \font\Tinyfont = cmr10 at 10pt \relax  \Tinyfont}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 14 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 13 зач., IV, 16-22.}\\
И пришел в Назарет, где был воспитан, и вошел, по обыкновению Своему, в день субботний в синагогу, и встал читать.
\\
Ему подали книгу пророка Исаии; и Он, раскрыв книгу, нашел место, где было написано:
\\
Дух Господень на Мне; ибо Он помазал Меня благовествовать нищим, и послал Меня исцелять сокрушенных сердцем, проповедовать пленным освобождение, слепым прозрение, отпустить измученных на свободу,
\\
проповедовать лето Господне благоприятное.
\\
И, закрыв книгу и отдав служителю, сел; и глаза всех в синагоге были устремлены на Него.
\\
И Он начал говорить им: ныне исполнилось писание сие, слышанное вами.
\\
И все засвидетельствовали Ему это, и дивились словам благодати, исходившим из уст Его, и говорили: не Иосифов ли это сын?
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 4:16--4:22.}\\
And he came to Nazareth, where he had been brought up: and, as his custom was, he went into the synagogue on the sabbath day, and stood up for to read.\\
And there was delivered unto him the book of the prophet Esaias. And when he had opened the book, he found the place where it was written,\\
The Spirit of the Lord is upon me, because he hath anointed me to preach the gospel to the poor; he hath sent me to heal the brokenhearted, to preach deliverance to the captives, and recovering of sight to the blind, to set at liberty them that are bruised,\\
To preach the acceptable year of the Lord.\\
And he closed the book, and he gave it again to the minister, and sat down. And the eyes of all them that were in the synagogue were fastened on him.\\
And he began to say unto them, This day is this scripture fulfilled in your ears.\\
And all bare him witness, and wondered at the gracious words which proceeded out of his mouth. And they said, Is not this Joseph's son?\\

\end{minipage}}
\vspace*{\fill}
\newpage
\vspace*{\fill}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\begin{spacing}{1.2}
\fontsize{30}{35}\selectfont
\textbf{路加福音 4:16--4:22.}\\
耶穌來到拿撒勒、就是他長大的地方．在安息日、照他平常的規矩、進了會堂、站起來要念聖經。\\
有人把先知以賽亞的書交給他、他就打開、找到一處寫著說、\\
『主的靈在我身上、因為他用膏膏我、叫我傳福音給貧窮的人．差遣我報告被擄的得釋放、瞎眼的得看見、叫那受壓制的得自由、\\
報告　神悅納人的禧年。』\\
於是把書捲起來、交還執事、就坐下．會堂裡的人都定睛看他。\\
耶穌對他們說、今天這經應驗在你們耳中了。\\
眾人都稱讚他、並希奇他口中所出的恩言．又說、這不是約瑟的兒子麼。
\end{spacing}
\end{CJK}
\end{minipage}}
\vspace*{\fill}
\end{document}
