\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 2 after the Pentecost (memorial reading)\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\onehalfspacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 10 зач., IV, 25 - V, 12.}\\
И следовало за Ним множество народа из Галилеи и Десятиградия, и Иерусалима, и Иудеи, и из-за Иордана.
\\
Увидев народ, Он взошел на гору; и, когда сел, приступили к Нему ученики Его.
\\
И Он, отверзши уста Свои, учил их, говоря:
\\
Блаженны нищие духом, ибо их есть Царство Небесное.
\\
Блаженны плачущие, ибо они утешатся.
\\
Блаженны кроткие, ибо они наследуют землю.
\\
Блаженны алчущие и жаждущие правды, ибо они насытятся.
\\
Блаженны милостивые, ибо они помилованы будут.
\\
Блаженны чистые сердцем, ибо они Бога узрят.
\\
Блаженны миротворцы, ибо они будут наречены сынами Божиими.
\\
Блаженны изгнанные за правду, ибо их есть Царство Небесное.
\\
Блаженны вы, когда будут поносить вас и гнать и всячески неправедно злословить за Меня.
\\
Радуйтесь и веселитесь, ибо велика ваша награда на небесах: так гнали и пророков, бывших прежде вас.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 4:25--5:12.}\\
And there followed him great multitudes of people from Galilee, and from Decapolis, and from Jerusalem, and from Judaea, and from beyond Jordan.\\
And seeing the multitudes, he went up into a mountain: and when he was set, his disciples came unto him:\\
And he opened his mouth, and taught them, saying,\\
Blessed are the poor in spirit: for theirs is the kingdom of heaven.\\
Blessed are they that mourn: for they shall be comforted.\\
Blessed are the meek: for they shall inherit the earth.\\
Blessed are they which do hunger and thirst after righteousness: for they shall be filled.\\
Blessed are the merciful: for they shall obtain mercy.\\
Blessed are the pure in heart: for they shall see God.\\
Blessed are the peacemakers: for they shall be called the children of God.\\
Blessed are they which are persecuted for righteousness' sake: for theirs is the kingdom of heaven.\\
Blessed are ye, when men shall revile you, and persecute you, and shall say all manner of evil against you falsely, for my sake.\\
Rejoice, and be exceeding glad: for great is your reward in heaven: for so persecuted they the prophets which were before you.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.1}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 4:25--5:12.}\\
當下、有許多人從加利利、低加波利、耶路撒冷、猶太、約但河外、來跟著他。\\
耶穌看見這許多的人、就上了山、既已坐下、門徒到他跟前來。\\
他就開口教訓他們說、\\
虛心的人有福了．因為天國是他們的。\\
哀慟的人有福了．因為他們必得安慰。\\
溫柔的人有福了．因為他們必承受地土。\\
飢渴慕義的人有福了．因為他們必得飽足。\\
憐恤人的人有福了．因為他們必蒙憐恤。\\
清心的人有福了．因為他們必得見　神。\\
使人和睦的人有福了．因為他們必稱為　神的兒子。\\
為義受逼迫的人有福了．因為天國是他們的。\\
人若因我辱罵你們、逼迫你們、捏造各樣壞話毀謗你們、你們就有福了。\\
應當歡喜快樂．因為你們在天上的賞賜是大的．在你們以前的先知、人也是這樣逼迫他們。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
