\documentclass[14pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 25 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 66 зач., XII, 16-21.}\\
И сказал им притчу: у одного богатого человека был хороший урожай в поле;
\\
и он рассуждал сам с собою: что мне делать? некуда мне собрать плодов моих?
\\
И сказал: вот что сделаю: сломаю житницы мои и построю большие, и соберу туда весь хлеб мой и всё добро мое,
\\
и скажу душе моей: душа! много добра лежит у тебя на многие годы: покойся, ешь, пей, веселись.
\\
Но Бог сказал ему: безумный! в сию ночь душу твою возьмут у тебя; кому же достанется то, что ты заготовил?
\\
Так бывает с тем, кто собирает сокровища для себя, а не в Бога богатеет.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 12:16--12:21.}\\
And he spake a parable unto them, saying, The ground of a certain rich man brought forth plentifully:\\
And he thought within himself, saying, What shall I do, because I have no room where to bestow my fruits?\\
And he said, This will I do: I will pull down my barns, and build greater; and there will I bestow all my fruits and my goods.\\
And I will say to my soul, Soul, thou hast much goods laid up for many years; take thine ease, eat, drink, and be merry.\\
But God said unto him, Thou fool, this night thy soul shall be required of thee: then whose shall those things be, which thou hast provided?\\
So is he that layeth up treasure for himself, and is not rich toward God.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.3}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 12:16--12:21.}\\
就用比喻對他們說、有一個財主、田產豐盛．\\
自己心裡思想說、我的出產沒有地方收藏、怎麼辦呢。\\
又說、我要這麼辦．要把我的倉房拆了、另蓋更大的．在那裡好收藏我一切的糧食和財物。\\
然後要對我的靈魂說、靈魂哪、你有許多財物積存、可作多年的費用．只管安安逸逸的喫喝快樂罷。\\
　神卻對他說、無知的人哪、今夜必要你的靈魂．你所預備的、要歸誰呢。\\
凡為自己積財、在　神面前卻不富足的、也是這樣。
\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
