27

\singlespacing %\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus

\singlespacing %for chinese

\Large

Лк., 76 зач., XIV, 16-24.

Luke 14:16 -- 14:24.

路加福音 14:16 -- 14:24.

Он же сказал ему: один человек сделал большой ужин и звал многих,
и когда наступило время ужина, послал раба своего сказать званым: идите, ибо уже всё готово.
И начали все, как бы сговорившись, извиняться. Первый сказал ему: я купил землю и мне нужно пойти посмотреть ее; прошу тебя, извини меня.
Другой сказал: я купил пять пар волов и иду испытать их; прошу тебя, извини меня.
Третий сказал: я женился и потому не могу прийти.
И, возвратившись, раб тот донес о сем господину своему. Тогда, разгневавшись, хозяин дома сказал рабу своему: пойди скорее по улицам и переулкам города и приведи сюда нищих, увечных, хромых и слепых.
И сказал раб: господин! исполнено, как приказал ты, и еще есть место.
Господин сказал рабу: пойди по дорогам и изгородям и убеди прийти, чтобы наполнился дом мой.
Ибо сказываю вам, что никто из тех званых не вкусит моего ужина, ибо много званых, но мало избранных.

Then said he unto him, A certain man made a great supper, and bade many:
And sent his servant at supper time to say to them that were bidden, Come; for all things are now ready.
And they all with one consent began to make excuse. The first said unto him, I have bought a piece of ground, and I must needs go and see it: I pray thee have me excused.
And another said, I have bought five yoke of oxen, and I go to prove them: I pray thee have me excused.
And another said, I have married a wife, and therefore I cannot come.
So that servant came, and shewed his lord these things. Then the master of the house being angry said to his servant, Go out quickly into the streets and lanes of the city, and bring in hither the poor, and the maimed, and the halt, and the blind.
And the servant said, Lord, it is done as thou hast commanded, and yet there is room.
And the lord said unto the servant, Go out into the highways and hedges, and compel them to come in, that my house may be filled.
For I say unto you, That none of those men which were bidden shall taste of my supper.

耶穌對他說：「有人擺設大宴席，請了許多客人。
到了坐席的時候，他打發僕人去對所請的人說：『請來吧！樣樣都已齊備了。』
眾人異口同聲地推辭。頭一個對他說：『我買了一塊地，必須去看看。請你准我辭了。』
另一個說：『我買了五對牛，要去試一試。請你准我辭了。』
又有一個說：『我才娶了妻子，所以不能去。』
那僕人回來，把這些事都告訴了主人。這家的主人就發怒，對僕人說：『快出去，到城裏大街小巷，領那貧窮的、殘疾的、失明的、瘸腿的來。』
僕人說：『主啊，你所吩咐的已經辦了，還有空位。』
主人對僕人說：『你出去，到大街小巷強拉人進來，坐滿我的屋子。
我告訴你們，先前所請的人沒有一個可以嘗到我的宴席。』」 
