\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 15 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\LARGE%for eng/rus
\onehalfspacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Ин., 9 зач., III, 13-17.}\\
Никто не восходил на небо, как только сшедший с небес Сын Человеческий, сущий на небесах.
\\
И как Моисей вознес змию в пустыне, так должно вознесену быть Сыну Человеческому,
\\
дабы всякий, верующий в Него, не погиб, но имел жизнь вечную.
\\
Ибо так возлюбил Бог мир, что отдал Сына Своего Единородного, дабы всякий верующий в Него, не погиб, но имел жизнь вечную.
\\
Ибо не послал Бог Сына Своего в мир, чтобы судить мир, но чтобы мир спасен был чрез Него.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{John 3:13--3:17.}\\
And no man hath ascended up to heaven, but he that came down from heaven, even the Son of man which is in heaven.\\
And as Moses lifted up the serpent in the wilderness, even so must the Son of man be lifted up:\\
That whosoever believeth in him should not perish, but have eternal life.\\
For God so loved the world, that he gave his only begotten Son, that whosoever believeth in him should not perish, but have everlasting life.\\
For God sent not his Son into the world to condemn the world; but that the world through him might be saved.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\begin{spacing}{1.2}
\fontsize{30}{35}\selectfont
\textbf{約翰福音 3:13--3:17.}\\
除了從天降下仍舊在天的人子、沒有人升過天。\\
摩西在曠野怎樣舉蛇、人子也必照樣被舉起來．\\
叫一切信他的都得永生。〔或作叫一切信的人在他裡面得永生〕\\
　神愛世人、甚至將他的獨生子賜給他們、叫一切信他的、不至滅亡、反得永生。\\
因為　神差他的兒子降世、不是要定世人的罪、〔或作審判世人下同〕乃是要叫世人因他得救。
\end{spacing}
\end{CJK}
\end{minipage}}
\vspace*{\fill}
\end{document}
