\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.2in,bottom=0.2in,left=0in,right=0.4in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 25 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 39 зач., VIII, 41-56.}\\
И вот, пришел человек, именем Иаир, который был начальником синагоги; и, пав к ногам Иисуса, просил Его войти к нему в дом,
\\
потому что у него была одна дочь, лет двенадцати, и та была при смерти. Когда же Он шел, народ теснил Его.
\\
И женщина, страдавшая кровотечением двенадцать лет, которая, издержав на врачей всё имение, ни одним не могла быть вылечена,
\\
подойдя сзади, коснулась края одежды Его; и тотчас течение крови у ней остановилось.
\\
И сказал Иисус: кто прикоснулся ко Мне? Когда же все отрицались, Петр сказал и бывшие с Ним: Наставник! народ окружает Тебя и теснит,- и Ты говоришь: кто прикоснулся ко Мне?
\\
Но Иисус сказал: прикоснулся ко Мне некто, ибо Я чувствовал силу, исшедшую из Меня.
\\
Женщина, видя, что она не утаилась, с трепетом подошла и, пав пред Ним, объявила Ему перед всем народом, по какой причине прикоснулась к Нему и как тотчас исцелилась.
\\
Он сказал ей: дерзай, дщерь! вера твоя спасла тебя; иди с миром.
\\
Когда Он еще говорил это, приходит некто из дома начальника синагоги и говорит ему: дочь твоя умерла; не утруждай Учителя.
\\
Но Иисус, услышав это, сказал ему: не бойся, только веруй, и спасена будет.
\\
Придя же в дом, не позволил войти никому, кроме Петра, Иоанна и Иакова, и отца девицы, и матери.
\\
Все плакали и рыдали о ней. Но Он сказал: не плачьте; она не умерла, но спит.
\\
И смеялись над Ним, зная, что она умерла.
\\
Он же, выслав всех вон и взяв ее за руку, возгласил: девица! встань.
\\
И возвратился дух ее; она тотчас встала, и Он велел дать ей есть.
\\
И удивились родители ее. Он же повелел им не сказывать никому о происшедшем.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 8:41--8:56.}\\
And, behold, there came a man named Jairus, and he was a ruler of the synagogue: and he fell down at Jesus' feet, and besought him that he would come into his house:\\
For he had one only daughter, about twelve years of age, and she lay a dying. But as he went the people thronged him.\\
And a woman having an issue of blood twelve years, which had spent all her living upon physicians, neither could be healed of any,\\
Came behind him, and touched the border of his garment: and immediately her issue of blood stanched.\\
And Jesus said, Who touched me? When all denied, Peter and they that were with him said, Master, the multitude throng thee and press thee, and sayest thou, Who touched me?\\
And Jesus said, Somebody hath touched me: for I perceive that virtue is gone out of me.\\
And when the woman saw that she was not hid, she came trembling, and falling down before him, she declared unto him before all the people for what cause she had touched him, and how she was healed immediately.\\
And he said unto her, Daughter, be of good comfort: thy faith hath made thee whole; go in peace.\\
While he yet spake, there cometh one from the ruler of the synagogue's house, saying to him, Thy daughter is dead; trouble not the Master.\\
But when Jesus heard it, he answered him, saying, Fear not: believe only, and she shall be made whole.\\
And when he came into the house, he suffered no man to go in, save Peter, and James, and John, and the father and the mother of the maiden.\\
And all wept, and bewailed her: but he said, Weep not; she is not dead, but sleepeth.\\
And they laughed him to scorn, knowing that she was dead.\\
And he put them all out, and took her by the hand, and called, saying, Maid, arise.\\
And her spirit came again, and she arose straightway: and he commanded to give her meat.\\
And her parents were astonished: but he charged them that they should tell no man what was done.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 8:41--8:56.}\\
有一個管會堂的、名叫睚魯、來俯伏在耶穌腳前、求耶穌到他家裡去．\\
因他有一個獨生女兒、約有十二歲、快要死了。耶穌去的時候、眾人擁擠他。\\
有一個女人、患了十二年的血漏、在醫生手裡花盡了他一切養生的、並沒有一人能醫好他．\\
他來到耶穌背後、摸他的衣裳繸子、血漏立刻就止住了。\\
耶穌說、摸我的是誰．眾人都不承認、彼得和同行的人都說、夫子、眾人擁擁擠擠緊靠著你。〔有古卷在此有你還問摸我的是誰麼〕\\
耶穌說、總有人摸我．因我覺得有能力從我身上出去。\\
那女人知道不能隱藏、就戰戰兢兢的來俯伏在耶穌腳前、把摸他的緣故、和怎樣立刻得好了、當著眾人都說出來。\\
耶穌對他說、女兒、你的信救了你、平平安安的去罷。\\
還說話的時候、有人從管會堂的家裡來說、你的女兒死了、不要勞動夫子。\\
耶穌聽見就對他說、不要怕、只要信、你的女兒就必得救。\\
耶穌到了他的家、除了彼得、約翰、雅各、和女兒的父母、不許別人同他進去。\\
眾人都為這女兒哀哭捶胸。耶穌說、不要哭．他不是死了、是睡著了。\\
他們曉得女兒已經死了、就嗤笑耶穌。\\
耶穌拉著他的手、呼叫說、女兒、起來罷。\\
他的靈魂便回來、他就立刻起來了．耶穌吩咐給他東西喫。\\
他的父母驚奇得很．耶穌囑咐他們、不要把所作的事告訴人。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
