%simple
\documentclass[14pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage{extsizes}
\usepackage[top=0.3in,bottom=0.3in,left=0.3in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\usepackage{extsizes}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 2 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 9 зач., IV, 18-23.}\\
Проходя же близ моря Галилейского, Он увидел двух братьев: Симона, называемого Петром, и Андрея, брата его, закидывающих сети в море, ибо они были рыболовы,
\\
и говорит им: идите за Мною, и Я сделаю вас ловцами человеков.
\\
И они тотчас, оставив сети, последовали за Ним.
\\
Оттуда, идя далее, увидел Он других двух братьев, Иакова Зеведеева и Иоанна, брата его, в лодке с Зеведеем, отцом их, починивающих сети свои, и призвал их.
\\
И они тотчас, оставив лодку и отца своего, последовали за Ним.
\\
И ходил Иисус по всей Галилее, уча в синагогах их и проповедуя Евангелие Царствия, и исцеляя всякую болезнь и всякую немощь в людях.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 4:18--4:23.}\\
And Jesus, walking by the sea of Galilee, saw two brethren, Simon called Peter, and Andrew his brother, casting a net into the sea: for they were fishers.\\
And he saith unto them, Follow me, and I will make you fishers of men.\\
And they straightway left their nets, and followed him.\\
And going on from thence, he saw other two brethren, James the son of Zebedee, and John his brother, in a ship with Zebedee their father, mending their nets; and he called them.\\
And they immediately left the ship and their father, and followed him.\\
And Jesus went about all Galilee, teaching in their synagogues, and preaching the gospel of the kingdom, and healing all manner of sickness and all manner of disease among the people.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 4:18--4:23.}\\
耶穌在加利利海邊行走、看見弟兄二人、就是那稱呼彼得的西門、和他兄弟安得烈、在海裡撒網．他們本是打魚的。\\
耶穌對他們說、來跟從我、我要叫你們得人如得魚一樣。\\
他們就立刻捨了網、跟從了他。\\
從那裡往前走、又看見弟兄二人、就是西庇太的兒子雅各、和他兄弟約翰、同他們的父親西庇太在船上補網．耶穌就招呼他們。\\
他們立刻捨了船、別了父親、跟從了耶穌。\\
耶穌走遍加利利、在各會堂裡教訓人、傳天國的福音、醫治百姓各樣的病症。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
