\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 7 after the Pentecost\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\Large%for eng/rus
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мф., 33 зач., IX, 27-35.}\\
Когда Иисус шел оттуда, за Ним следовали двое слепых и кричали: помилуй нас, Иисус, сын Давидов!
\\
Когда же Он пришел в дом, слепые приступили к Нему. И говорит им Иисус: веруете ли, что Я могу это сделать? Они говорят Ему: ей, Господи!
\\
Тогда Он коснулся глаз их и сказал: по вере вашей да будет вам.
\\
И открылись глаза их; и Иисус строго сказал им: смотрите, чтобы никто не узнал.
\\
А они, выйдя, разгласили о Нем по всей земле той.
\\
Когда же те выходили, то привели к Нему человека немого бесноватого.
\\
И когда бес был изгнан, немой стал говорить. И народ, удивляясь, говорил: никогда не бывало такого явления в Израиле.
\\
А фарисеи говорили: Он изгоняет бесов силою князя бесовского.
\\
И ходил Иисус по всем городам и селениям, уча в синагогах их, проповедуя Евангелие Царствия и исцеляя всякую болезнь и всякую немощь в людях.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Matthew 9:27--9:35.}\\
And when Jesus departed thence, two blind men followed him, crying, and saying, Thou Son of David, have mercy on us.\\
And when he was come into the house, the blind men came to him: and Jesus saith unto them, Believe ye that I am able to do this? They said unto him, Yea, Lord.\\
Then touched he their eyes, saying, According to your faith be it unto you.\\
And their eyes were opened; and Jesus straitly charged them, saying, See that no man know it.\\
But they, when they were departed, spread abroad his fame in all that country.\\
As they went out, behold, they brought to him a dumb man possessed with a devil.\\
And when the devil was cast out, the dumb spake: and the multitudes marvelled, saying, It was never so seen in Israel.\\
But the Pharisees said, He casteth out devils through the prince of the devils.\\
And Jesus went about all the cities and villages, teaching in their synagogues, and preaching the gospel of the kingdom, and healing every sickness and every disease among the people.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.25}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬太福音 9:27--9:35.}\\
耶穌從那裡往前走、有兩個瞎子跟著他、喊叫說、大衛的子孫、可憐我們罷。\\
耶穌進了房子、瞎子就來到他跟前．耶穌說、你們信我能作這事麼．他們說、主阿、我們信。\\
耶穌就摸他們的眼睛、說、照著你們的信給你們成全了罷。\\
他們的眼睛就開了。耶穌切切的囑咐他們說、你們要小心、不可叫人知道。\\
他們出去、竟把他的名聲傳遍了那地方。\\
他們出去的時候、有人將鬼所附的一個啞吧、帶到耶穌跟前來。\\
鬼被趕出去、啞吧就說出話來．眾人都希奇說、在以色列中、從來沒有見過這樣的事。\\
法利賽人卻說、他是靠著鬼王趕鬼。\\
耶穌走遍各城各鄉、在會堂裡教訓人、宣講天國的福音、又醫治各樣的病症。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
