\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[margin=0.5in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 21 after the Pentecost\vspace{-3ex}}
\date{\vspace{-5ex}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\normalsize
\singlespacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Лк., 39 зач., VIII, 41-56.}\\
И вот, пришел человек, именем Иаир, который был начальником синагоги; и, пав к ногам Иисуса, просил Его войти к нему в дом,\\
потому что у него была одна дочь, лет двенадцати, и та была при смерти. Когда же Он шел, народ теснил Его.\\
И женщина, страдавшая кровотечением двенадцать лет, которая, издержав на врачей всё имение, ни одним не могла быть вылечена,\\
подойдя сзади, коснулась края одежды Его; и тотчас течение крови у ней остановилось.\\
И сказал Иисус: кто прикоснулся ко Мне? Когда же все отрицались, Петр сказал и бывшие с Ним: Наставник! народ окружает Тебя и теснит,- и Ты говоришь: кто прикоснулся ко Мне?\\
Но Иисус сказал: прикоснулся ко Мне некто, ибо Я чувствовал силу, исшедшую из Меня.\\
Женщина, видя, что она не утаилась, с трепетом подошла и, пав пред Ним, объявила Ему перед всем народом, по какой причине прикоснулась к Нему и как тотчас исцелилась.\\
Он сказал ей: дерзай, дщерь! вера твоя спасла тебя; иди с миром.\\
Когда Он еще говорил это, приходит некто из дома начальника синагоги и говорит ему: дочь твоя умерла; не утруждай Учителя.\\
Но Иисус, услышав это, сказал ему: не бойся, только веруй, и спасена будет.\\
Придя же в дом, не позволил войти никому, кроме Петра, Иоанна и Иакова, и отца девицы, и матери.\\
Все плакали и рыдали о ней. Но Он сказал: не плачьте; она не умерла, но спит.\\
И смеялись над Ним, зная, что она умерла.\\
Он же, выслав всех вон и взяв ее за руку, возгласил: девица! встань.\\
И возвратился дух ее; она тотчас встала, и Он велел дать ей есть.\\
И удивились родители ее. Он же повелел им не сказывать никому о происшедшем.\\
\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Luke 8:41 -- 8:56.}\\
And, behold, there came a man named Jairus, and he was a ruler of the synagogue: and he fell down at Jesus' feet, and besought him that he would come into his house:\\
For he had one only daughter, about twelve years of age, and she lay a dying. But as he went the people thronged him.\\
And a woman having an issue of blood twelve years, which had spent all her living upon physicians, neither could be healed of any,\\
Came behind him, and touched the border of his garment: and immediately her issue of blood stanched.\\
And Jesus said, Who touched me? When all denied, Peter and they that were with him said, Master, the multitude throng thee and press thee, and sayest thou, Who touched me?\\
And Jesus said, Somebody hath touched me: for I perceive that virtue is gone out of me.\\
And when the woman saw that she was not hid, she came trembling, and falling down before him, she declared unto him before all the people for what cause she had touched him, and how she was healed immediately.\\
And he said unto her, Daughter, be of good comfort: thy faith hath made thee whole; go in peace.\\
While he yet spake, there cometh one from the ruler of the synagogue's house, saying to him, Thy daughter is dead; trouble not the Master.\\
But when Jesus heard it, he answered him, saying, Fear not: believe only, and she shall be made whole.\\
And when he came into the house, he suffered no man to go in, save Peter, and James, and John, and the father and the mother of the maiden.\\
And all wept, and bewailed her: but he said, Weep not; she is not dead, but sleepeth.\\
And they laughed him to scorn, knowing that she was dead.\\
And he put them all out, and took her by the hand, and called, saying, Maid, arise.\\
And her spirit came again, and she arose straightway: and he commanded to give her meat.\\
And her parents were astonished: but he charged them that they should tell no man what was done.\\
\end{minipage}}
\newpage\huge
\singlespacing %for chinese
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{路加福音 8:41 -- 8:56.}\\
有一個會堂主管，名叫 葉魯，來俯伏在耶穌腳前，求耶穌到他家裏去，\\
因為他有一個獨生女，約十二歲，快要死了。 耶穌去的時候，眾人簇擁着他。\\
有一個女人，患了經血不止的病有十二年，在醫生手裏花盡了一生所有的(註)，但沒有人能治好她。\\
她來到耶穌背後，摸他的衣裳繸子，經血立刻止住了。\\
耶穌說：「摸我的是誰？」眾人都不承認。 彼得說：「老師，眾人擁擁擠擠緊靠着你。」\\
耶穌說：「有人摸了我，因為我覺得有能力從我身上出去。」\\
那女人知道瞞不住了，就戰戰兢兢地俯伏在耶穌跟前，把摸他的緣故和怎樣立刻痊癒的事，當着眾人都說出來。\\
耶穌對她說：「女兒，你的信救了你。平安地回去吧！」\\
耶穌還在說話的時候，有人從會堂主管的家裏來，說：「你的女兒死了，不要勞駕老師了。」\\
耶穌聽見就對他說：「不要怕，只要信！她必得痊癒。」\\
耶穌到了他的家，除了 彼得、 約翰、 雅各，和女兒的父母，不許別人同他進去。\\
眾人都在為這女孩哀哭捶胸。耶穌說：「不要哭，她不是死了，是睡着了。」\\
他們知道她已經死了，就嘲笑耶穌。\\
耶穌拉着她的手，呼叫着：「孩子，起來吧！」\\
她的靈魂就回來了，她立刻起來。耶穌吩咐給她東西吃。\\
她的父母非常驚奇；耶穌吩咐他們不要把所發生的事告訴任何人。 \\
\end{CJK}
\end{minipage}}
\end{document}
