\documentclass[10pt]{article} % use larger type; default would be 10pt
\usepackage[utf8]{inputenc}       % кодування документа; замість cp866nav
\usepackage[top=0.2in,bottom=0.1in,left=0.3in,right=0.3in]{geometry}
\usepackage[russian,english]{babel} % національна локалізація; може бути декілька
\usepackage{setspace}
\usepackage{CJKutf8}
\usepackage{mdframed}
\title{Divine Liturgy\\Reading from The Gospels}
\author{Week 2 of the Great Lent\vspace{
-3ex%for author
}}
\date{\vspace{
-7ex%for date
}}
\begin{document}
\pagenumbering{gobble}
\begin{otherlanguage*}{russian}
\maketitle
\end{otherlanguage*}
\vspace*{\fill}
\large%for eng/rus
\onehalfspacing %\\onehalfspacing \\doublespacing % for eng/rus
\framebox[\textwidth]{
\begin{minipage}[t]{0.45\textwidth}
\begin{otherlanguage*}{russian}
\textbf{Мк., 7 зач., II, 1-12.}\\
Через несколько дней опять пришел Он в Капернаум; и слышно стало, что Он в доме.
\\
Тотчас собрались многие, так что уже и у дверей не было места; и Он говорил им слово.
\\
И пришли к Нему с расслабленным, которого несли четверо;
\\
и, не имея возможности приблизиться к Нему за многолюдством, раскрыли кровлю дома, где Он находился, и, прокопав ее, спустили постель, на которой лежал расслабленный.
\\
Иисус, видя веру их, говорит расслабленному: чадо! прощаются тебе грехи твои.
\\
Тут сидели некоторые из книжников и помышляли в сердцах своих:
\\
что Он так богохульствует? кто может прощать грехи, кроме одного Бога?
\\
Иисус, тотчас узнав духом Своим, что они так помышляют в себе, сказал им: для чего так помышляете в сердцах ваших?
\\
Что легче? сказать ли расслабленному: прощаются тебе грехи? или сказать: встань, возьми свою постель и ходи?
\\
Но чтобы вы знали, что Сын Человеческий имеет власть на земле прощать грехи,- говорит расслабленному:
\\
тебе говорю: встань, возьми постель твою и иди в дом твой.
\\
Он тотчас встал и, взяв постель, вышел перед всеми, так что все изумлялись и прославляли Бога, говоря: никогда ничего такого мы не видали.
\\

\end{otherlanguage*}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\textbf{Mark 2:1--2:12.}\\
And again he entered into Capernaum after some days; and it was noised that he was in the house.\\
And straightway many were gathered together, insomuch that there was no room to receive them, no, not so much as about the door: and he preached the word unto them.\\
And they come unto him, bringing one sick of the palsy, which was borne of four.\\
And when they could not come nigh unto him for the press, they uncovered the roof where he was: and when they had broken it up, they let down the bed wherein the sick of the palsy lay.\\
When Jesus saw their faith, he said unto the sick of the palsy, Son, thy sins be forgiven thee.\\
But there were certain of the scribes sitting there, and reasoning in their hearts,\\
Why doth this man thus speak blasphemies? who can forgive sins but God only?\\
And immediately when Jesus perceived in his spirit that they so reasoned within themselves, he said unto them, Why reason ye these things in your hearts?\\
Whether is it easier to say to the sick of the palsy, Thy sins be forgiven thee; or to say, Arise, and take up thy bed, and walk?\\
But that ye may know that the Son of man hath power on earth to forgive sins, (he saith to the sick of the palsy,)\\
I say unto thee, Arise, and take up thy bed, and go thy way into thine house.\\
And immediately he arose, took up the bed, and went forth before them all; insomuch that they were all amazed, and glorified God, saying, We never saw it on this fashion.\\

\end{minipage}}
\vspace*{\fill}
\newpage
\Huge%for chi
\vspace*{\fill}
\begin{spacing}{1.0}
\framebox[\textwidth]{
\begin{minipage}[t]{\textwidth}
\begin{CJK}{UTF8}{bsmi}
\textbf{馬可福音 2:1--2:12.}\\
過了些日子、耶穌又進了迦百農．人聽見他在房子裡、\\
就有許多人聚集、甚至連門前都沒有空地、耶穌就對他們講道。\\
有人帶著一個癱子來見耶穌、是用四個人抬來的。\\
因為人多、不得近前、就把耶穌所在的房子、拆了房頂、既拆通了、就把癱子連所躺臥的褥子都縋下來。\\
耶穌見他們的信心、就對癱子說、小子、你的罪赦了。\\
有幾個文士坐在那裡、心裡議論說、\\
這個人為甚麼這樣說呢．他說僭妄的話了．除了　神以外、誰能赦罪呢。\\
耶穌心中知道他們心裡這樣議論、就說、你們心裡為甚麼這樣議論呢。\\
或對癱子說、你的罪赦了．或說、起來、拿你的褥子行走．那一樣容易呢。\\
但要叫你們知道人子在地上有赦罪的權柄、就對癱子說、\\
我吩咐你起來、拿你的褥子回家去罷。\\
那人就起來、立刻拿著褥子、當眾人面前出去了．以致眾人都驚奇、歸榮耀與　神說、我們從來沒有見過這樣的事。\\

\end{CJK}
\end{minipage}}
\end{spacing}
\vspace*{\fill}
\end{document}
