\begin{thebibliography}{CK{\O}P11}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi

\bibitem[BR04]{bernstein2004estimates}
J.~Bernstein and A.~Reznikov.
\newblock Estimates of automorphic functions.
\newblock \emph{Mosc. Math. J}, \textbf{\textbf{4}}(1), (2004), pp. 19--37.

\bibitem[CK{\O}P11]{clerc2011generalized}
J.-L. Clerc, T.~Kobayashi, B.~{\O}rsted and M.~Pevzner.
\newblock Generalized {B}ernstein--{R}eznikov integrals.
\newblock \emph{Math. Ann.}, \textbf{349}(2), (2011), pp. 395--431.

\bibitem[HT93]{howe1993homogeneous}
R.~E. Howe and E.-C. Tan.
\newblock Homogeneous functions on light cones: the infinitesimal structure of
  some degenerate principal series representations.
\newblock \emph{Bull. Amer. Math. Soc.}, \textbf{28}(1), (1993), pp. 1--74.

\bibitem[J09]{juhl2009families}
A.~Juhl.
\newblock \emph{Families of {C}onformally {C}ovariant {D}ifferential
  {O}perators, {Q}-curvature and {H}olography}, \emph{Progr. Math,}
  \textbf{275}.
\newblock Springer Science \& Business Media (2009).

\bibitem[K15]{kobayashi2015program}
T.~Kobayashi.
\newblock A program for branching problems in the representation theory of real
  reductive groups.
\newblock \emph{Progr. Math.}, \textbf{312}, (2015), pp. 277--322.
\newblock In: \emph{{\normalfont Special issue in honor of Vogan's 60th years
  birthday}}.

\bibitem[K{\O}03]{KO2}
T.~Kobayashi and B.~{\O}rsted.
\newblock Analysis on the minimal representation of\/ {${\rm
  O}(p,q)$}.{\;}{{\rm{II}}}. {B}ranching laws.
\newblock \emph{Adv. Math.}, \textbf{180}(2), (2003), pp. 513--550.

\bibitem[KO13]{kobayashi2013finite}
T.~Kobayashi and T.~Oshima.
\newblock Finite multiplicity theorems for induction and restriction.
\newblock \emph{Adv. Math.}, \textbf{248}, (2013), pp. 921--944.

\bibitem[Kob93]{kobayashi1993}
T.~Kobayashi.
\newblock The restriction of ${A}_q \left( \lambda \right)$ to reductive
  subgroups.
\newblock \emph{Proc. Japan Acad. Ser. A Math. Sci.}, \textbf{69}(7), (1993),
  pp. 262--267.
\newblock \doi{10.3792/pjaa.69.262}.

\bibitem[K98]{10.2307/120963}
T.~Kobayashi.
\newblock Discrete decomposability of the restriction of ${A}_q(\lambda)$ with
  respect to reductive subgroups {I}{I}: Micro-local analysis and asymptotic
  {K}-support.
\newblock \emph{Annals of Mathematics}, \textbf{147}(3), (1998), pp. 709--729.

\bibitem[K14]{KOBAYASHI2014272}
T.~Kobayashi.
\newblock F-method for symmetry breaking operators.
\newblock \emph{Differential Geometry and its Applications}, \textbf{33},
  (2014), pp. 272 -- 289.

\bibitem[K16]{kobayashi16birth}
T.~Kobayashi.
\newblock \emph{Birth of new branching problems}.
\newblock
  日本数学会70年記念　総合講演・企業特別講演アブストラクト, pp. 65--92,
  日本数学会, 2016.

\bibitem[K{\O}SS15]{kobayashi2015branching}
T.~Kobayashi, B.~{\O}rsted, P.~Somberg and V.~Sou{\v{c}}ek.
\newblock Branching laws for verma modules and applications in parabolic
  geometry. {I}.
\newblock \emph{Adv. Math.}, \textbf{285}, (2015), pp. 1796--1852.

\bibitem[KP16a]{kobayashi2016differential1}
T.~Kobayashi and M.~Pevzner.
\newblock Differential symmetry breaking operators: I. {G}eneral theory and
  {F}-method.
\newblock \emph{Selecta Mathematica}, \textbf{22}(2), (2016), pp. 801--845.

\bibitem[KP16b]{Kobayashi2016}
T.~Kobayashi and M.~Pevzner.
\newblock Differential symmetry breaking operators: {I}{I}. {R}ankin--{C}ohen
  operators for symmetric pairs.
\newblock \emph{Selecta Mathematica}, \textbf{22}(2), (2016), pp. 847--911.

\bibitem[KS15]{kobayashi2015symmetry}
T.~Kobayashi and B.~Speh.
\newblock \emph{Symmetry {B}reaking for {R}epresentations of {R}ank {O}ne
  {O}rthogonal {G}roups}, \emph{Memoirs of the Amer. Math. Soc,} \textbf{238}.
\newblock American Mathematical Society (2015).

\end{thebibliography}
